### 2022-09-16 Draft_GFC.tex
file_tesis

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{tabularx}
%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption}
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}

\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\parindent 0mm    
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\tikzset{
    cross/.pic = {
    \draw[rotate = 45] (-#1,0) -- (#1,0);
    \draw[rotate = 45] (0,-#1) -- (0, #1);
    }
}

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
}

\begin{document}
\section{Introduction}
\textbf{Cabana : Affine Processes: A test of isotropy based on level sets.} 
Class of affine processes for the alternative, $H_{0} :X$ is isotropic, create the test using Estimators for the affinity parameters based only on one level set of the observed process, show consistence under some hypothesis. Proposes estimators of the affinity parameters $k = (1 - \frac{\lambda_{1}^{2}}{\lambda_{1}^{2}})$ and $\theta_{0}$ using the shape of the level curve of $X$ for fixed level $x$. Gets TCL for estimators under condition of \textit{X is uniformly mixing}. \\
Let $\mathscr{C}$ is the level sets, principal objects that are used are $\mathscr{L}(T) = |T|^{-1}\int_{\mathscr{C}}ds$, $\mathscr{C}(T) = |T|^{-1}\int_{\mathcal{C}} \cos\Theta ds$, $\mathscr{S}(T) = |T|^{-1}\int_{\mathscr{C}} \sin2\Theta ds$ that are particular c*ases of line integrals : $\mathscr{F}(f, T) = |T|^{-1}\int_{\mathscr{C}}f(\Theta)ds$, with $f:(-\pi, \pi) \to \mathbb{R}$ is a bounded measurable function.\\
Weird assumptions imply that integrals such as $\mathscr{F}$ have a first and second moment. When we assume that the field $X(t) = Y(At)$ with $Y$ isotropic and we substitute $f$ with the function that are of interest for us, we get a formula for the first moment of $\mathscr{L}$, $\mathscr{C}$ and $\mathscr{S}$. that only depends on $\lambda_{1}, k$ and $\theta_{0}$ and a weird function $g$ that is a continuously increasing function. Thus, we get that $\tan 2\theta_{0} = E\mathscr{S}/E\mathscr{C}$ and $g(k) = \sqrt{(E\mathscr{C})^2 + (E\mathscr{S})^2}/E\mathscr{L}$, \textbf{Asymptotic distributions}. Assuming the field $X$ is uniformly mixing, then we have a TCL for $\mathscr{F}(f, T)$ when the window goes to infinity, that give them the fact that $\hat{\theta_{0}}$ and $\hat{k}$ are consistent. $k$ measures the departure from isotropy. I didn't understand the last paragraph of page 5. But something leads them to consider an $F$ test of isotropy. Considering a horrible test variable $\mathscr{B}(\mathscr{T})$ with $\mathscr{T}$ is partition of $T$, they know that its distribution under $H_{0}$ ($k = 0$) tends to $F_{2, 2n-2}$ $n$ the number of partitions, if $X$ is an affine process, but not isotropic ($k \neq 0$) than the limit law is a non central F, as it is apparently well known from the analysis of variance. The critical region $\mathscr{B}(\lambda \mathscr{T}) > F_{2, 2n-2}(1-\alpha)$ ($\lambda \to \infty$ is an expansion parameter). \\
\textbf{Molina and al. : A method for testing anisotropy and quantifying its direction in digital images.}\\
 \textit{The identification of appropriate spatial models require the previous knowledge of the process exploratory properties such as the existence of a directional component which determines an anisotropic behavior of the phenomenon. Techniques used for analyzing anistropy are limited (compared to techniques for exploring stationarity) and they are only devoted to examining "by eye" experimental variograms in
different directions. (I do not know if that is true or not).} \\
They try to detect anisothropy using a method based on second order bi variate \textit{circular statistics} this allows them also to quantify the direction in which it appears. They also present an application of the method to  the flow of seawater through the Strait of Gibraltar. Tools : a parametric procedure based on the calculation of standard and confidence ellipses, well how do they do that ? and what is that. Well, It's pretty weird, they start by considering a sub image $Z_{l,l}$ of the image $Z$ and $Z(s)$ the random variable (yep nothing more on this mystery variable ), from $Z_{l,l}$ they draw $N=\{z_{1}, \ldots, z_{m}\}$ a random sample of $m$ elements, nothing is being said about this random sample. $\overrightarrow{z_{i}z_{j}}$ represents a variation of $Z(s)$ with intensity $|z_{j} - z_{i}|$ in the direction $\gamma$, being 
\begin{equation*}
\gamma = \begin{cases} \arctan{\frac{z_{jy} - z_{iy}}{z_{jx} - z_{ix}}}& \text{if} (z_{j} - z_{i}) > 0, \\
0 & \text{if} (z_{j} - z_{i}) = 0, \\
 \arctan{\frac{z_{jy} - z_{iy}}{z_{jx} - z_{ix}}} + \pi & \text{if} (z_{j} - z_{i})  < 0, 
\end{cases}
\end{equation*}
where $(z_{ix}, z_{iy})$ are the coordinates of intensity $z_i$, same for the other one. Taking the vectors $\overrightarrow{z_{i}z_{j}}$ we obtain the set $\Gamma = \{\gamma_{i}, i = 1, \ldots, n, n = \binom{m}{2}\}$, that contains the orientations in the plane of vectors. Then, they proceed to the computation of the mean vector $\hat{m}$. Given a sample $\Gamma$ its mean vector $\hat{m}$ (of length $r$ and mean angle $\hat{\Phi}$) is calculated as follows : 
\begin{equation*}
\hat{x} = \frac{1}{n} \sum_{i}^{n} b_{i}\cos{\gamma_{i}}, \; \hspace{3cm}  \; \hat{y} = \frac{1}{n}\sum_{i}^{n}b_{i}\sin{\gamma_{i}}
\end{equation*}
\begin{equation*}
r=\sqrt{\hat{x}^{2} + \hat{y}^{2}}, \; \hspace{1cm} \; \hat{\Phi} = \begin{cases} \arctan{\frac{\hat{y}}{\hat{x}}} \hspace{0.5cm} \text{if} \; \hat{x} > 0 , \\
180 + \arctan{\frac{\hat{y}}{\hat{x}}} \hspace{0.5cm} \text{if} \; \hat{x} < 0 
\end{cases}
\end{equation*}
% where $b_{i} = \begin{cases}0 \; \text{if} \; \gamma = 0 \\ 1 \; \text{else} \end{cases}$, for each sample $\Gamma_{1}, \ldots, \Gamma_{d}$ they determine a mean vector of length $r$ and mean angle $\hat{\Phi}$, (They just sample from the same image $Z_{l,l}$...). They use the standard ellipse to analyses these statistics. Hum this is what they say about this \textit{The tips of the vectors of a second order
% sample form a scatter diagram of data with
% standard deviations in the $X$ and $Y$ directions and a
% certain trend upward or downward. The standard ellipse
% describes this behavior in a condensed way: assuming
% normality, roughly $40\%$ of data points fall inside the
% ellipse and $60\%$ of them outside. The parent population
% does not need to be normal, although it is desirable that
% it does not deviate from normality too much.}
% They define the standard ellipse in the following way
% \begin{itemize}
%   \item its center $(\hat{x}, \hat{y})$ \\
%   \item Construct a rectangle with center at $(\hat{x}, \hat{y})$ and sides parallel to the $X$ and $Y$ axes.. 
%   \item the standard ellipse is embedded in the rectangle above (see the article for more details on the construction). 
  % \end{itemize}
By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$. So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ and for $x \in G_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3,4}{
  \foreach \y in {0,1,2,3,4}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $G_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in G_m}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, Using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in G_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

    here the test 
\foreach \x in {0,1}{
    \foreach \y in {0,1}
        \node[box] at (\x,\y){};
}

\node[box, fill=black] at (0,0){};  
\node[box, pattern = north west lines, pattern color=gray] at (1,0){};  
\draw[step = 1cm, red, thick] (0.5,-0.5) -- (0.5,0.5);
\foreach \x in {0.5}
{
  \draw 
    (\x cm, 0pt) -- (\x cm, 0pt) node[anchor=north] {\scriptsize $\text{\textcolor{red}{}}$};
  \pic[line width=0.5pt,red, rotate = 45] at (\x, 0.5) {mycross};
  \pic[line width=0.5pt,red, rotate = 45] at (\x, -0.5) {mycross};  
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{The edge $w_{1} = (1,1)$ in red belongs to $C_{2}(0,0) \cap C_{2}(1, 0)$, with the cell $C_{2}(0,0)$ colored in black and $C_{2}(1, 0)$ in gray dashed stripes.}
\label{fig1}
\end{figure}
\vspace{-0.5cm}
Following this consideration, one can define the random quantity
\begin{equation}
f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x}, X_{\scriptscriptstyle x +e_{i}}\right) < t \leq \max\left(X_{x}, X_{\scriptscriptstyle x+e_{i}}\right)\right\}}
\label{fi}
\end{equation}
to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of $Z^{\scriptscriptstyle (m)}$.
\begin{Definition}[Perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{x: w_{i}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$. Then, the perimeter of the binary image $Z$ is given by
\begin{equation}
\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t).
 \label{eq:6}
\end{equation}
\end{Definition}
% \section{Statistics of the perimeter} 
\section{First moment}
Let us start this study by investigating the first moment of the perimeter.
\begin{Proposition}[First moment of the perimeter] 
\label{propFisrtmoment}
We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field and $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ with $\rho(e_i) \in [-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)\right) + \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)$  and
if $\rho(e_{i}) \in ]-1,1]$, 
{\small
\begin{align}
\label{propEquationFisrtmoment}
\mathbb{E}\left(f^{(i)}(t) \right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)
\end{align}}
with $N \sim \mathcal{N}(0,1)$. 
\end{Proposition}
\begin{remark}(degenerative case)
If  $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$
\end{remark}
\begin{proof}
Let us start with the case where $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since
\begin{align*}
\left\{ x \in G_{m}; w_{i}(x) \subset (0,m)^{2}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
& = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},
\end{align*}
one can write that, 
\begin{equation}
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right).
\label{covarianeproof}
\end{equation}
 with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. \\
 We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation}
The covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
-1 & 1 \\
1 & 1  \\
\end{pmatrix}$} and $\Sigma_{i}(0) = \begin{pmatrix} 1 & \rho(e_i) \\
\rho(e_i) & 1  \\ 
\end{pmatrix}.$ \\
Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_1)  \end{pmatrix}$, which directly  implies that the two variables are independent.
{\small
\begin{align*}
\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
&= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_i} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_i}-X_{0})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2})\right\}}\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right). \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}  \leq Y \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right)
\end{align*}}  
with $N, Y \sim \mathcal{N}(0,I_{2})$, thus 
$$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
Let us now consider the case where $\rho(e_i) = -1$. Then there exists $N \sim \mathcal{N}\left(0,1\right)$ such that $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \overset{d}{=} \left(N, -N\right)$. Thus, 
\begin{align*}
\mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\
& \hspace{-6cm}= \mathbb{P}\left(-|N| < t \leq |N|\right) = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{-z < t \leq z\right\}} e^{-\frac{z^2}{2}}dz  = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{t \leq z\right\}} e^{-\frac{z^2}{2}}dz \\
& \hspace{-6cm}= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).
\end{align*}
\end{proof}
Note that this result extends those given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$.

\begin{remark}
\label{iidCase}
In the independent case, $\rho(e_i) = 0$, we can write
{\small
\begin{align*}
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) & = m(m-1)\mathbb{E}\left(\Phi\left(\sqrt{2}t + |Z|\right) - \Phi\left(\sqrt{2}t - |Z|\right)\right) = 2m(m-1)\Phi(t)\left(1-\Phi(t)\right) 
\end{align*}}
by applying a variable change {\small$\left\{\begin{array}{rcl}
u & = & \frac{y - z}{\sqrt{2}} \\
v & = & \frac{y+z}{\sqrt{2}} \\
\end{array}\right.$}, we get the same result as in \cite{Psymetrie} (Proposition \textcolor{blue}{3.1}).
\end{remark}
\begin{remark}
In order to have convergence when $m \to \infty$, one has to consider the normalise perimeter with the area of the window ($m^2$).
\end{remark}
The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$.
\begin{Proposition}
Under the assumptions stated in Proposition \ref{propFisrtmoment}, we get 
\begin{equation}
\label{totalvariation}
\int_{\mathbb{R}} \mathbb{E}\left(\mathcal{P}^{(i)}_{m}(t)\right) dt = \frac{2m(m-1)}{\sqrt{\pi}}\left(\sqrt{1-\rho(e_i)}  \right).
\end{equation}
\end{Proposition}
\begin{proof}
Using the result stated in Proposition \ref{propFisrtmoment}, we get that $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right)$ is equal to,
{\small
\begin{align*}
\int_{\mathbb{R}} \mathbb{E}\left(\mathcal{P}^{(i)}_{m}(t)\right) dt & = \\
& \hspace{-2cm}\cfrac{m(m-1)}{\sqrt{2\pi}} \int_{\mathbb{R}}\int_{\mathbb{R}} \left(\Phi\left(\dfrac{\sqrt{2}t + \sqrt{1-\rho(e_i)}|u|}{\sqrt{1+\rho(e_i)}}\right) - \Phi\left(\dfrac{\sqrt{2}t - \sqrt{1-\rho(e_i)}|u|}{\sqrt{1+\rho(e_i)}}\right)\right)e^{-\frac{1}{2}u^2}dudt \\
& \hspace{-2cm}=\cfrac{m(m-1)}{2\pi} \int_{\mathbb{R}}\int_{\mathbb{R}}\int_{\mathbb{R}} e^{-\frac{1}{2}u^2}e^{-\frac{1}{2}v^2} \mathbbm{1}_{\left\{\dfrac{\sqrt{2}t - \sqrt{1-\rho(e_i)}|u|}{\sqrt{1+\rho(e_i)}}\leq v \leq\dfrac{\sqrt{2}t + \sqrt{1-\rho(e_i)}|u|}{\sqrt{1+\rho(e_i)}}\right\}} du dv dt ,\\
& \hspace{-2cm}\text{using Fubini-Tonelli Theorem,} \\
& \hspace{-2cm}= \cfrac{m(m-1)}{2\pi}\int_{\mathbb{R}}\int_{\mathbb{R}} e^{-\frac{1}{2}u^2}e^{-\frac{1}{2}v^2} \\
& \hspace{-2cm} \left(\int_{\mathbb{R}} \mathbbm{1}_{\left\{\dfrac{\sqrt{1+\rho(e_i)}v - \sqrt{1-\rho(e_i)}|u|}{\sqrt{2}}\leq t\leq\dfrac{\sqrt{1+\rho(e_i)}v + \sqrt{1-\rho(e_i)}|u|}{\sqrt{2}}\right\}} dt\right) du dv \\
& \hspace{-2cm}= \cfrac{m(m-1)}{2\pi} \int_{\mathbb{R}}\int_{\mathbb{R}} e^{-\frac{1}{2}u^2}e^{-\frac{1}{2}v^2}\left(\dfrac{2|u|\sqrt{1-\rho(e_i)}}{\sqrt{2}}\right)dudv = \frac{2\sqrt{1-\rho(e_i)}}{\sqrt{2}} m(m-1)\underbrace{\mathbb{E}(|U|)}_{\sqrt{\frac{2}{\pi}}}\\
&\hspace{-2cm}=\frac{2}{\sqrt{\pi}}m(m-1)\sqrt{1-\rho(e_i)}.
\end{align*}
}
\end{proof}
\begin{remark}
The first moment of the total variation is given by the sum over the two directions of Equation \eqref{totalvariation}. 
\end{remark}
\begin{remark}
Using this result, one can define an estimator for $\rho(e_i)$. 
\end{remark}
Study of the behavior of the nodal curve $t = 0$, 
\begin{remark}
Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 
\begin{equation*}
 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right).
\end{equation*}
Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the normalized perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
\end{remark}
\begin{proof}
Note that $\rho \mapsto \sqrt{1-\rho}$ is decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also decreasing. 
\end{proof}
\textcolor{blue}{reorient toward Github for illustrations.}
\section{Covariance of the perimeter for two thresholds}
Let $s, t \in \mathbb{R}$ such that $t \leq s$. Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
\begin{Lemma} 
\label{CovLemma}
\begin{align}
\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + 2\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .
\label{covariance}
\end{align} 
With 
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (i)}(s) \right) 
& = \sum_{x_{\scriptscriptstyle 1}=\left(1-m\right)}^{m-1}\sum_{x_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|x_{1}|\right)\left(m - 1- |x_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (i)}(0), f_{s}^{\scriptscriptstyle (i)}(x) \right) 
\end{align*} 
and 
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{x_1 = 0}^{m-2} \sum_{x_2=1}^{m-1}\left(m-x_1-1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = 0}^{m-2} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m-x_1-1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=1}^{m-1}\left(m+x_1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m+x_1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right) 
\end{align*}
\end{Lemma}
\begin{proof}
To simplify the notations, we chose to do the computations for direction $i =1$. Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 
\begin{align*}
\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))& = \text{Cov}\left( \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}}f_{t}^{\scriptscriptstyle (1)}(x), \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{s}^{\scriptscriptstyle (1)}(y)\right) \\
& = \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right).
\end{align*}
By the stationarity hypothesis, one has $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right)= \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(y-x) \right)$. Then 
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right)
\end{align*}
for $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has
\begin{align*} 
\left\{
\begin{array}{rcl}
0 \leq x_1 \leq m-1 \\
0 \leq y_1 \leq m-1 
\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
0 \leq x_1 \leq m-1 \hspace{0.7cm} \\
-x_1 \leq z_1 \leq m-1 - x_1
\end{array}\right. \\
& \implies  \left\{
\begin{array}{rcl}
1-m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
\max(0, -z_1) \leq x_1 \leq \min(m-1 , m-1-z_1)
\end{array}\right..
\end{align*} 
Similarly for $z_2 = y_2 - x_2$ and $x_2 \in [1, m-1]$
\begin{align*}
 \left\{
\begin{array}{rcl}
1 \leq x_2 \leq m-1 \\
1 \leq y_2 \leq m-1 
\end{array}\right. & \implies
\left\{
\begin{array}{rcl}
2-m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
\max(1, 1-z_2) \leq x_2 \leq \min(m-1 , m-1-z_2).
\end{array}\right., 
\end{align*}
Thus,
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(1-m\right)}^{m-1}\sum_{z_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|z_{1}|\right)\left(m - 1- |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right) 
\end{align*}
For the second part of \eqref{covariance}, we have still by stationarity
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \sum_{y, w_{2}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)\\
& =  \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 1}^{m-1}\sum_{y_2 = 0}^{m-1}\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)
\end{align*}
Again, considering $z_1 = y_1 - x_1$
\begin{align*} 
\left\{
\begin{array}{rcl}
0 \leq x_1 \leq m-1 \\
1 \leq y_1 \leq m-1 
\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
0 \leq x_1 \leq m-1 \hspace{0.7cm} \\
1 -x_1 \leq z_1 \leq m- 1 - x_1
\end{array}\right. \\
& \implies  \left\{
\begin{array}{rcl}
2 - m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
\max(0, 1-z_1) \leq x_1 \leq \min(m-1 , m-1-z_1),
\end{array}\right.
\end{align*} 
and, $z_{2} = y_{2}-x_{2}$
\begin{align*} 
\left\{
\begin{array}{rcl}
1 \leq x_2 \leq m-1 \\
0 \leq y_2 \leq m-1 
\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
1 \leq x_2 \leq m-1 \hspace{0.7cm} \\
-x_2 \leq z_2 \leq m- 1 - x_2
\end{array}\right. \\
& \implies  \left\{
\begin{array}{rcl}
1 - m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
\max(1, -z_2) \leq x_2 \leq \min(m-1 , m-1-z_2)
\end{array}\right..
\end{align*} 
Thus, 
\begin{align*}
\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{z_2 = 0}^{m-2} \sum_{z_1=1}^{m-1}\left(m-z_2-1\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = 0}^{m-2} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m-z_2-1\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=1}^{m-1}\left(m+z_2\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m+z_2\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) 
\end{align*}
\end{proof}
Getting the value of the covariance requires the computation of all the elements of the sum, let us first start with the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$,
\begin{Lemma}
The case $x=0$ is a special case, in order to compute it, we just have to apply the same strategy we used to compute the first moment in \ref{propFisrtmoment}, thus we get,
\begin{align*}
\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) \\
& - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right).
\end{align*}
And, 
{\small
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) & = \\
& \hspace{-9cm}\mathbb{E}\left(\left(\Phi\left(\dfrac{\sqrt{2}\max\left(t,s\right) + \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)  - \Phi\left(\dfrac{\sqrt{2}\min\left(t,s\right) - \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)\right)\right. \\
& \hspace{-1cm} \left.\mathbbm{1}_{\left\{(|s-t| \leq |Z|\sqrt{2(1-\rho(e_1))}\right\}}\right)
\end{align*}}
with $Z \sim \mathcal{N}(0,1)$. 
\end{Lemma}
\subsection{Three and four cells configuration}
Figure \ref{configurations} shows the four types of configurations that are encountered in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma} depending on the orientation $i$ and position on the grid $x$. We will call \textit{three cells} and \textit{four cells} configuration depending on how many cells are involved. 
\begin{figure}[H]
\begin{center}
  \captionsetup[subfigure]{justification=centering}
  \begin{subfigure}[b]{0.25\textwidth} 
  \centering
\begin{tikzpicture}[scale = 1.5]
\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
\draw[step = 2cm, line width =0.5mm, blue] (1,0) -- (1,0.5);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
\draw[pattern=north east lines, pattern color=red] (0.5, 0) rectangle (1,0.5);
\draw[pattern=north west lines, pattern color=cyan, opacity=1] (1, 0) rectangle (1.5,0.5);
\end{tikzpicture}
\caption{$i = 1$, $x = (0,1)$}
\end{subfigure}
  \hspace{0.5cm}
  \begin{subfigure}[b]{0.25\textwidth} 
  \centering
\begin{tikzpicture}[scale =1.5]
\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
\draw[step = 2cm, line width =0.5mm, blue] (0,0.5) -- (0.5,0.5);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
\draw[pattern=north east lines, pattern color=red] (0, 0.5) rectangle (0.5,1);
\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
\end{tikzpicture}
\caption{$i = 2, x = (0,0)$}
\end{subfigure}
~\\
\begin{subfigure}[b]{0.25\textwidth} 
\centering 
\begin{tikzpicture}[scale = 1.5]
\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
\draw[step = 2cm, line width =0.5mm, blue] (1,1) -- (1.5,1);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
\draw[pattern=north west lines, pattern color=green, opacity=1] (1.5, 1.5) rectangle (1,1);
\draw[pattern=north west lines, pattern color=red, opacity=1] (1, 0.5)  rectangle (1.5, 1);
\end{tikzpicture}
\caption{$i = 2, z = (2,1)$}
\end{subfigure}
  \hspace{0.5cm}
  \begin{subfigure}[b]{0.25\textwidth} 
  \centering 
\begin{tikzpicture}[scale = 1.5]
\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
\draw[step = 2cm, line width =0.5mm, blue] (1,1) -- (1,1.5);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
\draw[pattern=north west lines, pattern color=green, opacity=1] (1.5, 1.5) rectangle (1,1);
\draw[pattern=north west lines, pattern color=red, opacity=1] (0.5, 1)  rectangle (1, 1.5);
\end{tikzpicture}
\caption{$i = 1, x = (1,2)$}
\end{subfigure}
\end{center}
\caption{Illustration of the three cells and four cells configuration (respectively first and second row) involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
\label{configurations}
\end{figure}
Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
\rho(e_1) & 1 & \rho(x-e_1) &  \rho(x+e_i- e_1) \\ 
\rho(x) & \rho(x-e_1) & 1 & \rho(e_i) \\
\rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$ 
Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x}\end{equation} and 
{\small
$\left\{\begin{array}{rlc}
\Delta \rho(x) & = & \rho(x-e_1)-\rho(x) \\
S\rho(x) & = & \rho(x-e_1)+\rho(x)\\
\Delta \rho(x+e_i) & = & \rho(x+e_i-e_1)-\rho(x+e_i) \\
S\rho(x+e_i) & = & \rho(x+e_i-e_1)+\rho(x+e_i)\\
\end{array}\right.\\
$
}
The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}~= M\Sigma M^{\star}}$ with {\small $M = \begin{pmatrix}
-1 & 1 & 0 &  0 \\
1 & 1 & 0 &  0 \\
0& 0 & -1 &  1 \\
0 & 0 & 1 & 1
\end{pmatrix}$}. \\
Then $\tilde{\Sigma} = \begin{pmatrix} A_{1} & B \\ B^{\star} & A_{i} \end{pmatrix}$
with 
$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ \\
and {\small $B = \begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\ 
 S\rho(x+e_i)- S\rho(x) &  S\rho(x) + S\rho(x+e_i) 
 \end{pmatrix}$}. \\
The quantity we aim to compute is 
{\small
\begin{align}
\label{covconf}
\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right) & = \nonumber \\
& \hspace{-2.7cm} \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber\\
& \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
\end{align}}Considering the first part of the previous equation, 
{\small
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_1} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_1}-X_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, X_{x+e_i}-X_{\scriptscriptstyle x}) \leq s - X_{\scriptscriptstyle x} \leq \max(0, X_{x+e_i} - X_{\scriptscriptstyle x}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \leq s + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} - S^{i}_{\scriptscriptstyle x}}{2} \leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2})\right\}}\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \leq s - \frac{S^{i}_{\scriptscriptstyle x}}{2} \leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2},\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \right\}}\right) \\
& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\Sigma_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$. We get the following decomposition \\ 
$\left\{
  \begin{array}{rlc}
  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_1U, \\
  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_2V, \\
  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W, \\
  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(i)}_{U}(x)U +  \pi^{\scriptscriptstyle(i)}_{V}(x) V +  \pi^{\scriptscriptstyle(i)}_{W}(x) W +  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z, 
\end{array}\right.$ \\
with 
$\left\{
 \begin{array}{rlc}
 \sigma_1 & = &  \sqrt{2(1-\rho(e_1))} \\
 \sigma_2 & = & \sqrt{2(1+\rho(e_1))} \\
   \alpha^{\scriptscriptstyle(i)}_{U}(x) & = & \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma_1} \\
   \alpha^{\scriptscriptstyle(i)}_{V}(x) & = &  \frac{S\rho(x+e_i)-S\rho(x)}{\sigma_{2}}  \\
   \alpha^{\scriptscriptstyle(i)}_{W}(x)& = & \sqrt{2(1 - \rho(e_{i})) - \alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}} \\ 
   \pi^{\scriptscriptstyle(i)}_{U}(x) & = &  \frac{\Delta \rho(x) + \Delta \rho(x+e_i)}{\sigma_1} \\
    \pi^{\scriptscriptstyle(i)}_{V}(x) & = & \frac{S \rho(x) + S\rho(x+e_i)}{\sigma_{2}} \\
   \pi^{\scriptscriptstyle(i)}_{W}(x) & = & \frac{\rho(x)^{2} - \rho(x+e_i)^{2} + \rho(x-e_1)^{2} - \rho(x + e_i - e_1)^{2} - 2\rho(e_1)\left(\rho(x)\rho(x-e_1) - \rho(x+e_i)\rho(x+e_i-e_1)\right)}{(1-\rho(e_1)^{2})\alpha^{\scriptscriptstyle(i)}_{W}(x)}\\
   \pi^{\scriptscriptstyle(i)}_{Z}(x)& = & \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}
\end{array}\right.$ 
\begin{Proposition}
\label{PropositionFourCell}
Considering the assumptions above, the two cases that we have to distinguish when computing \eqref{covconf} are $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$ and $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, thus we get 
\begin{itemize}
  \item if $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$, then 
  {\small 
\begin{align}
\label{Thisthofour}
\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle 1}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \nonumber \\
& \hspace{-5.4cm} \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \geq 0\right\}} \right. \right. \nonumber \\
& \hspace{-5cm}\left. \left. \left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right. \right. \right. \nonumber \\
& \hspace{-5cm}\left. \left. \left. - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right) \right. \right. \nonumber \\
&  \hspace{-5cm} \left. \left. + \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 0\right\}} \right. \right. \nonumber\\
& \left. \left. \hspace{-5cm}\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W   \right)  \right. \right. \right. \nonumber \\
& \hspace{-5cm}\left. \left. \left. - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right)\right)\right)\right),
\end{align}
}with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x))^{-2})$.
\item else, if $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, and $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0, S\rho(x) > 0$, $S\rho(x+e_i) > 0$ then, 
{\tiny
\begin{align}
\label{thisthothree}
\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left( \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x+e_i)}\right) \right) \right)\right.\\
&\hspace{-4.5cm} \left. \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right)\\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right)\right)\right.\\
& \hspace{-4.5cm} \left. \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right) \\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x+e_i)}\right)\right) - \Phi\left( \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \right)\right)\right. \\
& \hspace{-4.5cm}\left. \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \right) \\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right)\right)\right.\\
& \hspace{-4.5cm}\left.\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}}\right)
\end{align}}
\item else if $\pi^{\scriptscriptstyle(i)}_{Z}(x)= \pi^{\scriptscriptstyle (i)}_{V}(x) = S\rho(x+e_i) = 0$, then
{\tiny 
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}\right) - \Phi\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}} \right) \right)\right.\\
&\hspace{-4.5cm}  \left.\left(\mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
& \left.\left. \left. + \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right.\right.\\
& \hspace{-4cm}+ \left.\left. \mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
& \left.\left.\left. \left. \left. + \mathbbm{1}_{\left\{ 0 \geq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right)\right)\right)\right)
\end{align*}
}
\end{itemize}
\end{Proposition}
\begin{proof}(Proof of Proposition \ref{PropositionFourCell})
Let us first consider the indicator functions and assume that $\Delta^{i}_{\scriptscriptstyle x} \geq 0$. Then 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ |2s - S^{i}_{\scriptscriptstyle x}| < \Delta^{i}_ {\scriptscriptstyle x}\right\}} & =  \mathbbm{1}_{\left\{- \Delta^{i}_ {\scriptscriptstyle x} \leq 2s - S^{i}_ {\scriptscriptstyle x} \leq \Delta^{i}_ {\scriptscriptstyle x}\right\}} \\
& \hspace{-2.1cm} = \mathbbm{1}_{\left\{ -  \alpha^{\scriptscriptstyle(i)}_{U}(x)U -  \alpha^{\scriptscriptstyle(i)}_{V}(x) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{U}(x)U -  \pi^{\scriptscriptstyle(i)}_{V}(x) V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
& \phantom{=} \hspace{4.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq   \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
&\hspace{-2.1cm} = \mathbbm{1}_{\left\{ \left( \pi^{\scriptscriptstyle(i)}_{U}(x) -  \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) -  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
& \phantom{=} \hspace{4.2cm}\textcolor{white}{\mathbbm{1}}_{\left.\leq \left( \pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) +  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\ 
& \hspace{-2.1cm} = \mathbbm{1}_{\left\{\frac{2\Delta \rho(x)}{\sigma_1} U + \frac{2S \rho(x)}{\sigma_{2}}V - \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq \frac{2\Delta \rho(x+e_i) }{\sigma_1}U + \frac{2S \rho(x+e_i)}{\sigma_{2}}V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W\right\}}.
\end{align*}}
Else if $\Delta^{i}_{\scriptscriptstyle x} < 0$, then  
\begin{align*}
\mathbbm{1}_{\left\{ |s - \frac{S^{i}_{\scriptscriptstyle x}}{2}| < -\frac{1}{2}\Delta^{i}_ {\scriptscriptstyle x}\right\}} & =  \mathbbm{1}_{\left\{\Delta^{i}_ {\scriptscriptstyle x} \leq 2s - S^{i}_ {\scriptscriptstyle x} \leq -\Delta^{i}_ {\scriptscriptstyle x}\right\}} \\
& \hspace{-2.2cm} = \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{U}(x)U -  \pi^{\scriptscriptstyle(i)}_{V}(x) V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
& \phantom{=} \hspace{2.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq  - \alpha^{\scriptscriptstyle(i)}_{U}(x)U -  \alpha^{\scriptscriptstyle(i)}_{V}(x) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
& \hspace{-2.2cm}  = \mathbbm{1}_{\left\{ \left( \pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) +  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
& \phantom{=} \hspace{2.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq \left( \pi^{\scriptscriptstyle(i)}_{U}(x) -  \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) -  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\ 
& \hspace{-2.2cm} = \mathbbm{1}_{\left\{\frac{2\Delta \rho(x+e_i) }{\sigma_1} U + \frac{2S\rho(x+e_i)}{\sigma_{2}}V + \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s - \pi^{\scriptscriptstyle(i)}_{W}(x) W - \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq \frac{2\Delta \rho(x)}{\sigma_1}U + \frac{2S \rho(x)}{\sigma_{2}}V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W\right\}}
\end{align*}
Putting everything together we get that 
{\tiny
\begin{align*}
\mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\mathbbm{1}_{ \left\{-2s + \frac{2\Delta \rho(x)}{\sigma_1} U + \frac{2S \rho(x)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq  -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq -2s + \frac{2\Delta \rho(x+e_i) }{\sigma_1}U + \frac{2S \rho(x+e_i)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}} \\
& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} < 0\right\}} \mathbbm{1}_{\left\{-2s + \frac{2\Delta \rho(x+e_i) }{\sigma_1} U + \frac{2S\rho(x+e_i)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq - \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq -2s + \frac{2\Delta \rho(x)}{\sigma_1}U + \frac{2S \rho(x)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}} \\
& \hspace{-14.5cm} = \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\mathbbm{1}_{\left\{2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq 2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}}\\
& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} < 0\right\}} \mathbbm{1}_{\left\{2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq  \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}} \\
& \hspace{-14.5cm} \overset{\mathbb{E}}{=} \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \leq 0\right\}}\left\{\left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right. \right.\\
& \left.\left. \hspace{-13cm} - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W\right) \right] \right. \\
& \hspace{-14.5cm} \left. \mathbbm{1}_{\left\{- \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right\}} \right\}\\
& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\left\{\left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)} \left(2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right. \right.\\
& \hspace{-14cm} \left. \left. - \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right] \right.\\ 
& \hspace{-14cm}\left.\mathbbm{1}_{\left\{- \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}}\right\} \\
&\hspace{-14.5cm} \overset{\mathbb{E}}{=} \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \leq 0\right\}} \left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right.\\
& \left. \hspace{-13cm} - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W\right) \right]\\
& \hspace{-14.2cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\left[\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right) \right.  \\
& \hspace{-13.5cm}\left.- \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right)\right]
\end{align*}}
Since
{\small
\begin{align*}
\mathbbm{1}_{\left\{- \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}} & = \\
& \hspace{-11.7cm} \mathbbm{1}_{\left\{- 2\alpha^{\scriptscriptstyle(i)}_{U}(x)U - 2\alpha^{\scriptscriptstyle(i)}_{V}(x)V - 2\alpha^{\scriptscriptstyle(i)}_{W}(x)W \leq  0\right\}}  = \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}
\end{align*}}Putting everything together, we get
{\small
\begin{align}
\label{Thistho}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber \\
& \hspace{-9.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \geq 0\right\}} \right. \right. \nonumber \\
& \hspace{-8.5cm}\left. \left. \left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right. \right. \right. \nonumber \\
& \hspace{-7.5cm}\left. \left. \left. - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right) \right. \right. \nonumber \\
&  \hspace{-8.75cm} \left. \left. + \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 0\right\}} \right. \right. \nonumber\\
& \left. \left. \hspace{-8.5cm}\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W   \right)  \right. \right. \right. \nonumber \\
& \hspace{-7.5cm}\left. \left. \left. - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right)\right)\right)\right)
\end{align}
}
with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x)^{2})^{-1})$. \\
Now, considering the case where $\pi^{1}_{Z}(x)= 0$, thus, we effectively lose the impact of the fourth variable $Z$, and we can express the whole system using only three variables independent Gaussian variables. Considering the new expression of the variables in the indicator function, we distinguish two cases $s - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2} \geq 0$ and $s - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2} \leq 0$, we shall start with the first one. 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{i}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\left(\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq \Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}\right\}}  +  \mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq \Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}\right\}}\right) \\
& = \mathbbm{1}_{\left\{ - \pi^{\scriptscriptstyle (i)}_{V}(x)V \geq -2s +   \pi^{\scriptscriptstyle (i)}_{U}(x)U + \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\right.\\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{ - \left(\alpha^{\scriptscriptstyle (i)}_{V}(x) + \pi^{\scriptscriptstyle (i)}_{V}(x)\right)V \leq -2s+ \left(\alpha^{\scriptscriptstyle (i)}_{U}(x)+\pi^{\scriptscriptstyle (i)}_{U}(x)\right)U +  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ \left(\alpha^{\scriptscriptstyle (i)}_{V}(x) - \pi^{\scriptscriptstyle (i)}_{V}(x)\right)V \leq  -2s + \left(\pi^{\scriptscriptstyle (i)}_{U}(x) - \alpha^{\scriptscriptstyle (i)}_{U}(x)\right)U + \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}}\right) \\
& = \mathbbm{1}_{\left\{ - \pi^{\scriptscriptstyle (i)}_{V}(x)V \geq -2s +   \pi^{\scriptscriptstyle (i)}_{U}(x)U + \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}}\left(\right.\\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{ - \frac{S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V \leq -2s+ 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U +   \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ -\frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V \leq  -2s +\frac{2\Delta\rho(x)}{\sigma_1}U +  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}}\right) \\
\end{align*}}
Assuming that $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0 $, $S\rho(x+e_i)> 0$ and $S\rho(x)> 0$ we get 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ V \leq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{V \geq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)}{S\rho(x+e_i)}\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ V \geq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{1}_{W}(e_1) - \alpha^{1}_{W}(e_1)\right)W\right)}{2S\rho(x)}\right\}}\right)
\end{align*}}
Considering now the first part of the expression, we get 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}} & =  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}
\end{align*}}
Thus putting those two inequalities together we get, 
{\tiny
\begin{align*}
\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
& \hspace{-5cm}=  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}\mathbbm{1}_{\left\{ V \leq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{V \geq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)}{S\rho(x+e_i)}\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ V \geq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right\}}\right)\\
& \hspace{-7cm}= \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\\
& \hspace{-5cm} + \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}
\end{align*}}
Then again considering the other part $2s - S^{i}_{\scriptscriptstyle x} \leq 0$ we get 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ V \geq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
& \hspace{0.35cm}   \mathbbm{1}_{\left\{ V \leq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)} \right\}}  \\
& \hspace{0.35cm}  + \mathbbm{1}_{\left\{ V \leq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right\}}\bigg)  
\end{align*}}

And again 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
& \hspace{-5cm} = \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)  \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \\
& \hspace{-4.5cm} + \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)  \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}} 
\end{align*}}
And now we integrate 
{\tiny 
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left( \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right) \right)\right.\\
&\hspace{-4.5cm} \left. \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right)\\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right)\right)\right.\\
& \hspace{-4.5cm} \left. \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right) \\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right)\right) - \Phi\left( \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \right)\right)\right. \\
& \hspace{-4.5cm}\left. \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \right) \\
& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right)\right)\right.\\
& \hspace{-4.5cm}\left.\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}}\right)
\end{align*}
}
if $S\rho(x) = 0$ and $S\rho(x+e_i) = 0$, thus $\pi^{\scriptscriptstyle (i)}_{V}(x) = 0$ then, 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ 0\geq \left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{1}_{W}(e_1) - \alpha^{1}_{W}(e_1)\right)W\right)\right\}}\right)
\end{align*}}
Then, again 
{\small
\begin{align*}
\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
& \hspace{-5cm}=  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}\mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)\right\}} \right. \\
& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ 0 \geq \left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)
\end{align*}}
Then, again,
{\small
\begin{align*}
\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
& \hspace{0.35cm}   \mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}  \\
& \hspace{0.35cm}  + \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\bigg)  
\end{align*}} 
{\tiny 
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}\right) - \Phi\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}} \right) \right)\right.\\
&\hspace{-4.5cm}  \left.\left(\mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
& \left.\left. \left. + \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right.\right.\\
& \hspace{-4cm}+ \left.\left. \mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
& \left.\left.\left. \left. \left. + \mathbbm{1}_{\left\{ 0 \geq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right)\right)\right)\right)
\end{align*}
}
\end{proof}
\subsubsection{Spatial independent case} 
Let us start by considering the four cell configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
$\alpha^{\scriptscriptstyle(i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thistho} becomes 
{\small
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber \\
& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}} \right.  \\
& \left. \hspace{-10cm} \left(\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_i))}W \geq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s + \sqrt{2(1-\rho(e_1))} W\right) - \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \sqrt{2(1-\rho(e_1))} W\right)\right) \right. \right. \\
&  \hspace{-10cm} \left. \left. \mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))} W  \leq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \sqrt{2(1-\rho(e_1))}W \right) - \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s + \sqrt{2(1-\rho(e_1))} W\right)\right)\right)\right)\\ 
& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}}\mathbbm{1}_{\left\{ |s - \frac{\sqrt{2(1+\rho(e_i))}Z}{2}| \leq |\frac{\sqrt{2(1-\rho(e_i))}W}{2}|\right\}}\right) \\
& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{ |s - \frac{\sqrt{2(1+\rho(e_i))}Z}{2}| \leq |\frac{\sqrt{2(1-\rho(e_i))}W}{2}|\right\}}\right).
\end{align*}
}Thus, $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (j)}(z)\right) = 0.$\\
Regarding the three cell configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$. Thus, those computations would give us the following expression,
{\tiny
\begin{align}
\label{IIDCase}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{e_1}, X_{e_2}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) \nonumber \\
& \hspace{-8.7cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U + \sqrt{2(1+\rho(e_1))}V \leq s\right\}}\right. \nonumber \\
& \hspace{-8cm} \left. \left(1 - \Phi_{\alpha^{(1)}(e_1)}\left(\max\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right) \nonumber\\
& \hspace{-8cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U+ \sqrt{2(1+\rho(e_1))}V \geq s\right\}}\right. \nonumber\\
& \hspace{-8cm} \left. \left(\Phi_{\alpha^{(1)}(e_1)}\left(\min\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right),
\end{align}}then if the Gaussian field $\left(X(x)\right)_{x \in G_{m}}$ is such that all the variables are independent, then $\rho(2e_1) = \rho(e_1) = 0$, thus Equation \eqref{IIDCase} becomes 
{\small
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
& \hspace{-9cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{\frac{1}{\sqrt{2}} U + \frac{1}{\sqrt{2}}V \leq s\right\}} \left(1 - \Phi\left(s\right)\right)\right) \\
& \hspace{-9cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{ s \leq \frac{1}{\sqrt{2}}U + \frac{1}{\sqrt{2}}V \right\}}\Phi\left(s\right)\right) \\
& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \leq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq s \right\}}\right) \right)\\
& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \geq s \right\}}\right) \right)
\end{align*}}
Applying the same strategy we adopted in \ref{iidCase} and considering the change variable $Z = \frac{V-U}{\sqrt{2}}$ and $Y = \frac{U+V}{\sqrt{2}}$ we get 
{\small
\begin{align*}
\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \leq s \right\}} + \mathbbm{1}_{\left\{Z \leq s \right\}}\right) \right)\\
& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \geq s \right\}} + \mathbbm{1}_{\left\{Z \geq s \right\}}\right) \right) \\
& \hspace{-9cm}= (1-\Phi(s))\Phi(t)\left(\Phi(s) - \Phi(t)\right) + (1-\Phi(s))\left(1-\Phi(t)\right)\Phi(t)   + \Phi(s)\Phi(t)\left(1-\Phi(s)\right)\\
& \hspace{-9cm}= \Phi(t)\left(1-\Phi(s)\right)\left(1+ 2\Phi(s) - 2\Phi(t)\right).
\end{align*}}
This result was previously proved in \cite{Psymetrie} (Proposition \textcolor{blue}{3.2}).
\subsubsection{The behavior of $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$ when $x\to \infty$.}
Considering the case where $x$ goes to $\infty$, one can assume that there exist $\epsilon > 0$ such that $\rho(x) \sim \epsilon$ thus the former expressions become \\

\begin{table}[H]
\begin{tabularx}{\textwidth}{|l| l|X|}
\hline
$\Delta \rho(x)$ & \hspace{4cm}$\rho(x-e_1)-\rho(x)$ & $O(\rho(x))$ \\ \hline
$S\rho(x)$ & \hspace{4cm}$\rho(x-e_1)+\rho(x)$ & $O(\rho(x))$ \\  \hline
$\Delta \rho(x+e_i)$ &\hspace{3cm} $\rho(x+e_i-e_1)-\rho(x+e_i)$ & $O(\rho(x))$ \\ \hline 
$S\rho(x + e_i)$ & \hspace{3cm}$\rho(x+e_i-e_1)+\rho(x+e_i)$ & $O(\rho(x))$ \\\hline 
$\alpha^{\scriptscriptstyle(i)}_{U}(x)$ &\hspace{4cm} $ \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma_1}$ & $O(\rho(x))$ \\  \hline
$\alpha^{\scriptscriptstyle(i)}_{V}(x)$ & \hspace{4cm}   $\frac{S\rho(x+e_i)-S\rho(x)}{\sigma_{2}}$  & $O(\rho(x))$ \\  \hline
$\alpha^{\scriptscriptstyle(i)}_{W}(x)$ & \hspace{2cm}$\sqrt{2(1 - \rho(e_{i})) - \alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}} $ & {\tiny$ \sqrt{2(1 - \rho(e_i)) } + O\left(\rho(x)^{2}\right)$}\\ 
\hline
$\pi^{\scriptscriptstyle(i)}_{U}(x)$ & $ \hspace{4cm} \frac{\Delta \rho(x) + \Delta \rho(x+e_i) }{\sigma_1}$ & $O(\rho(x))$  \\ \hline
$ \pi^{\scriptscriptstyle(i)}_{V}(x)$ & \hspace{4cm}$\frac{S \rho(x) + S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}} $ & $O(\rho(x))$ \\ \hline 
$ \pi^{\scriptscriptstyle(i)}_{W}(x) $ & $\frac{\rho(x)^{2} - \rho(x+e_i)^{2} + \rho(x-e_1)^{2} - \rho(x + e_i - e_1)^{2} - 2\rho(e_1)\left(\rho(x)\rho(x-e_1) - \rho(x+e_i)\rho(x+e_i-e_1)\right)}{(\sigma_{1}\sigma_{2})^{2}\alpha^{\scriptscriptstyle(i)}_{W}(x)}$ & $O\left(\rho(x)^2\right)$\\ \hline
$\pi^{\scriptscriptstyle(i)}_{Z}(x)$ & $ \hspace{2cm} \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}$ & {\tiny$ \sqrt{2(1 + \rho(e_i)) } + O\left(\rho(x)^{2}\right)$} \\\hline 
\end{tabularx}
\end{table}
We denote by $R_{1}(x) = \frac{-\alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}}{\sigma^{\scriptscriptstyle(i)}_{1}}$ and $R_{2}(x) = \frac{- \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}{\sigma^{\scriptscriptstyle(i)}_{2}}$.\\
Thus, Taylor's expansion of $\pi^{\scriptscriptstyle(i)}_{Z}(x)$ we get that $\pi^{\scriptscriptstyle(i)}_{Z}(x) -  \sigma^{\scriptscriptstyle(i)}_{2}  = \frac{\sigma^{\scriptscriptstyle(i)}_{2}}{2}R(x) + o(\rho(x)^{2})$.
Reconsidering the formula above,
{\small
\begin{align*}
 \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) & =  \\ 
& \hspace{-2.5cm}\mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1-R_1(x)} W \geq 0\right\}} \right. \right. \nonumber \\
& \left. \left. \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_2(x)} } \right)  \right. \right. \right. \nonumber \\
&\left. \left. \left. - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_2(x)} } \right)  \right) \right. \right. \nonumber \\
&   \left. \left. + \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)} W \leq 0\right\}} \right. \right. \nonumber\\
& \left. \left.\left(\Phi\left( \frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_1(x)} }   \right)  \right. \right. \right. \nonumber \\
& \left. \left. \left. - \Phi\left( \frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_1(x)} }\right)\right)\right)\right) \\
& \hspace{-2.5cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}}\left(\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \right.\right.\\
& \left. \left. \hspace{2cm} + \mathbbm{1}_{\left\{ W \leq 0\right\}} \left(\Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s +\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right)\right) \right).
\end{align*}
}To simplify the expression let us first get ride off all the second order degree terms (\textit{i.e.} $o(\rho(x)^{2})$), and now we consider the first part of the equation
{\small
\begin{align*}
\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} + o(\rho(x))\right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} + o(\rho(x))\right) & = \\
& \hspace{-17cm}  \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) - \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)- \left(\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}}V\right)\Phi'\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}}\right)\\ 
& \hspace{-15cm} + \left(\frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle(i)}_{2}\sigma_1} U + \frac{2S\rho(x + e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}}\right) + o\left(\rho(x)\right) 
\end{align*}
}
Considering the whole expression again, we would get 
{\tiny
\begin{align*}
\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{ \sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right)  \right)  \nonumber \\
& \hspace{-14cm} -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \\
& \hspace{-15cm}= \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) - \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)- \left(\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)\right.\\ 
& \hspace{-14cm}\left. + \left(\frac{2\Delta \rho(x+e_i) }{\sigma_2\sigma_1} U + \frac{2S\rho(x + e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) + o\left(\rho(x)\right)\right)  -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right)\\
& \hspace{-15cm}\leq \frac{1}{\sqrt{2\pi}^3} \int \int \int \left(\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}w \geq 0\right\}}\mathbbm{1}_{w \leq 0} + \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x) v +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}w \leq 0\right\}}\mathbbm{1}_{w \geq 0}\right)e^{-u^2/2}e^{-w^2/2}e^{-v^2/2}dudvdw \\
& \hspace{-13cm} + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
& \hspace{-15cm}\leq \frac{1}{2\pi} \int \int \left(\left(\Phi\left(0\right) - \Phi\left(\frac{- \alpha^{\scriptscriptstyle(i)}_{U}(x)u -  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\right)\right)\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \geq 0\right\}} + \left(\Phi\left(\frac{- \alpha^{\scriptscriptstyle(i)}_{U}(x)u -  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\right) - \Phi\left(0\right)\right)\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \leq 0\right\}}\right)\\
&  \hspace{-13cm}e^{-u^2/2}e^{-v^2/2}dudv + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
& \hspace{-15cm}\leq \frac{1}{2\pi}\int\int\frac{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\left(\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \geq 0\right\}} - \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \leq 0\right\}} \right)e^{-u^2/2}e^{-v^2/2}dudv \\
& \hspace{-13cm} + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
& \hspace{-15cm} \leq \frac{1}{2\pi}\int\int\frac{\left| \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v\right|}{\sigma_1}e^{-u^2/2}e^{-v^2/2}dudv + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
& \hspace{-15cm} \leq \mathbb{E}\left(\left|\frac{\Delta\rho(x+e_i) -\Delta \rho(x)}{(\sigma_1)^2}U +\frac{S\rho(x+e_i)-S\rho(x)}{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right)
\end{align*}
}Using the fact that $\Delta\rho(x+e_i), \Delta\rho(x), S\rho(x+e_i), S\rho(x)  \sim \rho(x)$. Let $C =~\frac{1}{2}\left( \frac{2}{(\sigma_1)^2} + \frac{6}{\sigma_{1}\sigma_2} + \frac{4}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}\right)$ 
Thus, 
{\tiny
\begin{align*}
\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right)  \right)  \nonumber \\
& \hspace{-14cm} -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \\
& \hspace{-15cm} \leq C|\rho(x)|
\end{align*}} Thus {\small
\begin{align*}
|\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| \leq 2C|\rho(x)|
\end{align*}}
Considering $R$ the residue of the sum in the covariance
\begin{align*}
|R_{m}| & \leq 4\sum_{x_{\scriptscriptstyle 1} = m}^{\infty}\sum_{x_{\scriptscriptstyle 2}= m}^{\infty}\left(m - x_{1}\right)\left(m - 1- x_{2}\right)|\rho(x)| \\
& \hspace{1cm}+ \sum_{x_1 = m}^{infty} \sum_{x_2=m}^{\infty}\left(m-x_1-1\right)\left(m-x_2\right)|\rho(x)| \\
& \hspace{1cm}+ \sum_{x_1 = m}^\infty \sum_{x_2= -\infty}^{\scriptscriptstyle -m}\left(m-x_1-1\right)\left(m+x_2-1\right)|\rho(x)|\\
& \hspace{1cm}+ \sum_{x_1 = -\infty}^{-m} \sum_{x_2=m}^{\infty}\left(m+x_1\right)\left(m-x_2\right)|\rho(x)|\\
& \hspace{1cm}+ \sum_{x_1 = -\infty}^{-m} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m+x_1\right)\left(m+x_2-1\right)|\rho(x)|
\end{align*}
Then, normalizing properly to have a convergent perimeter, we get that the residue of the sum is bounded by  
\begin{align*}
\frac{|R_{m}|}{m^2} & \leq 4C\sum_{x_{\scriptscriptstyle 1} = m+1}^{\infty}\sum_{x_{\scriptscriptstyle 2}= m+1}^{\infty}|\rho(x)| 
\end{align*}
thus, a sufficient condition on the covariance structure of the field is that~$\sum_{x \in \mathbb{Z}^{2}} |\rho(x)| <~\infty$.

~\\
Now, that we know more about how the covariance behave, we can construct a central limit theorem that will lead us to an isotropy test, the first CLT that we will propose follows the same idea as in \cite{Psymetrie}
\vspace{-0.5cm}{}
\subsection{Isotropy test using the oriented perimeter}
\begin{Theorem}(Multi-directional multivariate CLT for r-threshold). Let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, 
\begin{equation*}
m\left(\begin{pmatrix} \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
\end{equation*}
where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star$ given by
\begin{align*}
\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(m\check{\mathcal{P}}^{\scriptscriptstyle (i)}_{m}(t_{l}), m\check{\mathcal{P}}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
\end{align*}
\end{Theorem}
\begin{proof}
Following the idea that has been presented in \cite{Psymetrie}, 
starting with the well known Cram\`{e}r-Wold method. For the sake of completeness we recall it below.
\begin{Theorem}[Cram\`{e}r-Wold method, see, \textit{e.g.},  \cite{Billingsley}, p. 383]\label{Cramerwold}
Let $\overline {X}^{\scriptscriptstyle m} = (X^{m}_{\scriptscriptstyle 1}, \cdots, X^{m}_{\scriptscriptstyle r})$ and $\overline {X} = (X_{\scriptscriptstyle 1}, \cdots, X_{\scriptscriptstyle r})$ be random vectors of dimension $r \geq 1$. Then, $\overline {X}^{\scriptscriptstyle m}$ converges in distribution to $\overline {X}$ if and only if
\begin{center}
$\sum_{i = 1}^{r} a_{i}X_{i}^{m} \xrightarrow[m \to + \infty]{d} \sum_{i = 1}^{r} a_iX_i,$\end{center}
for each $(a_1, \cdots, a_r) \in \mathbb{R}^{r}$, \textit{i.e.}, if every fixed linear combination of the coordinates of $\overline{X}^{m}$ converges in distribution to the correspondent linear combination of coordinates of $\overline {X}$.
\end{Theorem}
We first need to recall some notations that were introduced in the first section \eqref{fi}. Let $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$  for $i \in \{1,2\}$,  $a^{\scriptscriptstyle (i)}_{1}, \ldots, a^{\scriptscriptstyle (i)}_{r} \in \mathbb{R}$, $t^{\scriptscriptstyle (i)}_{1}, \ldots, t^{\scriptscriptstyle (i)}_{r} \in \mathbb{R}$, $x \in G_{m}$ and $j \in \{1,\ldots,r\}$.  We recall as introduced in \eqref{fi}
\begin{align*}
f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t_j \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
\end{align*}
Note that $0 \leq f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) \leq 1$ \textit{a.s.} and $|f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x))| \leq 1$, \linebreak thus $|\sum^{2}_{i = 1}\sum_{j=1}^{r} a^{\scriptscriptstyle (i)}_j(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x)))| \leq \sum_{i = 1}^{2}\sum_{j =1}^{r} |a^{\scriptscriptstyle (i)}_j|$.
We note
\begin{equation}
\label{X}
W_{x}^{m} =~\cfrac{1}{m}\sum_{j = 1}^{r}a^{\scriptscriptstyle (1)}_j\big[f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (1)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (1)}(x))) \big] + a^{\scriptscriptstyle (2)}_j\big[f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (2)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (2)}(x))) \big] ,
\end{equation}
and finally,
\begin{equation*}
S_m = \sum_{x: w_{i}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} W_{x}^{m} = \cfrac{1}{m}\sum_{j = 1}^{r}a^{\scriptscriptstyle (1)}_j(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) - \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j))) + a^{\scriptscriptstyle (2)}_j(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) - \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j))) .
\end{equation*}
Using the Cram\`{e}r-Wold method, we need to prove that
\vspace{-0.2cm}
\begin{equation*}
S_{m} \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0, \, (\sigma^{\star}_{r})^{2} \right),
\end{equation*}
with $(\sigma^{\scriptscriptstyle \star}_{r})^{ \scriptscriptstyle 2} = \sum^{2}_{k = 1}\big[\sum_{j = 1}^{r}(a^{\scriptscriptstyle (k)}_{j})^{2}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(j,j) +  \sum_{0 \leq i < j \leq r} 2a^{\scriptscriptstyle (k)}_{i}a^{\scriptscriptstyle (k)}_{j}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(i,j)\big] + \sum_{0 \leq i < j \leq r}   2a^{\scriptscriptstyle (1)}_{i}a^{\scriptscriptstyle (2)}_{j}(\Sigma_{r}^{\scriptscriptstyle (1, 2)})^{\star}(i,j)$ with . To this purpose we use the following weaker version of Theorem 1 of \cite{Lothar} for bounded variables (see p.200 in \cite{Lothar} for details).
\begin{Proposition}
\label{tclbis}
Let $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ for $i \in \{1,2\}$ and $\{X^{m}_{x}, x \in G_{m}\}$ be a sequence of $D$\hspace{-0.05cm}-dependent random field, and $S_m = \sum_{x \in G_{m}} X^{m}_{x}$. If the following three conditions are satisfied:
\begin{enumerate}
\item[(i)]  $\forall \epsilon > 0$, $\sum_{x \in G_m} \mathbb{P}(|X^{m}_{x}| \geq \epsilon) \xrightarrow[m \to  \infty]{} 0 $,
\item[(ii)] $\sum_{x \in G_m} \mathbb{E}((X^{m}_{x})^{2}) \leq C < + \infty$,
\item[(iii)] $\mathbb{E}(S_m) \xrightarrow[m \to  \infty]{} 0$ and $\text{Var}(S_m) \xrightarrow[m \to  \infty]{} \sigma^{2}$ with $\sigma^{2} \in (0,\infty)$,
\end{enumerate}
then, $S_m\xrightarrow[m \to  \infty]{d} \mathcal{N}(0, \sigma^{2})$.
\end{Proposition}
We start by showing that $\{W^{m}_{x}, x \in G_{m}\}$ satisfies \textit{(i)}. For $\epsilon > 0$, we get~that,
\begin{align*}
\sum_{x \in G_m} \mathbb{P}\left(\big|W_{x}^{m}\big| \geq \epsilon\right) & \leq \sum_{x \in G_m}  \cfrac{\mathbb{E}(\big|W_{x}^{m}\big|^{3})}{\epsilon^{3}} \\
& \leq \cfrac{\left(\sum_{j=1}^{r}|a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{3}\times m(m-1)}{(m\epsilon)^3} \xrightarrow[m \to \infty]{}  0.
\end{align*}
To prove that $\{W^{m}_{x}, x\in G_{m}\}$ satisfies \textit{(ii)}, we write
\begin{align*}
\sum_{x \in G_m} \mathbb{E}\left(\left(W_{x}^{m}\right)^{2}\right) & \leq m(m-1) \left(\cfrac{1}{m} \sum_{j = 1}^{r} |a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{2}  \leq \left( \sum_{i = 1}^{r} |a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{2}.
\end{align*}
For \textit{(iii)} we observe that $\text{Var}(S_m) = \text{Var}\left( \sum^{r}_{j = 1}\frac{a^{\scriptscriptstyle (1)}_j}{m}\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) +\frac{a^{\scriptscriptstyle (2)}_j}{m}\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) \right)$ thus, as $m \to \infty$,
$\text{Var}\left( \sum^{r}_{j = 1}\frac{a^{\scriptscriptstyle (1)}_j}{m}\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) +\frac{a^{\scriptscriptstyle (2)}_j}{m}\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) \right) \rightarrow \sum^{2}_{k = 1}\big[\sum_{j = 1}^{r}(a^{\scriptscriptstyle (k)}_{j})^{2}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(j,j) +  \sum_{0 \leq i < j \leq r} 2a^{\scriptscriptstyle (k)}_{i}a^{\scriptscriptstyle (k)}_{j}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(i,j)\big] + \sum_{0 \leq i < j \leq r}   2a^{\scriptscriptstyle (1)}_{i}a^{\scriptscriptstyle (2)}_{j}(\Sigma_{r}^{\scriptscriptstyle (1, 2)})^{\star}(i,j)$.
\end{proof}
In order to establish the isotropy test,we only need the CLT on the behavior of $ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t)$ and $ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)$ at level $t$. Thus, we will show another central limit theorem with lesser conditions on the covariance structure $\rho$ of the field $X$.
\begin{Theorem}(Multi-directional CLT at level $t$). Let $t \in \mathbb{R}$ , $m \geq 2$, then
\begin{equation*}
m\left(\begin{pmatrix} \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t) \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t))  \\\mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right),
\end{equation*}
where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right)$ for the $2$-dimensional centered Gaussian distribution with covariance matrix $\Sigma_{2}^\star$ given by
\begin{align*}
\Sigma^{\star}_{2}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(m\check{\mathcal{P}}^{\scriptscriptstyle (i)}_{m}(t), m\check{\mathcal{P}}^{\scriptscriptstyle (j)}_{m}(t) \right)
\end{align*}
\end{Theorem}
For the proof of this Theorem we refer the reader to \cite{RVY}.
\paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.

Let us consider the null hypothesis
\begin{center}
  $H_{0}$ \, :\; The field $X$ is isotropic,
\end{center}
and consider the following normality asymptotic result.

\begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
Let  $t \in \mathbb{R}$, and $\check{\mathcal{P}}^{\scriptscriptstyle  (i) }(\cdot)$ be the scaled oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre} computed at level $t$. Then, it holds that,
\begin{equation*}
m\left(\cfrac{\check{\mathcal{P}}^{\scriptscriptstyle  (1) }_{m}(t)}{\check{\mathcal{P}}^{\scriptscriptstyle  (2)}_{m}(t)} - \cfrac{\mathbb{E}\left(\check{\mathcal{P}}^{\scriptscriptstyle  (1) }_{m}(t)\right)}{\mathbb{E}\left(\check{\mathcal{P}}^{\scriptscriptstyle  (2)}_{m}(t)\right)} \right)  \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t) \right),
\end{equation*}
with $\tilde{\sigma}^{2}(t) = \frac{\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t)(\mu^{\star}_{2}(t))^{2} - 2\mu^{\star}_{2}(t)\mu^{\star}_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t) +\tilde{\sigma}_{\scriptscriptstyle 2,2}^{2}(t)\mu^{\star}_{1}(t))^{2}}{\mu^{\star}_{2}(t)^4}$
Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\check{\mathcal{P}}^{\scriptscriptstyle  (1) }(t)}{\check{\mathcal{P}}^{\scriptscriptstyle  (2) }(t)}$. Then, under $H_{0}$, it holds that
\begin{equation}\label{ratiounderH0}
m\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
\end{equation}
and $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu^{\star}_{2}(t)^2}$
\end{Proposition}
Consider the consistent empirical estimator $\hat{\sigma}(t):= m^{2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m}(t)\right)}$ is the empirical variance of the considered ratio. Then, from \ref{deltamethodgeneralprop}, it holds that 
$$ \frac{m}{\sqrt{\hat{\sigma}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$. We define the symmetric accessible test $\hat{\phi}(t)_{m}$ with asymptotic level $\alpha$ as 
\begin{equation}
\label{phihat}
\hat{\phi}(t)_{m}= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|\left(R_{m}(t) - 1 \right)\right| \geq q_{1- \frac{\alpha}{2}} \right\}}
\end{equation}
\section{Numerical studies}

\subsection{Numerical studies of moments of the estimated perimeter}

Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/3C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
\begin{equation}
A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
\end{equation}
with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{X}(x) = (1 -3||Ax||_{2}/3C + (||Ax||_{2}/2C)^{3})\mathbbm{1}_{||Ax||_{2} < C},$, note that $a\neq b$ if and only if $Y$ is anisotropic. We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$. 
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
    \hspace{0.2cm}
 \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$. }
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
    \hspace{0.2cm}
 \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ and $C = 40$.}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{ThreeConfNew.pdf}}
    \hspace{0.2cm}
 \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1,-1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$. }
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{fourConfNew.pdf}}
    \hspace{0.2cm}
 \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1, 1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$. }
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{Variance_40.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40$. }
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{Testanisotropy2.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$in blue color for a Montecarlo $= 2000$, and $C = 40$.}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiovsRHO.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, and $C = 40$.}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{imageU.pdf}}
    \hspace{3cm}
    {\includegraphics[scale=0.3]{levelset30000.pdf}}
    \hspace{0.2cm}
 \caption{ Image of level $30000$}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.25]{ConfidenceIntervalRDStD.pdf}}
    {\includegraphics[scale=0.25]{BoxplotRDStD.pdf}}
    \hspace{0.2cm}
 \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
\label{fig2}
\end{figure}

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.25]{ConfidenceIntervalRDAu.pdf}}
    {\includegraphics[scale=0.25]{BoxplotRDAu.pdf}}
    \hspace{0.2cm}
 \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
\label{fig2}
\end{figure}
\bibliographystyle{plain}
\bibliography{biblioLKC}
\end{document}

### 2022-10-21 Draft_GFC.tex
Version 21 octobre recup version final

@@
 \begin{equation*}
-m\left(\begin{pmatrix} \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
+\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
 \end{equation*}
@@
 \begin{align*}
-\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(m\check{\mathcal{P}}^{\scriptscriptstyle (i)}_{m}(t_{l}), m\check{\mathcal{P}}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
+\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
 \end{align*}
@@
 \end{proof}
-In order to establish the isotropy test,we only need the CLT on the behavior of $ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t)$ and $ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)$ at level $t$.
-Thus, we will show another central limit theorem with lesser conditions on the covariance structure $\rho$ of the field $X$.
+In order to establish the isotropy test,we only need the CLT on the behavior of $ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t)$ and $ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)$ at level $t$.To get this result we just need to assume that the field has a covariance kernel is exponentially decaying.
+
 \begin{Theorem}(Multi-directional CLT at level $t$). Let $t \in \mathbb{R}$ , $m \geq 2$, then
 \begin{equation*}
-m\left(\begin{pmatrix} \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t) \\ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t))  \\\mathbb{E}(\check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right),
+\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)  \\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right),
 \end{equation*}
@@
 \begin{align*}
-\Sigma^{\star}_{2}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(m\check{\mathcal{P}}^{\scriptscriptstyle (i)}_{m}(t), m\check{\mathcal{P}}^{\scriptscriptstyle (j)}_{m}(t) \right)
+\Sigma^{\star}_{2}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t), \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t) \right)
 \end{align*}
 \end{Theorem}
-For the proof of this Theorem we refer the reader to \cite{RVY}.
+For the proof of this Theorem the main ingredients can be found in \cite{RVY}.
+\begin{proof}
+\begin{Theorem}(CLT for exponentially quasi-local statistics of clustering spin clusters models) Let $G$ be a discrete Cayley graph (basically $\mathbb{Z}^{2}$) and together with $(\epsilon, \mathcal{P})$: if $G$ is $b$-amenable, $\mathcal{P}$ is a clustering spin model with summable $\Phi$, $\left(\sum_{x \in V}\Phi^{1/p}(c|x|) = \sum_{n \geq 0} |\partial W_n| \phi^{1/p}(cn) < \infty \right)$ and $\epsilon$ is a local score function.
+Then you get the CLT.
+\end{Theorem}
+\begin{Corollary}
+Let $\mathcal{H}$ be a stationnary Gaussian field, on a discrete Cayley graph $G$ with $X(0)$ having unit variance.
+the level set $\mathcal{P}_{u}$ satisfy exponential clustering constant $C = 2^{12/5}k^{8/5}$, $c_{k} = 1$ and clustering function $\Phi(t) = w(O,x)$.
+\end{Corollary}
+\begin{Definition}
+\end{Definition}(Clustering spin models) We say that $\mathcal{P}$ is a clustering spin model if for all $p,q \geq 1$ there exists constant $C_{p+q}, c_{p+q}$ and a fast decreasing function $\Phi$ ($\Phi \leq 1$,  decreasing and $\lim_{s \to \infty}s^{m}\Phi(s) = 0$ for all $m\geq 1$) such that for all distinct $x_{1}, \ldots, x_{p+q} \in V$ (vertices) we have
+$$|\mathbb{P}\left(\{x_{1}, \ldots, x_{p+q}\} \subset \mathcal{P}\right) - \mathbb{P}\left(\{x_{1}, \ldots, x_{p}\}\subset \mathcal{P}\right)\mathbb{P}\left(\{x_{p+1}, \ldots, x_{p+q}\}\subset \mathcal{P}\right)| \leq C_{p+q}\Phi\left(c_{p+q}s\right)$$
+where $s = d\left(\{x_{1}, \ldots, x_{p}\}, \{x_{p+1}, \ldots, x_{p+q}\}\right)$
+$\rightarrow$ A spin model $\mathcal{P}$ is said to be \textbf{exponentially} if $\mathcal{P}$ is a \textbf{clustering spin} model with $c_{k} \geq c > 0$ and $C_{k} = O(k^{ak})$ for some $a \in [0,1)$and the clustering function satisfies the growth condition $\lim\sup_{t\to \infty}\frac{\log\Phi(t)}{t^{b}} < 0$.
+\end{proof}
 \paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.
@@
 \begin{equation*}
-m\left(\cfrac{\check{\mathcal{P}}^{\scriptscriptstyle  (1) }_{m}(t)}{\check{\mathcal{P}}^{\scriptscriptstyle  (2)}_{m}(t)} - \cfrac{\mathbb{E}\left(\check{\mathcal{P}}^{\scriptscriptstyle  (1) }_{m}(t)\right)}{\mathbb{E}\left(\check{\mathcal{P}}^{\scriptscriptstyle  (2)}_{m}(t)\right)} \right)  \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t) \right),
+\frac{1}{m}\left(\cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)} - \cfrac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)} \right)  \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t) \right),
 \end{equation*}
 with $\tilde{\sigma}^{2}(t) = \frac{\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t)(\mu^{\star}_{2}(t))^{2} - 2\mu^{\star}_{2}(t)\mu^{\star}_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t) +\tilde{\sigma}_{\scriptscriptstyle 2,2}^{2}(t)\mu^{\star}_{1}(t))^{2}}{\mu^{\star}_{2}(t)^4}$
-Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\check{\mathcal{P}}^{\scriptscriptstyle  (1) }(t)}{\check{\mathcal{P}}^{\scriptscriptstyle  (2) }(t)}$. Then, under $H_{0}$, it holds that
+Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }(t)}$. Then, under $H_{0}$, it holds that
 \begin{equation}\label{ratiounderH0}
-m\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
+\frac{1}{m}\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
 \end{equation}
@@
 \end{Proposition}
-Consider the consistent empirical estimator $\hat{\sigma}(t):= m^{2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m}(t)\right)}$ is the empirical variance of the considered ratio.
+Consider the consistent empirical estimator $\hat{\sigma}(t):= \frac{1}{m^2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m}(t)\right)}$ is the empirical variance of the considered ratio.
 Then, from \ref{deltamethodgeneralprop}, it holds that
-$$ \frac{m}{\sqrt{\hat{\sigma}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
+$$ \frac{1}{m\sqrt{\hat{\sigma}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
 Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$.

### 2022-10-21 Draft_GFC.tex
added figures

@@
 \begin{remark}
+\label{decreasingrho}
 Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 
 \begin{equation*}
- \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right).
+ \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right).
 \end{equation*}
-Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the normalized perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
+Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
 \end{remark}
 \begin{proof}
-Note that $\rho \mapsto \sqrt{1-\rho}$ is decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also decreasing.
+Note that $\rho \mapsto \sqrt{1-\rho}$ is strictly decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing.
 \end{proof}
@@
 \begin{Corollary}
-Let $\mathcal{H}$ be a stationnary Gaussian field, on a discrete Cayley graph $G$ with $X(0)$ having unit variance.
+Let $\mathcal{H}$ be a stationary Gaussian field, on a discrete Cayley graph $G$ with $X(0)$ having unit variance.
 the level set $\mathcal{P}_{u}$ satisfy exponential clustering constant $C = 2^{12/5}k^{8/5}$, $c_{k} = 1$ and clustering function $\Phi(t) = w(O,x)$.
@@
 \end{equation}
+\begin{remark}(Power of the statistical test for the level $t = 0$) In Remark \ref{decreasingrho} we showed that the function $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(0)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(0)\right)} \neq 1$.
+\end{remark}
 \section{Numerical studies}
-
 \subsection{Numerical studies of moments of the estimated perimeter}
@@
     \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$in blue color for a Montecarlo $= 2000$, and $C = 40$.}
+ \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
 \label{fig2}
@@
   \centering
-    {\includegraphics[scale=0.4]{TestaniRatiovsRHO.pdf}}
+    {\includegraphics[scale=0.2]{TestaniRatiovsRHO.pdf}}
+    {\includegraphics[scale=0.2]{TestaniRatiovsTVA.pdf}}
     \hspace{0.2cm} 
- \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, and $C = 40$.}
+ \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
 \label{fig2}

### 2022-10-27 Draft_GFC.tex
version 27/10

@@
 \end{remark}
+\begin{remark}
+the function $t \mapsto \mathbb{E}\left(f^{(i)}(t) \right)$ is even.
+\end{remark}
 \begin{proof}
@@
 \begin{remark}
-In order to have convergence when $m \to \infty$, one has to consider the normalise perimeter with the area of the window ($m^2$).
+In order to have convergence when $m$ goes to infinity, one has to consider the normalised perimeter with the area of the window ($m^2$).
 \end{remark}
@@
 Note that $\rho \mapsto \sqrt{1-\rho}$ is strictly decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing.
+\end{proof}
+\textcolor{blue}{Decreasing behavior for all level $t$.}
+\begin{remark}
+Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 
+\begin{equation*}
+ \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
+\end{equation*}
+Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
+\end{remark}
+\begin{proof}
+Let $x\in(-1,1)$ and $f: x \mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ we consider $a,b  \in (-1,1)$, such that $a > b$,
+{\tiny
+\begin{align*}
+f(a) - f(b) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)- \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) \\
+= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) \\
+= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0} \\
+= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0}
+\end{align*}}
+Thus if $a > b$
+{\tiny
+\begin{align*}
+\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) <  \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)
+\end{align*}}
+
 \end{proof}
@@
   \centering
-    {\includegraphics[scale=0.3]{Variance_40.pdf}}
+    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
     \hspace{0.2cm}

### 2022-10-31 Draft_GFC.tex
Last version  31/10

@@
 \end{cases}
-\end{equation*}
-% where $b_{i} = \begin{cases}0 \; \text{if} \; \gamma = 0 \\ 1 \; \text{else} \end{cases}$, for each sample $\Gamma_{1}, \ldots, \Gamma_{d}$ they determine a mean vector of length $r$ and mean angle $\hat{\Phi}$, (They just sample from the same image $Z_{l,l}$...).
-They use the standard ellipse to analyses these statistics.
-Hum this is what they say about this \textit{The tips of the vectors of a second order
-% sample form a scatter diagram of data with
-% standard deviations in the $X$ and $Y$ directions and a
-% certain trend upward or downward. The standard ellipse
-% describes this behavior in a condensed way: assuming
-% normality, roughly $40\%$ of data points fall inside the
-% ellipse and $60\%$ of them outside. The parent population
-% does not need to be normal, although it is desirable that
-% it does not deviate from normality too much.}
-% They define the standard ellipse in the following way
-% \begin{itemize}
-%   \item its center $(\hat{x}, \hat{y})$ \\
-%   \item Construct a rectangle with center at $(\hat{x}, \hat{y})$ and sides parallel to the $X$ and $Y$ axes.. 
-%   \item the standard ellipse is embedded in the rectangle above (see the article for more details on the construction). 
-  % \end{itemize}
+\end{equation*}We debi
 By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$.
@@
 Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares.
-We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ and for $x \in G_{m}$, we define $C_{m}(x)$ as
+We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in G_{m}$, we define $C_{m}(x)$ as
 \begin{equation*}
@@
 \draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
-\foreach \x in {0,1,2,3,4}{
-  \foreach \y in {0,1,2,3,4}{
+\foreach \x in {0,1,2,3}{
+  \foreach \y in {0,1,2,3}{
   \draw[fill = red] (\x,\y) circle (2pt);
@@
     \vspace{-2cm}
- \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, Using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
+ \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
 \label{fig22}
@@
 \begin{Definition}[Perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
-For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{x: w_{i}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$.
+For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$.
 Then, the perimeter of the binary image $Z$ is given by
@@
 \label{propFisrtmoment}
-We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field and $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ with $\rho(e_i) \in [-1, 1]$.
-The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)\right) + \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)$  and
-if $\rho(e_{i}) \in ]-1,1]$, 
+We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
+The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and
+\begin{itemize}
+  \item if $\rho(e_{i}) \in ]-1,1]$, 
     {\small
@@
 with $N \sim \mathcal{N}(0,1)$. 
+\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$
+  \end{itemize}
 \end{Proposition}
-\begin{remark}(degenerative case)
-If  $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$
-\end{remark}
-\begin{remark}
-the function $t \mapsto \mathbb{E}\left(f^{(i)}(t) \right)$ is even.
-\end{remark}
+\textcolor{blue}{\begin{remark}
+Note that $\mathbb{E}\left(f^{(i)}(t) \right) = 0$ in the case where $\rho(e_i) = 1$ 
+\end{remark}}
 \begin{proof}
-Let us start with the case where $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since
-\begin{align*}
-\left\{ x \in G_{m}; w_{i}(x) \subset (0,m)^{2}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
+Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since
+\begin{align*}
+\left\{ x \in G_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
 & = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},
@@
 one can write that, 
-\begin{equation}
+\begin{equation*}
 \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right).
 \label{covarianeproof}
-\end{equation}
+\end{equation*}
  with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. \\
- We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation}
-The covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
+ We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation*}
+Let us introduce the following Lemma, 
+\begin{Lemma}
+\label{lemmasommediff}
+Let $a,b,t \in \mathbb{R}$, then 
+$$\min(a,b) \leq t \leq \max(a,b) \iff\left|t - \frac{a+b}{2}\right| \leq \left| \frac{ b-a }{2}\right| $$
+\end{Lemma}
+\begin{proof}
+\begin{align*}
+\min(a,b) \leq t \leq \max(a,b) & \leftrightarrow \min(0, b - a) \leq t - a \leq \max(0, b - a) \\
+& \iff \min(0, b - a) \leq t + \frac{b-a - (b+a)}{2} \leq \max(0, b - a) \\
+& \iff\min(- \frac{b-a}{2}, \frac{b - a}{2}) \leq t -\frac{b+a}{2} \leq \max(- \frac{b-a}{2}, \frac{b-a}{2}) \\
+& \iff - \frac{\left|b-a\right|}{2} \leq t -\frac{b+a}{2} \leq + \frac{\left|b-a\right|}{2} \\
+& \iff \left|t -\frac{b+a}{2}\right| \leq \frac{\left|b-a\right|}{2}
+\end{align*}
+\end{proof}
+Thus, applying the Lemma we get 
+{\small
+\begin{align*}
+\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
+\end{align*}}Besides, the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
 -1 & 1 \\
@@
 \end{pmatrix}.$ \\
-Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_1)  \end{pmatrix}$, which directly  implies that the two variables are independent.
-{\small
-\begin{align*}
-\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
-&= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_i} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_i}-X_{0})\right\}}\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0})\right\}}\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}}{2})\right\}}\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right).
-\\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}  \leq Y \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right)
-\end{align*}}  
-with $N, Y \sim \mathcal{N}(0,I_{2})$, thus 
+Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent, we get the following system
+$\left\{
+ \begin{array}{rlc}
+  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \textcolor{white}{(1-\rho(e_i))U + }\\
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \textcolor{white}{(1-\rho(e_i))U + } \sqrt{2(1+\rho(e_i)}V, 
+\end{array}
+\right.$
+{\small
+\begin{align*}
+\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq 2t - \sqrt{2(1+\rho(e_i)}V \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}  \leq V \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right), 
+\end{align*}}  
+with $U, V \sim \mathcal{N}(0,I_{2})$, thus 
 $$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
@@
 \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\
-& \hspace{-6cm}= \mathbb{P}\left(-|N| < t \leq |N|\right) = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{-z < t \leq z\right\}} e^{-\frac{z^2}{2}}dz  = \cfrac{2}{\sqrt{2\pi}} \int_{\scriptscriptstyle 0}^{+\infty} \mathbbm{1}_{\left\{t \leq z\right\}} e^{-\frac{z^2}{2}}dz \\
-& \hspace{-6cm}= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).
+& = \mathbb{P}\left(|t| \leq |N|\right) = 2\left(1 - \Phi\left(|t|\right)\right).
 \end{align*}
@@
 Note that this result extends those given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 
-
 \begin{remark}
@@
 \end{remark}
-The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$.
+The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$ .
 \begin{Proposition}
@@
 \begin{remark}
-The first moment of the total variation is given by the sum over the two directions of Equation \eqref{totalvariation}. 
+Using this result, one can define an estimator for $\rho(e_i)$. 
 \end{remark}
 \begin{remark}
-Using this result, one can define an estimator for $\rho(e_i)$. 
-\end{remark}
-Study of the behavior of the nodal curve $t = 0$, 
-\begin{remark}
 \label{decreasingrho}
-Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 
+Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter of the nodal curve ($t=0$).
 \begin{equation*}
- \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right).
+ \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right),
 \end{equation*}
-Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
+where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
 \end{remark}
 \begin{proof}
-Note that $\rho \mapsto \sqrt{1-\rho}$ is strictly decreasing similarly  for level $0$, one has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - 1$, since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing.
+One has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) -~1$.
+Since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing.
 \end{proof}
@@
 \begin{remark}
-Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result 
+Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter at level $t$:
 \begin{equation*}
@@
 \end{align*}}
-
 \end{proof}
@@
 Let $s, t \in \mathbb{R}$ such that $t \leq s$.
-Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
+Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
 \begin{Lemma} 
@@
 \begin{align}
-\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + 2\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .
+\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \\
+& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .
 \label{covariance}
@@
 \begin{proof}
-To simplify the notations, we chose to do the computations for direction $i =1$.
 Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 
 \begin{align*}
-\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))& = \text{Cov}\left( \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}}f_{t}^{\scriptscriptstyle (1)}(x), \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} f_{s}^{\scriptscriptstyle (1)}(y)\right) \\
-& = \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \sum_{y, w_{1}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right).
-\end{align*}
-By the stationarity hypothesis, one has $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right)= \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(y-x) \right)$.
-Then
-\begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right)
-\end{align*}
-for $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has
+\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))& = \sum_{x, w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle (1)}_{m}} \sum_{y, w_{1}(y) \in \mathbb{E}^{\scriptscriptstyle (1)}_{m}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right).
+\end{align*}
+By stationarity, one has $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(x), f_{s}^{\scriptscriptstyle (1)}(y) \right)= \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(y-x) \right)$,
+\begin{align*}
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).
+\end{align*}
+For $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has
 \begin{align*} 
@@
 \end{align*}
-Again, considering $z_1 = y_1 - x_1$
-\begin{align*} 
-\left\{
-\begin{array}{rcl}
-0 \leq x_1 \leq m-1 \\
-1 \leq y_1 \leq m-1 
-\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
-0 \leq x_1 \leq m-1 \hspace{0.7cm} \\
-1 -x_1 \leq z_1 \leq m- 1 - x_1
-\end{array}\right. \\
-& \implies  \left\{
-\begin{array}{rcl}
-2 - m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
-\max(0, 1-z_1) \leq x_1 \leq \min(m-1 , m-1-z_1),
-\end{array}\right.
-\end{align*} 
-and, $z_{2} = y_{2}-x_{2}$
-\begin{align*} 
-\left\{
-\begin{array}{rcl}
-1 \leq x_2 \leq m-1 \\
-0 \leq y_2 \leq m-1 
-\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
-1 \leq x_2 \leq m-1 \hspace{0.7cm} \\
--x_2 \leq z_2 \leq m- 1 - x_2
-\end{array}\right. \\
-& \implies  \left\{
-\begin{array}{rcl}
-1 - m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
-\max(1, -z_2) \leq x_2 \leq \min(m-1 , m-1-z_2)
-\end{array}\right..
-\end{align*} 
-Thus, 
+Again, considering $z_1 = y_1 - x_1$ and, $z_{2} = y_{2}-x_{2}$, we get
 \begin{align*}
@@
 & + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=1}^{m-1}\left(m+z_2\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
-& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m+z_2\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) 
+& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m+z_2\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) \\
+& = \sum_{z_1=2-m}^{m-1} \sum_{z_2 = 1-m}^{m-2} \left(m-|z_1| - \mathbbm{1}_{z_{1} \leq 0}\right)\left(m-|z_2|-\mathbbm{1}_{z_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)
 \end{align*}
 \end{proof}
-Getting the value of the covariance requires the computation of all the elements of the sum, let us first start with the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$,
+Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure.
+Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}.
+We get the next result.
 \begin{Lemma}
-The case $x=0$ is a special case, in order to compute it, we just have to apply the same strategy we used to compute the first moment in \ref{propFisrtmoment}, thus we get,
 \begin{align*}
 \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) \\
-& - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right).
-\end{align*}
-And, 
+& - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right),
+\end{align*}
+where, 
 {\small
@@
 \end{Lemma}
-\subsection{Three and four cells configuration}
 Figure \ref{configurations} shows the four types of configurations that are encountered in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma} depending on the orientation $i$ and position on the grid $x$.
@@
   \centering
+  \begin{tikzpicture}[scale = 1.5]
+\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
+\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
+\draw[step = 2cm, line width =0.5mm, blue] (1,0) -- (1,0.5);
+\draw[pattern=north east lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
+\draw[pattern=north west lines, pattern color=green, opacity=1] (0, 0) rectangle (0.5,0.5);
+\draw[pattern=north east lines, pattern color=red] (0.5, 0) rectangle (1,0.5);
+\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
+\end{tikzpicture}
 \begin{tikzpicture}[scale = 1.5]
@@
     \pi^{\scriptscriptstyle(i)}_{V}(x) & = & \frac{S \rho(x) + S\rho(x+e_i)}{\sigma_{2}} \\
-   \pi^{\scriptscriptstyle(i)}_{W}(x) & = & \frac{\rho(x)^{2} - \rho(x+e_i)^{2} + \rho(x-e_1)^{2} - \rho(x + e_i - e_1)^{2} - 2\rho(e_1)\left(\rho(x)\rho(x-e_1) - \rho(x+e_i)\rho(x+e_i-e_1)\right)}{(1-\rho(e_1)^{2})\alpha^{\scriptscriptstyle(i)}_{W}(x)}\\
+   \pi^{\scriptscriptstyle(i)}_{W}(x) & = & \frac{- \left(\alpha^{\scriptscriptstyle(i)}_{U}(x)\pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{V}(x)\pi^{\scriptscriptstyle(i)}_{V}(x)\right) }{\alpha^{\scriptscriptstyle(i)}_{W}(x)}\\
    \pi^{\scriptscriptstyle(i)}_{Z}(x)& = & \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}
@@
 \label{Thisthofour}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle 1}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \nonumber \\
-& \hspace{-5.4cm} \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \geq 0\right\}} \right.
+\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle 1}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}}\right.
+\\
+& \hspace{-6cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right) \right.
 \right.
 \nonumber \\
-& \hspace{-5cm}\left.
-\left.
-\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right.
-\right.
-\right.
-\nonumber \\
-& \hspace{-5cm}\left.
-\left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right) \right.
-\right.
-\nonumber \\
-&  \hspace{-5cm} \left.
-\left.
-+ \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 0\right\}} \right.
-\right.
-\nonumber\\
-& \left.
-\left.
-\hspace{-5cm}\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W   \right)  \right.
-\right.
-\right.
-\nonumber \\
-& \hspace{-5cm}\left.
-\left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right)\right)\right)\right),
+& \hspace{-4cm}\left.
+\left.
+- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right| \right)
 \end{align}
-}with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x))^{-2})$.
+}with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x))^{2})$.
 \item else, if $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, and $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0, S\rho(x) > 0$, $S\rho(x+e_i) > 0$ then, 

### 2022-11-11 Draft_GFC.tex
Courage

@@
 }
-
 \begin{document}
@@
 \end{Proposition}
-\textcolor{blue}{\begin{remark}
+\begin{remark}
 Note that $\mathbb{E}\left(f^{(i)}(t) \right) = 0$ in the case where $\rho(e_i) = 1$ 
-\end{remark}}
+\end{remark}
 \begin{proof}
@@
 \begin{proof}
-\begin{align*}
-\min(a,b) \leq t \leq \max(a,b) & \leftrightarrow \min(0, b - a) \leq t - a \leq \max(0, b - a) \\
-& \iff \min(0, b - a) \leq t + \frac{b-a - (b+a)}{2} \leq \max(0, b - a) \\
-& \iff\min(- \frac{b-a}{2}, \frac{b - a}{2}) \leq t -\frac{b+a}{2} \leq \max(- \frac{b-a}{2}, \frac{b-a}{2}) \\
-& \iff - \frac{\left|b-a\right|}{2} \leq t -\frac{b+a}{2} \leq + \frac{\left|b-a\right|}{2} \\
-& \iff \left|t -\frac{b+a}{2}\right| \leq \frac{\left|b-a\right|}{2}
-\end{align*}
+Let $a,b,t \in \mathbb{R}$,
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}[scale = 1.5]
+\draw (-1,0)--(9,0);
+\draw (0,-0.08)--(0,0.08);
+\draw (8,-0.08)--(8,0.08);
+\draw (2.5, -0.08) -- (2.5, 0.08);
+\draw (4, -0.08) -- (4, 0.08);
+\draw (0,0) node[below]{$\min(a,b)$};
+\draw (8,0) node[below]{$\max(a,b)$};
+\draw (4,0) node[below]{$\frac{b+a}{2}$};
+\draw (2.5,0) node[below]{$t$};
+\draw (2.5,-0.6) -- (4,-0.6);
+\draw (2.5, -0.6) -- (2.75,-0.5);
+\draw (2.5, -0.6) -- (2.75,-0.7);
+\draw (4, -0.6) -- (3.75,-0.5);
+\draw (4, -0.6) -- (3.75,-0.7);
+\draw (0,0.6) -- (8,0.6);
+\draw (0, 0.6) -- (0.25,0.5);
+\draw (0, 0.6) -- (0.25,0.7);
+\draw (8, 0.6) -- (7.75,0.7);
+\draw (8, 0.6) -- (7.75,0.5);
+\node[text width= 1.6cm, font=\large] at (4,1) {$\frac{|b-a|}{2}$};
+\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{b+a}{2}|$};
+\end{tikzpicture}
+\end{figure}
+
 \end{proof}
@@
 \begin{remark}
-In order to have convergence when $m$ goes to infinity, one has to consider the normalised perimeter with the area of the window ($m^2$).
+In order to have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window ($m^2$), considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.
 \end{remark}
@@
 \begin{align*}
-f(a) - f(b) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)- \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) \\
-= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) \\
-= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0} \\
-= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0}
+f(a) - f(b) = \mathbb{E}\left(\Phi_{\pi_{V}}\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(2t - \sqrt{2(1-b)}|N|\right)- \Phi\left(2t - \sqrt{2(1-a)}|N|\right)\right) \\
+= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right) \\
+= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0} \\
+= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0}
 \end{align*}}
@@
 \text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (i)}(s) \right) 
-& = \sum_{x_{\scriptscriptstyle 1}=\left(1-m\right)}^{m-1}\sum_{x_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|x_{1}|\right)\left(m - 1- |x_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (i)}(0), f_{s}^{\scriptscriptstyle (i)}(x) \right)
-\end{align*} 
-and 
-\begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{x_1 = 0}^{m-2} \sum_{x_2=1}^{m-1}\left(m-x_1-1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
-& + \sum_{x_1 = 0}^{m-2} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m-x_1-1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
-& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=1}^{m-1}\left(m+x_1\right)\left(m-x_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)\\
-& + \sum_{x_1 = -m+1}^{-1} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m+x_1\right)\left(m+x_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right) 
+& = \sum_{x_{\scriptscriptstyle j}=\left(1-m\right)}^{m-1}\sum_{x_{\scriptscriptstyle i}=\left(2-m\right)}^{m-2}\left(m -|x_{j}|\right)\left(m - 1- |x_{i}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (i)}(0), f_{s}^{\scriptscriptstyle (i)}(x) \right)
+\end{align*} 
+for $i,j \in\{1,2\}, i\neq j$, and 
+\begin{align*}
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) 
+& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} < 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)
 \end{align*}
@@
 \begin{proof}
-Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$ for $t \leq s$. 
+Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$, $i = 1$for $t \leq s$. 
 \begin{align*}
@@
 \begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 1}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).
-\end{align*}
-For $x_1 \in [0,m-1]$ and $z_1 = y_1 - x_1$ one has
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1}\sum_{y_1 = 0}^{m-2}\sum_{y_2 = 0}^{m-1} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (1)}(y-x) \right).
+\end{align*}
+For $x_1 \in [0,m-2]$ and $z_1 = y_1 - x_1$ one has
 \begin{align*} 
@@
 \begin{array}{rcl}
-0 \leq x_1 \leq m-1 \\
-0 \leq y_1 \leq m-1 
-\end{array}\right.& \implies  \left\{ \begin{array}{rcl}
-0 \leq x_1 \leq m-1 \hspace{0.7cm} \\
--x_1 \leq z_1 \leq m-1 - x_1
+0 \leq x_1 \leq m-2 \\
+0 \leq y_1 \leq m-2 
+\end{array}\right.& \Leftrightarrow  \left\{ \begin{array}{rcl}
+0 \leq x_1 \leq m-2 \hspace{0.7cm} \\
+-x_1 \leq z_1 \leq m-2 - x_1
 \end{array}\right. \\
-& \implies  \left\{
+& \Leftrightarrow  \left\{
 \begin{array}{rcl}
-1-m \leq z_1 \leq m-1 \hspace{2.5cm}  \\
-\max(0, -z_1) \leq x_1 \leq \min(m-1 , m-1-z_1)
+2-m \leq z_1 \leq m-2 \hspace{2.5cm}  \\
+\max(0, -z_1) \leq x_1 \leq \min(m-2 , m-2-z_1)
 \end{array}\right..
 \end{align*} 
-Similarly for $z_2 = y_2 - x_2$ and $x_2 \in [1, m-1]$
+Similarly for $z_2 = y_2 - x_2$ and $x_2 \in [0, m-1]$
 \begin{align*}
@@
 \begin{array}{rcl}
-2-m \leq z_2 \leq m-2 \hspace{2.5cm}  \\
-\max(1, 1-z_2) \leq x_2 \leq \min(m-1 , m-1-z_2).
+1-m \leq z_2 \leq m-1 \hspace{2.5cm}  \\
+\max(0, -z_2) \leq x_2 \leq \min(m-1 , m-1-z_2).
 \end{array}\right., 
@@
 \text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{x, w_{1}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \sum_{y, w_{2}(y) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)\\
-& =  \sum_{x_1 = 0}^{m-1}\sum_{x_2 = 1}^{m-1}\sum_{y_1 = 1}^{m-1}\sum_{y_2 = 0}^{m-1}\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)
+& =  \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1}\sum_{y_1 = 0}^{m-1}\sum_{y_2 = 0}^{m-2}\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(y-x) \right)
 \end{align*}
@@
 \begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{z_2 = 0}^{m-2} \sum_{z_1=1}^{m-1}\left(m-z_2-1\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
-& + \sum_{z_2 = 0}^{m-2} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m-z_2-1\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
-& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=1}^{m-1}\left(m+z_2\right)\left(m-z_1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
-& + \sum_{z_2 = -m+1}^{-1} \sum_{z_1=2-m}^{\scriptscriptstyle 0}\left(m+z_2\right)\left(m+z_1-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) \\
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) & = \sum_{z_1=1}^{m-1}\sum_{z_2 = 0}^{m-2}\left(m-z_1\right)\left(m-z_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
+& +  \sum_{z_1=2-m}^{\scriptscriptstyle 0}\sum_{z_2 = 0}^{m-2}\left(m+z_1-1\right)\left(m-z_2-1\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
+& +  \sum_{z_1=1}^{m-1}\sum_{z_2 = -m+1}^{-1}\left(m-z_1\right)\left(m+z_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)\\
+& + \sum_{z_1=2-m}^{\scriptscriptstyle 0}\sum_{z_2 = -m+1}^{-1} \left(m+z_1-1\right)\left(m+z_2\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right) \\
 & = \sum_{z_1=2-m}^{m-1} \sum_{z_2 = 1-m}^{m-2} \left(m-|z_1| - \mathbbm{1}_{z_{1} \leq 0}\right)\left(m-|z_2|-\mathbbm{1}_{z_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(z) \right)
@@
 Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure.
-Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}.
-We get the next result.
-\begin{Lemma}
-\begin{align*}
-\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) \\
-& - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right),
-\end{align*}
-where, 
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) & = \\
-& \hspace{-9cm}\mathbb{E}\left(\left(\Phi\left(\dfrac{\sqrt{2}\max\left(t,s\right) + \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)  - \Phi\left(\dfrac{\sqrt{2}\min\left(t,s\right) - \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)\right)\right.
-\\
-& \hspace{-1cm} \left.\mathbbm{1}_{\left\{(|s-t| \leq |Z|\sqrt{2(1-\rho(e_1))}\right\}}\right)
-\end{align*}}
-with $Z \sim \mathcal{N}(0,1)$. 
-\end{Lemma}
-Figure \ref{configurations} shows the four types of configurations that are encountered in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma} depending on the orientation $i$ and position on the grid $x$.
-We will call \textit{three cells} and \textit{four cells} configuration depending on how many cells are involved.
+Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and position on the grid $x$. 
 \begin{figure}[H]
 \begin{center}
-  \captionsetup[subfigure]{justification=centering}
   \begin{subfigure}[b]{0.25\textwidth} 
@@
 \draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
-\draw[step = 2cm, line width =0.5mm, blue] (1,0) -- (1,0.5);
+% \draw[step = 2cm, line width =0.5mm, blue] (1,0) -- (1,0.5);
 \draw[pattern=north east lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
@@
 \end{tikzpicture}
+\caption{$i = 1, x = (0,0)$}
+\end{subfigure}
+\begin{subfigure}[b]{0.25\textwidth} 
+  \centering
 \begin{tikzpicture}[scale = 1.5]
@@
 \end{subfigure}
+\begin{subfigure}[b]{0.25\textwidth} 
+  \centering 
+\begin{tikzpicture}[scale = 1.5]
+\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
+\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
+\draw[step = 2cm, line width =0.5mm, blue] (1,1) -- (1,1.5);
+\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
+\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
+\draw[pattern=north west lines, pattern color=green, opacity=1] (1.5, 1.5) rectangle (1,1);
+\draw[pattern=north west lines, pattern color=red, opacity=1] (0.5, 1)  rectangle (1, 1.5);
+\end{tikzpicture}
+\caption{$i = 1, x = (1,2)$}
+\end{subfigure}
   \hspace{0.5cm}
@@
 \end{subfigure}
-~\\
 \begin{subfigure}[b]{0.25\textwidth} 
@@
 \end{subfigure}
-  \hspace{0.5cm}
-  \begin{subfigure}[b]{0.25\textwidth} 
-  \centering 
-\begin{tikzpicture}[scale = 1.5]
-\draw[step = 0.5cm, black, thick](0,0) grid (1.5,1.5);
-\draw[step = 2cm, line width =0.5mm, blue] (0.5,0) -- (0.5,0.5);
-\draw[step = 2cm, line width =0.5mm, blue] (1,1) -- (1,1.5);
-\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (0.5,0.5);
-\draw[pattern=north west lines, pattern color=cyan, opacity=1] (0.5, 0) rectangle (1,0.5);
-\draw[pattern=north west lines, pattern color=green, opacity=1] (1.5, 1.5) rectangle (1,1);
-\draw[pattern=north west lines, pattern color=red, opacity=1] (0.5, 1)  rectangle (1, 1.5);
-\end{tikzpicture}
-\caption{$i = 1, x = (1,2)$}
-\end{subfigure}
 \end{center}
-\caption{Illustration of the three cells and four cells configuration (respectively first and second row) involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
+\caption{Illustration of the two three and four cells configuration involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
 \label{configurations}
 \end{figure}
+Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}.
+Thus, We get the next result.
+\\
+\begin{Lemma}
+\begin{align*}
+\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) \\
+& - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right),
+\end{align*}
+where, 
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle  e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{ \scriptscriptstyle  e_1}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle e_1}) \right\}}\right) & = \\
+& \hspace{-9cm}\mathbb{E}\left(\left(\Phi\left(\dfrac{\sqrt{2}\max\left(t,s\right) + \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)  - \Phi\left(\dfrac{\sqrt{2}\min\left(t,s\right) - \sqrt{1-\rho(e_1)}|Z|}{\sqrt{1+\rho(e_1)}}\right)\right)\right.
+\\
+& \hspace{-1cm} \left.\mathbbm{1}_{\left\{(|s-t| \leq |Z|\sqrt{2(1-\rho(e_1))}\right\}}\right)
+\end{align*}}
+with $Z \sim \mathcal{N}(0,1)$. 
+\end{Lemma}
 Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
@@
 \rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$ 
-Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{i}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{i}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x}\end{equation} and
-{\small
-$\left\{\begin{array}{rlc}
-\Delta \rho(x) & = & \rho(x-e_1)-\rho(x) \\
-S\rho(x) & = & \rho(x-e_1)+\rho(x)\\
-\Delta \rho(x+e_i) & = & \rho(x+e_i-e_1)-\rho(x+e_i) \\
-S\rho(x+e_i) & = & \rho(x+e_i-e_1)+\rho(x+e_i)\\
-\end{array}\right.\\
-$
-}
-The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}~= M\Sigma M^{\star}}$ with {\small $M = \begin{pmatrix}
+Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
+$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$.
+The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}_{i}(x)~= M\Sigma_{i}(x) M^{\star}}$ with {\small $M = \begin{pmatrix}
 -1 & 1 & 0 &  0 \\
@@
 0 & 0 & 1 & 1
-\end{pmatrix}$}. \\
-Then $\tilde{\Sigma} = \begin{pmatrix} A_{1} & B \\ B^{\star} & A_{i} \end{pmatrix}$
+\end{pmatrix}$}. Then $\tilde{\Sigma}_{i}(x) = \begin{pmatrix} A_{1} & B_{i}(x) \\ B^{\star}_{i}(x) & A_{i} \end{pmatrix}$
 with 
-$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ \\
-and {\small $B = \begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\ 
+$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ and \linebreak {\small $B_{i}(x) =~\begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\
  S\rho(x+e_i)- S\rho(x) &  S\rho(x) + S\rho(x+e_i) 
- \end{pmatrix}$}. \\
-The quantity we aim to compute is 
+ \end{pmatrix}$}. The quantity we aim to compute is 
 {\small
@@
 & \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
-\end{align}}Considering the first part of the previous equation, 
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \\
-& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, X_{e_1} -X_{\scriptscriptstyle 0}) \leq t -X_{\scriptscriptstyle 0}\leq \max(0, X_{e_1}-X_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, X_{x+e_i}-X_{\scriptscriptstyle x}) \leq s - X_{\scriptscriptstyle x} \leq \max(0, X_{x+e_i} - X_{\scriptscriptstyle x}) \right\}}\right) \\
-& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}) \leq t + \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(0, \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0})\right\}}\mathbbm{1}_{\left\{\min(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \leq s + \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} - S^{i}_{\scriptscriptstyle x}}{2} \leq \max(0, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}) \right\}}\right) \\
-& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}) \leq t - \frac{S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}\leq \max(-\frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2}, \frac{\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}}{2})\right\}}\mathbbm{1}_{\left\{\min(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}, \frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \leq s - \frac{S^{i}_{\scriptscriptstyle x}}{2} \leq \max(-\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2},\frac{\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2}) \right\}}\right) \\
-& \hspace{-9.75cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
+\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right)\\
+& \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
 \end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\Sigma_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
@@
   \begin{array}{rlc}
-  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_1U, \\
-  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma_2V, \\
-  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W, \\
-  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(i)}_{U}(x)U +  \pi^{\scriptscriptstyle(i)}_{V}(x) V +  \pi^{\scriptscriptstyle(i)}_{W}(x) W +  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z,
+  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z,
 \end{array}\right.$ \\
@@
  \begin{array}{rlc}
- \sigma_1 & = &  \sqrt{2(1-\rho(e_1))} \\
- \sigma_2 & = & \sqrt{2(1+\rho(e_1))} \\
-   \alpha^{\scriptscriptstyle(i)}_{U}(x) & = & \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma_1} \\
-   \alpha^{\scriptscriptstyle(i)}_{V}(x) & = &  \frac{S\rho(x+e_i)-S\rho(x)}{\sigma_{2}}  \\
-   \alpha^{\scriptscriptstyle(i)}_{W}(x)& = & \sqrt{2(1 - \rho(e_{i})) - \alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}} \\ 
-   \pi^{\scriptscriptstyle(i)}_{U}(x) & = &  \frac{\Delta \rho(x) + \Delta \rho(x+e_i)}{\sigma_1} \\
-    \pi^{\scriptscriptstyle(i)}_{V}(x) & = & \frac{S \rho(x) + S\rho(x+e_i)}{\sigma_{2}} \\
-   \pi^{\scriptscriptstyle(i)}_{W}(x) & = & \frac{- \left(\alpha^{\scriptscriptstyle(i)}_{U}(x)\pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{V}(x)\pi^{\scriptscriptstyle(i)}_{V}(x)\right) }{\alpha^{\scriptscriptstyle(i)}_{W}(x)}\\
-   \pi^{\scriptscriptstyle(i)}_{Z}(x)& = & \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}
+ \sigma^{\scriptscriptstyle (-)}_{1} & = &  \sqrt{2(1-\rho(e_1))} \\
+ \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
+ \end{array}\right.$ 
+ $\left\{
+ \begin{array}{rlc}
+   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right) \\
+   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ \\
+    $\left\{
+ \begin{array}{rlc}
+   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
+    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
+     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
+   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}
 \end{array}\right.$ 
@@
 \label{PropositionFourCell}
-Considering the assumptions above, the two cases that we have to distinguish when computing \eqref{covconf} are $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$ and $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, thus we get
-\begin{itemize}
-  \item if $\pi^{\scriptscriptstyle(i)}_{Z}(x) \neq 0$, then 
+Considering the assumptions above we get 
 {\small 
@@
 \label{Thisthofour}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle 1}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}}\right.
-\\
+\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right.
+\nonumber\\
 & \hspace{-6cm} \left.
-\left|\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right) \right.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
 \right.
@@
 \left.
-- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right| \right)
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
 \end{align}
-}with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x))^{2})$.
-\item else, if $\pi^{\scriptscriptstyle(i)}_{Z}(x) = 0$, and $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0, S\rho(x) > 0$, $S\rho(x+e_i) > 0$ then, 
-{\tiny
-\begin{align}
-\label{thisthothree}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
-& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left( \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x+e_i)}\right) \right) \right)\right.\\
-&\hspace{-4.5cm} \left.
-\mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right)\\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right)\right)\right.\\
-& \hspace{-4.5cm} \left.
-\mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right) \\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x+e_i)}\right)\right) - \Phi\left( \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \right)\right)\right.
-\\
-& \hspace{-4.5cm}\left.
-\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \right) \\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right)\right)\right.\\
-& \hspace{-4.5cm}\left.\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}}\right)
-\end{align}}
-\item else if $\pi^{\scriptscriptstyle(i)}_{Z}(x)= \pi^{\scriptscriptstyle (i)}_{V}(x) = S\rho(x+e_i) = 0$, then
-{\tiny 
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
-& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}\right) - \Phi\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}} \right) \right)\right.\\
-&\hspace{-4.5cm}  \left.\left(\mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
-& \left.\left.
-\left.
-+ \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right.\right.\\
-& \hspace{-4cm}+ \left.\left.
-\mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
-& \left.\left.\left.
-\left.
-\left.
-+ \mathbbm{1}_{\left\{ 0 \geq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right)\right)\right)\right)
-\end{align*}
-}
-\end{itemize}
+}with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$.
 \end{Proposition}
 \begin{proof}(Proof of Proposition \ref{PropositionFourCell})
-Let us first consider the indicator functions and assume that $\Delta^{i}_{\scriptscriptstyle x} \geq 0$. Then 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ |2s - S^{i}_{\scriptscriptstyle x}| < \Delta^{i}_ {\scriptscriptstyle x}\right\}} & =  \mathbbm{1}_{\left\{- \Delta^{i}_ {\scriptscriptstyle x} \leq 2s - S^{i}_ {\scriptscriptstyle x} \leq \Delta^{i}_ {\scriptscriptstyle x}\right\}} \\
-& \hspace{-2.1cm} = \mathbbm{1}_{\left\{ -  \alpha^{\scriptscriptstyle(i)}_{U}(x)U -  \alpha^{\scriptscriptstyle(i)}_{V}(x) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{U}(x)U -  \pi^{\scriptscriptstyle(i)}_{V}(x) V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
-& \phantom{=} \hspace{4.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq   \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-&\hspace{-2.1cm} = \mathbbm{1}_{\left\{ \left( \pi^{\scriptscriptstyle(i)}_{U}(x) -  \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) -  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
-& \phantom{=} \hspace{4.2cm}\textcolor{white}{\mathbbm{1}}_{\left.\leq \left( \pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) +  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-& \hspace{-2.1cm} = \mathbbm{1}_{\left\{\frac{2\Delta \rho(x)}{\sigma_1} U + \frac{2S \rho(x)}{\sigma_{2}}V - \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq \frac{2\Delta \rho(x+e_i) }{\sigma_1}U + \frac{2S \rho(x+e_i)}{\sigma_{2}}V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W\right\}}.
-\end{align*}}
-Else if $\Delta^{i}_{\scriptscriptstyle x} < 0$, then  
-\begin{align*}
-\mathbbm{1}_{\left\{ |s - \frac{S^{i}_{\scriptscriptstyle x}}{2}| < -\frac{1}{2}\Delta^{i}_ {\scriptscriptstyle x}\right\}} & =  \mathbbm{1}_{\left\{\Delta^{i}_ {\scriptscriptstyle x} \leq 2s - S^{i}_ {\scriptscriptstyle x} \leq -\Delta^{i}_ {\scriptscriptstyle x}\right\}} \\
-& \hspace{-2.2cm} = \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{U}(x)U -  \pi^{\scriptscriptstyle(i)}_{V}(x) V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
-& \phantom{=} \hspace{2.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq  - \alpha^{\scriptscriptstyle(i)}_{U}(x)U -  \alpha^{\scriptscriptstyle(i)}_{V}(x) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-& \hspace{-2.2cm}  = \mathbbm{1}_{\left\{ \left( \pi^{\scriptscriptstyle(i)}_{U}(x) + \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) +  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s -  \pi^{\scriptscriptstyle(i)}_{W}(x) W -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \right.} \\
-& \phantom{=} \hspace{2.2cm} \textcolor{white}{\mathbbm{1}}_{\left.\leq \left( \pi^{\scriptscriptstyle(i)}_{U}(x) -  \alpha^{\scriptscriptstyle(i)}_{U}(x)\right) U + \left( \pi^{\scriptscriptstyle(i)}_{V}(x) -  \alpha^{\scriptscriptstyle(i)}_{V}(x) \right) V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-& \hspace{-2.2cm} = \mathbbm{1}_{\left\{\frac{2\Delta \rho(x+e_i) }{\sigma_1} U + \frac{2S\rho(x+e_i)}{\sigma_{2}}V + \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 2s - \pi^{\scriptscriptstyle(i)}_{W}(x) W - \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq \frac{2\Delta \rho(x)}{\sigma_1}U + \frac{2S \rho(x)}{\sigma_{2}}V -  \alpha^{\scriptscriptstyle(i)}_{W}(x) W\right\}}
-\end{align*}
-Putting everything together we get that 
-{\tiny
-\begin{align*}
-\mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\mathbbm{1}_{ \left\{-2s + \frac{2\Delta \rho(x)}{\sigma_1} U + \frac{2S \rho(x)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq  -  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq -2s + \frac{2\Delta \rho(x+e_i) }{\sigma_1}U + \frac{2S \rho(x+e_i)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}} \\
-& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} < 0\right\}} \mathbbm{1}_{\left\{-2s + \frac{2\Delta \rho(x+e_i) }{\sigma_1} U + \frac{2S\rho(x+e_i)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq - \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq -2s + \frac{2\Delta \rho(x)}{\sigma_1}U + \frac{2S \rho(x)}{\sigma_{2}}V + \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}} \\
-& \hspace{-14.5cm} = \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\mathbbm{1}_{\left\{2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  \pi^{\scriptscriptstyle(i)}_{Z}(x)Z \leq 2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right\}}\\
-& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} < 0\right\}} \mathbbm{1}_{\left\{2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq  \pi^{\scriptscriptstyle(i)}_{Z}(x) Z \leq 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}} \\
-& \hspace{-14.5cm} \overset{\mathbb{E}}{=} \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \leq 0\right\}}\left\{\left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right.
-\right.\\
-& \left.\left.
-\hspace{-13cm} - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W\right) \right] \right.
-\\
-& \hspace{-14.5cm} \left.
-\mathbbm{1}_{\left\{- \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \leq - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right\}} \right\}\\
-& \hspace{-14.5cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\left\{\left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)} \left(2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right.
-\right.\\
-& \hspace{-14cm} \left.
-\left.
-- \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right] \right.\\
-& \hspace{-14cm}\left.\mathbbm{1}_{\left\{- \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}}\right\} \\
-&\hspace{-14.5cm} \overset{\mathbb{E}}{=} \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \leq 0\right\}} \left[\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right) \right.\\
-& \left.
-\hspace{-13cm} - \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x)}{\sigma_1}U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W\right) \right]\\
-& \hspace{-14.2cm} + \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}\left[\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right) \right.
-\\
-& \hspace{-13.5cm}\left.- \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \right)\right]
-\end{align*}}
-Since
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{- \frac{2\Delta \rho(x+e_i)}{\sigma_1}U - \frac{2S \rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right)W \leq  - \frac{2\Delta \rho(x)}{\sigma_1} U - \frac{2S \rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right\}} & = \\
-& \hspace{-11.7cm} \mathbbm{1}_{\left\{- 2\alpha^{\scriptscriptstyle(i)}_{U}(x)U - 2\alpha^{\scriptscriptstyle(i)}_{V}(x)V - 2\alpha^{\scriptscriptstyle(i)}_{W}(x)W \leq  0\right\}}  = \mathbbm{1}_{\left\{\Delta^{i}_{\scriptscriptstyle x} \geq 0\right\}}
-\end{align*}}Putting everything together, we get
-{\small
-\begin{align}
-\label{Thistho}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber \\
-& \hspace{-9.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \geq 0\right\}} \right.
+Let us first consider the following indicator function
+{\small
+\begin{align*}
+\mathbbm{1}_{\left\{ |2s - S^{i}_{\scriptscriptstyle x}| \leq |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}
+& = \mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}
+\end{align*}}Thus, 
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\left\{ |2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}| \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}| \right\}}\right)\\
+&\hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}\right)\\
+& \hspace{-6.5cm} \text{The variable}\; Z \sim \mathcal{N}\left(0, \pi^{\scriptscriptstyle(+, i)}_{Z}(x)^{2}\right) \text{and} \; \text{$\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ being an increasing function,}\\
+& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
+&\hspace{-4cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  + \Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}  \right) \right.
 \right.
 \nonumber \\
-& \hspace{-8.5cm}\left.
+& \hspace{-4cm}\left.
 \left.
-\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W \right)  \right.
-\right.
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - \Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x} \right)  \right| \right) \\
+& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
+&\hspace{-6cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right.
 \right.
 \nonumber \\
-& \hspace{-7.5cm}\left.
+& \hspace{-5cm}\left.
 \left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W \right)  \right) \right.
-\right.
-\nonumber \\
-&  \hspace{-8.75cm} \left.
-\left.
-+ \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \alpha^{\scriptscriptstyle(i)}_{W}(x) W \leq 0\right\}} \right.
-\right.
-\nonumber\\
-& \left.
-\left.
-\hspace{-8.5cm}\left(\Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma_1}U - \frac{2S \rho(x+e_i) }{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) +  \alpha^{\scriptscriptstyle(i)}_{W}(x) \right)W   \right)  \right.
-\right.
-\right.
-\nonumber \\
-& \hspace{-7.5cm}\left.
-\left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma_{2}}V - \left( \pi^{\scriptscriptstyle(i)}_{W}(x) -  \alpha^{\scriptscriptstyle(i)}_{W}(x)\right) W\right)\right)\right)\right)
-\end{align}
-}
-with $\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(i)}_{Z}(x)^{2})^{-1})$. \\
-Now, considering the case where $\pi^{1}_{Z}(x)= 0$, thus, we effectively lose the impact of the fourth variable $Z$, and we can express the whole system using only three variables independent Gaussian variables.
-Considering the new expression of the variables in the indicator function, we distinguish two cases $s - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2} \geq 0$ and $s - \frac{S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}}{2} \leq 0$, we shall start with the first one.
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{i}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\left(\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq \Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}\right\}}  +  \mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq \Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}\right\}}\right) \\
-& = \mathbbm{1}_{\left\{ - \pi^{\scriptscriptstyle (i)}_{V}(x)V \geq -2s +   \pi^{\scriptscriptstyle (i)}_{U}(x)U + \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\right.\\
-& \hspace{0.35cm}  \left.
-\mathbbm{1}_{\left\{ - \left(\alpha^{\scriptscriptstyle (i)}_{V}(x) + \pi^{\scriptscriptstyle (i)}_{V}(x)\right)V \leq -2s+ \left(\alpha^{\scriptscriptstyle (i)}_{U}(x)+\pi^{\scriptscriptstyle (i)}_{U}(x)\right)U +  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}} \right.
-\\
-& \hspace{0.35cm} \left.
-+ \mathbbm{1}_{\left\{ \left(\alpha^{\scriptscriptstyle (i)}_{V}(x) - \pi^{\scriptscriptstyle (i)}_{V}(x)\right)V \leq  -2s + \left(\pi^{\scriptscriptstyle (i)}_{U}(x) - \alpha^{\scriptscriptstyle (i)}_{U}(x)\right)U + \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}}\right) \\
-& = \mathbbm{1}_{\left\{ - \pi^{\scriptscriptstyle (i)}_{V}(x)V \geq -2s +   \pi^{\scriptscriptstyle (i)}_{U}(x)U + \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}}\left(\right.\\
-& \hspace{0.35cm}  \left.
-\mathbbm{1}_{\left\{ - \frac{S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V \leq -2s+ 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U +   \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}} \right.
-\\
-& \hspace{0.35cm} \left.
-+ \mathbbm{1}_{\left\{ -\frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V \leq  -2s +\frac{2\Delta\rho(x)}{\sigma_1}U +  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right\}}\right) \\
-\end{align*}}
-Assuming that $\pi^{\scriptscriptstyle (i)}_{V}(x) > 0 $, $S\rho(x+e_i)> 0$ and $S\rho(x)> 0$ we get 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ V \leq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
-& \hspace{0.35cm}  \left.
-\mathbbm{1}_{\left\{V \geq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)}{S\rho(x+e_i)}\right\}} \right.
-\\
-& \hspace{0.35cm} \left.
-+ \mathbbm{1}_{\left\{ V \geq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{1}_{W}(e_1) - \alpha^{1}_{W}(e_1)\right)W\right)}{2S\rho(x)}\right\}}\right)
-\end{align*}}
-Considering now the first part of the expression, we get 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}} & =  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}
-\end{align*}}
-Thus putting those two inequalities together we get, 
-{\tiny
-\begin{align*}
-\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
-& \hspace{-5cm}=  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}\mathbbm{1}_{\left\{ V \leq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
-& \hspace{0.35cm}  \left.
-\mathbbm{1}_{\left\{V \geq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)}{S\rho(x+e_i)}\right\}} \right.
-\\
-& \hspace{0.35cm} \left.
-+ \mathbbm{1}_{\left\{ V \geq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right\}}\right)\\
-& \hspace{-7cm}= \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\\
-& \hspace{-5cm} + \mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}
-\end{align*}}
-Then again considering the other part $2s - S^{i}_{\scriptscriptstyle x} \leq 0$ we get 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ V \geq \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right\}} \bigg( \\
-& \hspace{0.35cm}   \mathbbm{1}_{\left\{ V \leq \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)} \right\}}  \\
-& \hspace{0.35cm}  + \mathbbm{1}_{\left\{ V \leq \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right\}}\bigg)
-\end{align*}}
-
-And again 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
-& \hspace{-5cm} = \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)  \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \\
-& \hspace{-4.5cm} + \mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)  \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}}
-\end{align*}}
-And now we integrate 
-{\tiny 
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
-& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left( \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right) \right)\right.\\
-&\hspace{-4.5cm} \left.
-\mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right)\\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right)\right)\right.\\
-& \hspace{-4.5cm} \left.
-\mathbbm{1}_{\left\{\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \leq V \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{2s - \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right\}}\right) \\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right)\right) - \Phi\left( \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \right)\right)\right.
-\\
-& \hspace{-4.5cm}\left.
-\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}},\frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{S\rho(x+e_i)}\right) \right\}} \right) \\
-& \hspace{-5cm} + \mathbb{E}\left(\left(\Phi\left(\min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right)\right) - \Phi\left(\max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right)\right)\right)\right.\\
-& \hspace{-4.5cm}\left.\mathbbm{1}_{\left\{ \max\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}}, \frac{2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W}{\pi^{\scriptscriptstyle (i)}_{V}(x)}\right) \leq \min\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}, \frac{\sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)}{2S\rho(x)}\right) \right\}}\right)
-\end{align*}
-}
-if $S\rho(x) = 0$ and $S\rho(x+e_i) = 0$, thus $\pi^{\scriptscriptstyle (i)}_{V}(x) = 0$ then, 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
-& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)\right\}} \right. \\
-& \hspace{0.35cm} \left. + \mathbbm{1}_{\left\{ 0\geq \left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{1}_{W}(e_1) - \alpha^{1}_{W}(e_1)\right)W\right)\right\}}\right)
-\end{align*}}
-Then, again 
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ |2t - \sigma_{2}V| \leq \sigma_{1}|U|\right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \geq 0 \right\}}\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} \\
-& \hspace{-5cm}=  \mathbbm{1}_{\left\{ \frac{2t - \sigma_{1}|U|}{\sigma_{2}} \leq V \leq \frac{2t + \sigma_{1}|U|}{\sigma_{2}}  \right\}}\mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
-& \hspace{0.35cm}  \left. \mathbbm{1}_{\left\{0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{1}_{W}(e_1) + \alpha^{1}_{W}(e_1)\right)W\right)\right\}} \right. \\
-& \hspace{0.35cm} \left.
-+ \mathbbm{1}_{\left\{ 0 \geq \left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)
-\end{align*}}
-Then, again,
-{\small
-\begin{align*}
-\mathbbm{1}_{\left\{ 2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq 0 \right\}}\mathbbm{1}_{\left\{ -2s + S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}|\right\}} & = \mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \bigg( \\
-& \hspace{0.35cm}   \mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}  \\
-& \hspace{0.35cm}  + \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\bigg)
-\end{align*}} 
-{\tiny 
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \\
-& \hspace{-5cm} \mathbb{E}\left(\left(\Phi\left(\frac{2t + \sigma_{1}|U|}{\sigma_{2}}\right) - \Phi\left(\frac{2t - \sigma_{1}|U|}{\sigma_{2}} \right) \right)\right.\\
-&\hspace{-4.5cm}  \left.\left(\mathbbm{1}_{\left\{ 0 \geq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \leq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
-& \left.\left.
-\left.
-+ \mathbbm{1}_{\left\{ 0 \leq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right.\right.\\
-& \hspace{-4cm}+ \left.\left.
-\mathbbm{1}_{\left\{ 0 \leq 2s -   \pi^{\scriptscriptstyle (i)}_{U}(x)U - \pi^{\scriptscriptstyle (i)}_{W}(x)W\right\}} \left(\mathbbm{1}_{\left\{ 0 \geq \left(2s - 2\frac{\Delta\rho(x+e_i)}{\sigma_1}U -  \left(\pi^{\scriptscriptstyle (i)}_{W}(x) + \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right) \right\}}\right.\right.\right.\\
-& \left.\left.\left.
-\left.
-\left.
-+ \mathbbm{1}_{\left\{ 0 \geq \sigma_{2}\left(2s -\frac{2\Delta\rho(x)}{\sigma_1}U - \left(\pi^{\scriptscriptstyle (i)}_{W}(x) - \alpha^{\scriptscriptstyle (i)}_{W}(x)\right)W\right)\right\}}\right)\right)\right)\right)\right)
-\end{align*}
-}
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+ \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+ \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V   - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
+\end{align*}
 \end{proof}
+\begin{remark} In the third cell configuration,the matrix $\Sigma_{i}(x)$ is not positive-definite, thus the Cholesky decomposition does not apply, we have to proceed a differently, but this case is not relevant to the establishment of the Central Limit Theorem, therefor its computations will be presented in the Appendix.
+\end{remark}
 \subsubsection{Spatial independent case} 
 Let us start by considering the four cell configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
-$\alpha^{\scriptscriptstyle(i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thistho} becomes
+$\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(+, i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thistho} becomes
 {\small
@@
 & \left.
-\hspace{-10cm} \left(\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_i))}W \geq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s + \sqrt{2(1-\rho(e_1))} W\right) - \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s - \sqrt{2(1-\rho(e_1))} W\right)\right) \right.
+\hspace{-10cm} \left(\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_i))}W \geq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \sqrt{2(1-\rho(e_1))} W\right) - \Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left(2s - \sqrt{2(1-\rho(e_1))} W\right)\right) \right.
 \right.
@@
 \left.
-\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))} W  \leq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left( 2s - \sqrt{2(1-\rho(e_1))}W \right) - \Phi_{\pi^{\scriptscriptstyle(i)}_{Z}(x)}\left(2s + \sqrt{2(1-\rho(e_1))} W\right)\right)\right)\right)\\
+\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))} W  \leq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \sqrt{2(1-\rho(e_1))}W \right) - \Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left(2s + \sqrt{2(1-\rho(e_1))} W\right)\right)\right)\right)\\
 & \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}}\mathbbm{1}_{\left\{ |s - \frac{\sqrt{2(1+\rho(e_i))}Z}{2}| \leq |\frac{\sqrt{2(1-\rho(e_i))}W}{2}|\right\}}\right) \\
@@
 \end{align*}
-}Thus, $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (j)}(z)\right) = 0.$\\
-Regarding the three cell configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.
-Thus, those computations would give us the following expression,
-{\tiny
-\begin{align}
-\label{IIDCase}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{e_1}, X_{e_2}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) \nonumber \\
-& \hspace{-8.7cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U + \sqrt{2(1+\rho(e_1))}V \leq s\right\}}\right.
-\nonumber \\
-& \hspace{-8cm} \left.
-\left(1 - \Phi_{\alpha^{(1)}(e_1)}\left(\max\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right) \nonumber\\
-& \hspace{-8cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U+ \sqrt{2(1+\rho(e_1))}V \geq s\right\}}\right.
-\nonumber\\
-& \hspace{-8cm} \left.
-\left(\Phi_{\alpha^{(1)}(e_1)}\left(\min\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right),
-\end{align}}then if the Gaussian field $\left(X(x)\right)_{x \in G_{m}}$ is such that all the variables are independent, then $\rho(2e_1) = \rho(e_1) = 0$, thus Equation \eqref{IIDCase} becomes 
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
-& \hspace{-9cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{\frac{1}{\sqrt{2}} U + \frac{1}{\sqrt{2}}V \leq s\right\}} \left(1 - \Phi\left(s\right)\right)\right) \\
-& \hspace{-9cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{ s \leq \frac{1}{\sqrt{2}}U + \frac{1}{\sqrt{2}}V \right\}}\Phi\left(s\right)\right) \\
-& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \leq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq s \right\}}\right) \right)\\
-& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \geq s \right\}}\right) \right)
-\end{align*}}
-Applying the same strategy we adopted in \ref{iidCase} and considering the change variable $Z = \frac{V-U}{\sqrt{2}}$ and $Y = \frac{U+V}{\sqrt{2}}$ we get 
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
-& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \leq s \right\}} + \mathbbm{1}_{\left\{Z \leq s \right\}}\right) \right)\\
-& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \geq s \right\}} + \mathbbm{1}_{\left\{Z \geq s \right\}}\right) \right) \\
-& \hspace{-9cm}= (1-\Phi(s))\Phi(t)\left(\Phi(s) - \Phi(t)\right) + (1-\Phi(s))\left(1-\Phi(t)\right)\Phi(t)   + \Phi(s)\Phi(t)\left(1-\Phi(s)\right)\\
-& \hspace{-9cm}= \Phi(t)\left(1-\Phi(s)\right)\left(1+ 2\Phi(s) - 2\Phi(t)\right).
-\end{align*}}
-This result was previously proved in \cite{Psymetrie} (Proposition \textcolor{blue}{3.2}).
-\subsubsection{The behavior of $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$ when $x\to \infty$.}
-Considering the case where $x$ goes to $\infty$, one can assume that there exist $\epsilon > 0$ such that $\rho(x) \sim \epsilon$ thus the former expressions become \\
-
+}Thus, $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (j)}(z)\right) = 0.$
+\subsubsection{Behavior at large distance.}
+Considering the case the size of the window $S$ goes to infinity, we would like to study the behavior of $ \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$for $x >> 1$, \\
 \begin{table}[H]
@@
 $S\rho(x + e_i)$ & \hspace{3cm}$\rho(x+e_i-e_1)+\rho(x+e_i)$ & $O(\rho(x))$ \\\hline 
-$\alpha^{\scriptscriptstyle(i)}_{U}(x)$ &\hspace{4cm} $ \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma_1}$ & $O(\rho(x))$ \\  \hline
-$\alpha^{\scriptscriptstyle(i)}_{V}(x)$ & \hspace{4cm}   $\frac{S\rho(x+e_i)-S\rho(x)}{\sigma_{2}}$  & $O(\rho(x))$ \\  \hline
-$\alpha^{\scriptscriptstyle(i)}_{W}(x)$ & \hspace{2cm}$\sqrt{2(1 - \rho(e_{i})) - \alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}} $ & {\tiny$ \sqrt{2(1 - \rho(e_i)) } + O\left(\rho(x)^{2}\right)$}\\
+$\pi^{\scriptscriptstyle(-, i)}_{U}(x)$ &\hspace{4cm} $ \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$ & $O(\rho(x))$ \\  \hline
+$\pi^{\scriptscriptstyle(-, i)}_{V}(x)$ & \hspace{4cm}   $\frac{S\rho(x+e_i)-S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  & $O(\rho(x))$ \\  \hline
+$\pi^{\scriptscriptstyle(-, i)}_{W}(x)$ & \hspace{2cm}$\sqrt{2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}} $ & {\tiny$ \sigma^{\scriptscriptstyle (-)}_{i} + O\left(\rho(x)^{2}\right)$}\\
 \hline
-$\pi^{\scriptscriptstyle(i)}_{U}(x)$ & $ \hspace{4cm} \frac{\Delta \rho(x) + \Delta \rho(x+e_i) }{\sigma_1}$ & $O(\rho(x))$  \\ \hline
-$ \pi^{\scriptscriptstyle(i)}_{V}(x)$ & \hspace{4cm}$\frac{S \rho(x) + S\rho(x+e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}} $ & $O(\rho(x))$ \\ \hline 
-$ \pi^{\scriptscriptstyle(i)}_{W}(x) $ & $\frac{\rho(x)^{2} - \rho(x+e_i)^{2} + \rho(x-e_1)^{2} - \rho(x + e_i - e_1)^{2} - 2\rho(e_1)\left(\rho(x)\rho(x-e_1) - \rho(x+e_i)\rho(x+e_i-e_1)\right)}{(\sigma_{1}\sigma_{2})^{2}\alpha^{\scriptscriptstyle(i)}_{W}(x)}$ & $O\left(\rho(x)^2\right)$\\ \hline
-$\pi^{\scriptscriptstyle(i)}_{Z}(x)$ & $ \hspace{2cm} \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}$ & {\tiny$ \sqrt{2(1 + \rho(e_i)) } + O\left(\rho(x)^{2}\right)$} \\\hline
+$\pi^{\scriptscriptstyle(+, i)}_{U}(x)$ & $ \hspace{4cm} \frac{\Delta \rho(x) + \Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}$ & $O(\rho(x))$  \\ \hline
+$ \pi^{\scriptscriptstyle(+, i)}_{V}(x)$ & \hspace{4cm}$\frac{S \rho(x) + S\rho(x+e_i)}{\sigma^{\scriptscriptstyle (+)}_{i}} $ & $O(\rho(x))$ \\ \hline 
+$ \pi^{\scriptscriptstyle(+, i)}_{W}(x) $ & $\frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) $ & $O\left(\rho(x)^2\right)$\\ \hline
+$\pi^{\scriptscriptstyle(+, i)}_{Z}(x)$ & $ \hspace{2cm} \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}$ & {\tiny$ \sigma^{\scriptscriptstyle (+)}_{i} + O\left(\rho(x)^{2}\right)$} \\\hline
 \end{tabularx}
 \end{table}
-We denote by $R_{1}(x) = \frac{-\alpha^{\scriptscriptstyle(i)}_{U}(x)^{2} - \alpha^{\scriptscriptstyle(i)}_{V}(x)^{2}}{\sigma^{\scriptscriptstyle(i)}_{1}}$ and $R_{2}(x) = \frac{- \pi^{\scriptscriptstyle(i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(i)}_{W}(x)^{2}}{\sigma^{\scriptscriptstyle(i)}_{2}}$.\\
-Thus, Taylor's expansion of $\pi^{\scriptscriptstyle(i)}_{Z}(x)$ we get that $\pi^{\scriptscriptstyle(i)}_{Z}(x) -  \sigma^{\scriptscriptstyle(i)}_{2}  = \frac{\sigma^{\scriptscriptstyle(i)}_{2}}{2}R(x) + o(\rho(x)^{2})$.
-Reconsidering the formula above,
+Thus, $\frac{2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}} - \frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} = O(\rho(x))$ and $ \frac{2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+\pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) +\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}} - \frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} = O(\rho(x))$.\\
+Reconsidering Equation (\ref{Thisthofour}) we get,
 {\small
@@
  \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) & =  \\ 
-& \hspace{-2.5cm}\mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}} \left( \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1-R_1(x)} W \geq 0\right\}} \right.
+ & \hspace{-2.5cm} \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
+&\hspace{-2.5cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right.
 \right.
 \nonumber \\
-& \left.
+& \hspace{-2.5cm}\left.
 \left.
-\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_2(x)} } \right)  \right.
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+ \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+ \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V   - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right) \\
+& \hspace{-2.5cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right|\right)\\
+& \hspace{-2.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}} \left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right| \right.
 \right.
+\\
+& \hspace{4.75cm} \left.\left.
+-  \left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right| \right)\right),
+\end{align*}
+}
+thus, 
+{\small
+\begin{align*}
+ |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq \\
+ &  \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right.
 \right.
-\nonumber \\
-&\left.
-\left.
-\left.
-- \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_2(x)} } \right)  \right) \right.
-\right.
-\nonumber \\
-&   \left.
-\left.
-+ \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)} W \leq 0\right\}} \right.
-\right.
-\nonumber\\
-& \left.
-\left.\left(\Phi\left( \frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_1(x)} }   \right)  \right.
-\right.
-\right.
-\nonumber \\
-& \left.
-\left.
-\left.
-- \Phi\left( \frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V -  \pi^{\scriptscriptstyle(i)}_{W}(x) W}{\sigma^{\scriptscriptstyle(i)}_{2}\sqrt{1 - R_1(x)} }\right)\right)\right)\right) \\
-& \hspace{-2.5cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma_2V}{2}| \leq |\frac{\sigma_1U}{2}|\right\}}\left(\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \right.\right.\\
-& \left.
-\left.
-\hspace{2cm} + \mathbbm{1}_{\left\{ W \leq 0\right\}} \left(\Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s +\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right)\right) \right).
-\end{align*}
-}To simplify the expression let us first get ride off all the second order degree terms (\textit{i.e.} $o(\rho(x)^{2})$), and now we consider the first part of the equation
-{\small
-\begin{align*}
-\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} + o(\rho(x))\right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} + o(\rho(x))\right) & = \\
-& \hspace{-17cm}  \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) - \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)- \left(\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}}V\right)\Phi'\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}}\right)\\
-& \hspace{-15cm} + \left(\frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle(i)}_{2}\sigma_1} U + \frac{2S\rho(x + e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}}\right) + o\left(\rho(x)\right)
-\end{align*}
-}
-Considering the whole expression again, we would get 
-{\tiny
-\begin{align*}
-\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{ \sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right)  \right)  \nonumber \\
-& \hspace{-14cm} -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \\
-& \hspace{-15cm}= \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) - \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)- \left(\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right)\right.\\
-& \hspace{-14cm}\left.
-+ \left(\frac{2\Delta \rho(x+e_i) }{\sigma_2\sigma_1} U + \frac{2S\rho(x + e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right)\Phi'\left(\frac{2s - \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}}\right) + o\left(\rho(x)\right)\right)  -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right)\\
-& \hspace{-15cm}\leq \frac{1}{\sqrt{2\pi}^3} \int \int \int \left(\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}w \geq 0\right\}}\mathbbm{1}_{w \leq 0} + \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x) v +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}w \leq 0\right\}}\mathbbm{1}_{w \geq 0}\right)e^{-u^2/2}e^{-w^2/2}e^{-v^2/2}dudvdw \\
-& \hspace{-13cm} + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
-& \hspace{-15cm}\leq \frac{1}{2\pi} \int \int \left(\left(\Phi\left(0\right) - \Phi\left(\frac{- \alpha^{\scriptscriptstyle(i)}_{U}(x)u -  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\right)\right)\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \geq 0\right\}} + \left(\Phi\left(\frac{- \alpha^{\scriptscriptstyle(i)}_{U}(x)u -  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\right) - \Phi\left(0\right)\right)\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \leq 0\right\}}\right)\\
-&  \hspace{-13cm}e^{-u^2/2}e^{-v^2/2}dudv + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
-& \hspace{-15cm}\leq \frac{1}{2\pi}\int\int\frac{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v}{\sigma_1}\left(\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \geq 0\right\}} - \mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v \leq 0\right\}} \right)e^{-u^2/2}e^{-v^2/2}dudv \\
-& \hspace{-13cm} + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
-& \hspace{-15cm} \leq \frac{1}{2\pi}\int\int\frac{\left| \alpha^{\scriptscriptstyle(i)}_{U}(x)u +  \alpha^{\scriptscriptstyle(i)}_{V}(x)v\right|}{\sigma_1}e^{-u^2/2}e^{-v^2/2}dudv + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) \\
-& \hspace{-15cm} \leq \mathbb{E}\left(\left|\frac{\Delta\rho(x+e_i) -\Delta \rho(x)}{(\sigma_1)^2}U +\frac{S\rho(x+e_i)-S\rho(x)}{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right) + \mathbb{E}\left(\left|\frac{2\Delta \rho(x+e_i) }{\sigma_1\sigma^{\scriptscriptstyle(i)}_{2}} U + \frac{2S\rho(x+e_i)}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}V\right|\right)
-\end{align*}
-}Using the fact that $\Delta\rho(x+e_i), \Delta\rho(x), S\rho(x+e_i), S\rho(x)  \sim \rho(x)$.
-Let $C =~\frac{1}{2}\left( \frac{2}{(\sigma_1)^2} + \frac{6}{\sigma_{1}\sigma_2} + \frac{4}{\sigma_2\sigma^{\scriptscriptstyle(i)}_{2}}\right)$
-Thus, 
-{\tiny
-\begin{align*}
-\mathbbm{1}_{\left\{ \alpha^{\scriptscriptstyle(i)}_{U}(x)U +  \alpha^{\scriptscriptstyle(i)}_{V}(x) V +  \sigma^{\scriptscriptstyle(i)}_{1}\sqrt{1 - R_1(x)}W \geq 0\right\}}\left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x) }{\sigma_1} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W  - \frac{2\Delta \rho(x+e_i) }{\sigma_1} U - \frac{2S\rho(x + e_i)}{\sigma^{\scriptscriptstyle(i)}_{2}}V}{\sigma^{\scriptscriptstyle(i)}_{2}} \right)  \right)  \nonumber \\
-& \hspace{-14cm} -\mathbbm{1}_{\left\{ W \geq 0\right\}} \left(\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle(i)}_{1}W}{\sigma^{\scriptscriptstyle(i)}_{2}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle(i)}_{1}W }{\sigma^{\scriptscriptstyle(i)}_{2}} \right)\right) \\
-& \hspace{-15cm} \leq C|\rho(x)|
-\end{align*}} Thus {\small
-\begin{align*}
-|\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| \leq 2C|\rho(x)|
-\end{align*}}
+\\
+ & \hspace{2cm} \left.
+\left.+ \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right|\right) \\
+ & \leq \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right| \right.
+\\
+ & \hspace{2cm} \left.
++ \left| \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right|\right),
+ \end{align*}
+besides $||\Phi'||_{\infty} \leq \frac{1}{\sqrt{2\pi}}$, thus, there exist a constant $C \in \mathbb{R}^{+}$ such that 
+\begin{align*}
+&  |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| \leq 2C|\rho(x)|. 
+\end{align*}
 Considering $R$ the residue of the sum in the covariance
@@
 \begin{equation*}
-\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)  \\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right),
+\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)  \\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma^{\star}_{2}\right),
 \end{equation*}
-where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2}^{\star}\right)$ for the $2$-dimensional centered Gaussian distribution with covariance matrix $\Sigma_{2}^\star$ given by
-\begin{align*}
-\Sigma^{\star}_{2}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t), \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t) \right)
+where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma^{\star}\right)$ for the $2$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^{\star}_{2}$ given by
+\begin{align*}
+\Sigma^{\star}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t), \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t) \right)
 \end{align*}
@@
 \end{figure}
+\appendix 
+\section{Three cell configuration}
+Regarding the three cell configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.
+Thus, those computations would give us the following expression,
+{\tiny
+\begin{align}
+\label{IIDCase}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{e_1}, X_{e_2}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) \nonumber \\
+& \hspace{-8.7cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U + \sqrt{2(1+\rho(e_1))}V \leq s\right\}}\right.
+\nonumber \\
+& \hspace{-8cm} \left.
+\left(1 - \Phi_{\alpha^{(1)}(e_1)}\left(\max\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right) \nonumber\\
+& \hspace{-8cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sqrt{2(1+\rho(e_1))}V \leq \sqrt{2(1-\rho(e_1))}U|\right\}}\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))}U+ \sqrt{2(1+\rho(e_1))}V \geq s\right\}}\right.
+\nonumber\\
+& \hspace{-8cm} \left.
+\left(\Phi_{\alpha^{(1)}(e_1)}\left(\min\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right),
+\end{align}}then if the Gaussian field $\left(X(x)\right)_{x \in G_{m}}$ is such that all the variables are independent, then $\rho(2e_1) = \rho(e_1) = 0$, thus Equation \eqref{IIDCase} becomes 
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
+& \hspace{-9cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{\frac{1}{\sqrt{2}} U + \frac{1}{\sqrt{2}}V \leq s\right\}} \left(1 - \Phi\left(s\right)\right)\right) \\
+& \hspace{-9cm} + \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2}V}{2}| \leq |\frac{\sqrt{2}U}{2}|\right\}}\mathbbm{1}_{\left\{ s \leq \frac{1}{\sqrt{2}}U + \frac{1}{\sqrt{2}}V \right\}}\Phi\left(s\right)\right) \\
+& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \leq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq s \right\}}\right) \right)\\
+& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \leq t \right\}}\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq t \right\}}\mathbbm{1}_{\left\{U \geq 0\right\}}\left(\mathbbm{1}_{\left\{\frac{V+U}{\sqrt{2}} \geq s \right\}} + \mathbbm{1}_{\left\{\frac{V-U}{\sqrt{2}} \geq s \right\}}\right) \right)
+\end{align*}}
+Applying the same strategy we adopted in \ref{iidCase} and considering the change variable $Z = \frac{V-U}{\sqrt{2}}$ and $Y = \frac{U+V}{\sqrt{2}}$ we get 
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{e_1}, X_{2e_1}) \right\}}\right) & \\
+& \hspace{-9cm} = (1-\Phi(s))\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \leq s \right\}} + \mathbbm{1}_{\left\{Z \leq s \right\}}\right) \right)\\
+& \hspace{-9cm} + \Phi(s)\mathbb{E}\left(\mathbbm{1}_{\left\{Z \leq t \right\}}\mathbbm{1}_{\left\{Y \geq t \right\}}\left(\mathbbm{1}_{\left\{Y \geq s \right\}} + \mathbbm{1}_{\left\{Z \geq s \right\}}\right) \right) \\
+& \hspace{-9cm}= (1-\Phi(s))\Phi(t)\left(\Phi(s) - \Phi(t)\right) + (1-\Phi(s))\left(1-\Phi(t)\right)\Phi(t)   + \Phi(s)\Phi(t)\left(1-\Phi(s)\right)\\
+& \hspace{-9cm}= \Phi(t)\left(1-\Phi(s)\right)\left(1+ 2\Phi(s) - 2\Phi(t)\right).
+\end{align*}}
+This result was previously proved in \cite{Psymetrie} (Proposition \textcolor{blue}{3.2}).
 \bibliographystyle{plain}

### 2022-11-21 Draft_GFC.tex
21/11/2022

@@
 \addtolength{\topmargin}{-.8in}%
-
 \usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
@@
 \usepackage{epstopdf}
+\usepackage{array}
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
 
@@
 Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares.
-We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in G_{m}$, we define $C_{m}(x)$ as
+We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in \mathbb{G}_{m}$, we define $C_{m}(x)$ as
 \begin{equation*}
@@
 \vspace{-0.25cm}
-\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $G_{m}$.}
+\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
 \label{fig1}
@@
 \paragraph{Discrete setting}
-Using the previous square tiling, we write $S =  \underset{x \in G_m}{\cup}  C_{m}(x)$.
-We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$.
+Using the previous square tiling, we write $S =  \underset{x \in \mathbb{G}_{m}}{\cup}  C_{m}(x)$.
+We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{G}_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$.
 The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$,
@@
 Let us consider a threshold parameter $t \in \mathbb{R}$.
-We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in G_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$.
+We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$.
 \subsection{Perimeter of a binary image}\label{methods}
@@
 \end{Definition}
-% \section{Statistics of the perimeter} 
-\section{First moment}
+\section{Statistics of the perimeter} 
+\subsection{First moment}
 Let us start this study by investigating the first moment of the perimeter.
@@
 \label{propFisrtmoment}
-We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
+We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
 The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and
@@
 \begin{align*}
-\left\{ x \in G_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
+\left\{ x \in \mathbb{G}_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
 & = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},
@@
 \end{proof}
-\textcolor{blue}{Decreasing behavior for all level $t$.}
 \begin{remark}
@@
 \begin{equation*}
- \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
+ \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
 \end{equation*}
@@
 \begin{proof}
-Let $x\in(-1,1)$ and $f: x \mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ we consider $a,b  \in (-1,1)$, such that $a > b$,
-{\tiny
-\begin{align*}
-f(a) - f(b) = \mathbb{E}\left(\Phi_{\pi_{V}}\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(2t - \sqrt{2(1-b)}|N|\right)- \Phi\left(2t - \sqrt{2(1-a)}|N|\right)\right) \\
-= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right) \\
-= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0} \\
-= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0}
-\end{align*}}
-Thus if $a > b$
-{\tiny
-\begin{align*}
-\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) <  \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)
-\end{align*}}
+Let $t \in \mathbb{R}$ and $X$, $Y$ two centered with unit variance Gaussian random fields on $\mathbb{Z}^{2}$ of covariance stucture respectively $\tilde{\rho}$ and $\bar{\rho}$.
+We assume that $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$, and consider the Gaussian vectors $\left(X_{0}, X_{e_1}\right)$ and $\left(Y_{0}, Y_{e_1}\right)$, $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$ implies that $\mathbb{E}\left(X_{0}X_{e_1}\right) < \mathbb{E}\left(Y_{0}Y_{e_1}\right)$, we can write that
+\begin{align*}
+\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) = \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right) - \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right),
+\end{align*}
+according to Slepian's lemma, $\mathbb{P}\left(X_{\scriptscriptstyle 0} < t,  X_{e_1} < t\right) \leq \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right)$, \linebreak besides,~$\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right)=\mathbb{P}\left(X_{\scriptscriptstyle 0} < t\right)$ thus,
+\begin{align*}
+\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) \leq \mathbb{P}\left(X_{\scriptscriptstyle 0} < t \leq  X_{e_1}\right)
+\end{align*}
+and,
+\begin{align*}
+\mathbb{P}\left(\min\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right) < t \leq \max\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right)\right)  \leq \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_1}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_1}\right)\right)
+\end{align*}
+thus, 
+\begin{align*}
+\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
+\end{align*}
 \end{proof}
-\textcolor{blue}{reorient toward Github for illustrations.}
-\section{Covariance of the perimeter for two thresholds}
+\begin{remark}
+Considering the contraposition of this result, we get the following 
+\begin{equation*}
+ \text{if} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right)   \hspace{0.5cm} \text{then}  \hspace{0.5cm} \tilde{\rho}(e_i) \neq \bar{\rho}(e_i) \hspace{0.5cm}.
+\end{equation*} 
+\end{remark}
+\subsection{Covariance of the perimeter for two thresholds}
 Let $s, t \in \mathbb{R}$ such that $t \leq s$.
@@
 \text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) 
-& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} < 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)
+& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)
 \end{align*}
 \end{Lemma}
+
 \begin{proof}
@@
 \begin{array}{rcl}
-1 \leq x_2 \leq m-1 \\
-1 \leq y_2 \leq m-1 
-\end{array}\right. & \implies
+0 \leq x_2 \leq m-1 \\
+0 \leq y_2 \leq m-1 
+\end{array}\right. & \Leftrightarrow
 \left\{
@@
 \begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(1-m\right)}^{m-1}\sum_{z_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|z_{1}|\right)\left(m - 1- |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right)
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right)
 \end{align*}
@@
 & \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
-\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\Sigma_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
+\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
 We get the following decomposition \\
@@
 \mathbbm{1}_{\left\{ |2s - S^{i}_{\scriptscriptstyle x}| \leq |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}
-& = \mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}
+& = \mathbbm{1}_{\big\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z} \\
+& \hspace{3cm} _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}
 \end{align*}}Thus, 
@@
 \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\left\{ |2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}| \leq |\Delta^{\scriptscriptstyle (i)}_ {\scriptscriptstyle x}| \right\}}\right)\\
-&\hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}\right)\\
+&\hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\big\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z} \right.
+\\
+& \hspace{3cm}\left.
+_{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}\right)\\
 & \hspace{-6.5cm} \text{The variable}\; Z \sim \mathcal{N}\left(0, \pi^{\scriptscriptstyle(+, i)}_{Z}(x)^{2}\right) \text{and} \; \text{$\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ being an increasing function,}\\
@@
 & \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
-&\hspace{-6cm} \left.
+&\hspace{-6.2cm} \left.
 \left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right.
@@
 \nonumber \\
-& \hspace{-5cm}\left.
+& \hspace{-6.5cm}\left.
 \left.
@@
 \subsubsection{Behavior at large distance.}
-Considering the case the size of the window $S$ goes to infinity, we would like to study the behavior of $ \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$for $x >> 1$, \\
+Considering the case where the size of the window $S$ goes to infinity, and assuming that $\rho(x) \to 0$ when $||x||_{2} \to \infty$, we would like to study the decay of $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$ for~$||x||_{2} >> 1$,
+\begin{Lemma}
+Let $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$, there exist a constant $C \in \mathbb{R}^{+}$, for all $x \in \mathbb{G}_{m}$
+\begin{align*}
+&  |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| \leq Cr(x). 
+\end{align*}
+Besides, if $\sum_{x \in \mathbb{Z}^{2}} r(x) <~\infty$, then 
+$\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (i)}(s) \right)$ exists. 
+\end{Lemma}
+\begin{proof}
+Let us begin by reconsidering the previous quantities and 
 \begin{table}[H]
-\begin{tabularx}{\textwidth}{|l| l|X|}
+\centering 
+\begin{tabularx}{\textwidth}{|P{3.5cm}|P{11.85cm}|}
 \hline
-$\Delta \rho(x)$ & \hspace{4cm}$\rho(x-e_1)-\rho(x)$ & $O(\rho(x))$ \\ \hline
-$S\rho(x)$ & \hspace{4cm}$\rho(x-e_1)+\rho(x)$ & $O(\rho(x))$ \\  \hline
-$\Delta \rho(x+e_i)$ &\hspace{3cm} $\rho(x+e_i-e_1)-\rho(x+e_i)$ & $O(\rho(x))$ \\ \hline 
-$S\rho(x + e_i)$ & \hspace{3cm}$\rho(x+e_i-e_1)+\rho(x+e_i)$ & $O(\rho(x))$ \\\hline 
-$\pi^{\scriptscriptstyle(-, i)}_{U}(x)$ &\hspace{4cm} $ \frac{\Delta \rho(x+e_i) -\Delta \rho(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$ & $O(\rho(x))$ \\  \hline
-$\pi^{\scriptscriptstyle(-, i)}_{V}(x)$ & \hspace{4cm}   $\frac{S\rho(x+e_i)-S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  & $O(\rho(x))$ \\  \hline
-$\pi^{\scriptscriptstyle(-, i)}_{W}(x)$ & \hspace{2cm}$\sqrt{2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}} $ & {\tiny$ \sigma^{\scriptscriptstyle (-)}_{i} + O\left(\rho(x)^{2}\right)$}\\
+Variable & upper bound \\ \hline
+$\left|\pi^{\scriptscriptstyle(-, i)}_{U}(x)\right|$ & $\frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$ \\  \hline
+$\left|\pi^{\scriptscriptstyle(-, i)}_{V}(x)\right|$ & $\frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  \\  \hline
+$\left|\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \sigma^{(-)}_{i}\right|$ & $ \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)$ \\ 
 \hline
-$\pi^{\scriptscriptstyle(+, i)}_{U}(x)$ & $ \hspace{4cm} \frac{\Delta \rho(x) + \Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}$ & $O(\rho(x))$  \\ \hline
-$ \pi^{\scriptscriptstyle(+, i)}_{V}(x)$ & \hspace{4cm}$\frac{S \rho(x) + S\rho(x+e_i)}{\sigma^{\scriptscriptstyle (+)}_{i}} $ & $O(\rho(x))$ \\ \hline 
-$ \pi^{\scriptscriptstyle(+, i)}_{W}(x) $ & $\frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) $ & $O\left(\rho(x)^2\right)$\\ \hline
-$\pi^{\scriptscriptstyle(+, i)}_{Z}(x)$ & $ \hspace{2cm} \sqrt{2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}$ & {\tiny$ \sigma^{\scriptscriptstyle (+)}_{i} + O\left(\rho(x)^{2}\right)$} \\\hline
+$|\pi^{\scriptscriptstyle(+, i)}_{U}(x)|$ &  $\frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$   \\ \hline
+$|\pi^{\scriptscriptstyle(+, i)}_{V}(x)|$ &   $\frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  \\ \hline 
+$ \left|\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right| $ & $16r(x)^{2}\left(\sigma^{(-)}_{i} -  \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\right)^{-1}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)$\\ \hline
+$\left|\pi^{\scriptscriptstyle(+, i)}_{Z}(x) - \sigma^{(+)}_{i}\right|$ & $\frac{16r^{2}(x)}{\sigma^{(+)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} +  \frac{\pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}{16r^{2}(x)} \right)$\\\hline
 \end{tabularx}
 \end{table}
-Thus, $\frac{2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}} - \frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} = O(\rho(x))$ and $ \frac{2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+\pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) +\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}} - \frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} = O(\rho(x))$.\\
-Reconsidering Equation (\ref{Thisthofour}) we get,
+Let, $R_{1}(x) = \frac{2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)} - \frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}}$ and $ R_{2}(x) = \frac{2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+\pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) +\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)} - \frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} $.
+Considering $R_{1}(x)$
+{\small
+\begin{align*}
+|R_{1}(x)| = \left|\frac{\sigma^{(+)}_{i}\left(2s + \pi^{\scriptscriptstyle(-, i)}_{W}(x) W\right) - \pi^{\scriptscriptstyle(+, i)}_{Z}(x)\left( 2s +  \sigma^{(-)}_{i}W\right)}{\sigma^{(+)}_{i}\pi^{\scriptscriptstyle(+, i)}_{Z}(x)} \right.\\
+& \hspace{-5cm} \left.
++ \frac{\sigma^{(+)}_{i}\left(\left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \pi^{\scriptscriptstyle(+, i)}_{W}(x) W \right)}{\sigma^{(+)}_{i}\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\right| \\
+& \hspace{-10cm} \text{making use of the previous inequalities, there exist a constant $C_{1} \in \mathbb{R}^{+}$ depending}\\
+& \hspace{-10cm}  \text{on $s, \sigma^{(+)}_{i}, \sigma^{(-)}_{i}$ such that,} \\
+& \hspace{-8.8cm}\leq C_{1}r(x)\left(|U| + |V| + |W|\right)
+\end{align*}}
+Also, there exist $C_2$ such that $R_{2}(x) \leq C_{2}r(x)\left(|U| + |V| + |W|\right)$. 
+Reconsidering Equation~(\ref{Thisthofour}) we get,
 {\small
@@
 & \hspace{-2.5cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right|\right)\\
-& \hspace{-2.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}} \left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right| \right.
+& \hspace{-2.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}} \left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{1}(x)) \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right| \right.
 \right.
@@
  |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq \\
- &  \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right.
+ &  \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{1}(x) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right.
 \right.
@@
  & \hspace{2cm} \left.
-\left.+ \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right|\right) \\
- & \leq \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x)) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right| \right.
+\left.+ \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right|\right) \\
+ & \leq \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + |R_{1}(x)| \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right| \right.
 \\
  & \hspace{2cm} \left.
-+ \left| \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + O(\rho(x))\right)\right|\right),
- \end{align*}
-besides $||\Phi'||_{\infty} \leq \frac{1}{\sqrt{2\pi}}$, thus, there exist a constant $C \in \mathbb{R}^{+}$ such that 
-\begin{align*}
-&  |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| \leq 2C|\rho(x)|. 
-\end{align*}
-Considering $R$ the residue of the sum in the covariance
-\begin{align*}
-|R_{m}| & \leq 4\sum_{x_{\scriptscriptstyle 1} = m}^{\infty}\sum_{x_{\scriptscriptstyle 2}= m}^{\infty}\left(m - x_{1}\right)\left(m - 1- x_{2}\right)|\rho(x)| \\
-& \hspace{1cm}+ \sum_{x_1 = m}^{infty} \sum_{x_2=m}^{\infty}\left(m-x_1-1\right)\left(m-x_2\right)|\rho(x)| \\
-& \hspace{1cm}+ \sum_{x_1 = m}^\infty \sum_{x_2= -\infty}^{\scriptscriptstyle -m}\left(m-x_1-1\right)\left(m+x_2-1\right)|\rho(x)|\\
-& \hspace{1cm}+ \sum_{x_1 = -\infty}^{-m} \sum_{x_2=m}^{\infty}\left(m+x_1\right)\left(m-x_2\right)|\rho(x)|\\
-& \hspace{1cm}+ \sum_{x_1 = -\infty}^{-m} \sum_{x_2=2-m}^{\scriptscriptstyle 0}\left(m+x_1\right)\left(m+x_2-1\right)|\rho(x)|
-\end{align*}
-Then, normalizing properly to have a convergent perimeter, we get that the residue of the sum is bounded by  
-\begin{align*}
-\frac{|R_{m}|}{m^2} & \leq 4C\sum_{x_{\scriptscriptstyle 1} = m+1}^{\infty}\sum_{x_{\scriptscriptstyle 2}= m+1}^{\infty}|\rho(x)| 
-\end{align*}
-thus, a sufficient condition on the covariance structure of the field is that~$\sum_{x \in \mathbb{Z}^{2}} |\rho(x)| <~\infty$.
-
-~\\
-Now, that we know more about how the covariance behave, we can construct a central limit theorem that will lead us to an isotropy test, the first CLT that we will propose follows the same idea as in \cite{Psymetrie}
++ \left| \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right|\right),
+ \end{align*}}
+Applying the mean value theorem, there exist a constant $C \in \mathbb{R}^{+}$ such that 
+\begin{align*}
+ |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq C\mathbb{E}\left(|R_{1}(x)| + |R_{2}(x)|\right) \\
+& \leq Cr(x)
+\end{align*}
+Considering the series $\sum_{x \in \mathbb{Z}^{2}}\left(\mathbbm{1}_{x_{1} \in [2-m, m-2]}\mathbbm{1}_{x_{2} \in [1-m, m-1]} \frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) \right)$
+The limit of the general term as $m$ goes to infinity is
+\begin{align*}
+\lim_{m \to \infty}\frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{x_{1} \in [2-m, m-2]\cap \mathbb{Z}}\mathbbm{1}_{x_{2} \in [1-m, m-1]\cap \mathbb{Z}} \\
+& \hspace{-7cm} =\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{x \in \mathbb{Z}^{2}} 
+\end{align*}
+Besides, we just proved that for $m \in \mathbb{N}$, for all $x\in \mathbb{Z}^{2}$, $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x)\right) \leq Cr(x)$, thus applying the dominated convergence theorem, $\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (i)}(s) \right)$ exists.
+\end{proof}
+Now that we know more about how the covariance behaves, we can construct a Multi-directional multivariate CLT that will lead us to an isotropy test.
 \vspace{-0.5cm}{}
 \subsection{Isotropy test using the oriented perimeter}
-\begin{Theorem}(Multi-directional multivariate CLT for r-threshold). Let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, 
+In order to get the CLT we have to add some assumptions on the covariance structure of the field, we will need the following  assumptions 
+\begin{itemize}
+\item \textbf{$(A_{1})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y)$ exists.
+\item \textbf{$(A_{2})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2}$ exists.
+\end{itemize} 
+\begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
+We consider taht $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
 \begin{equation*}
@@
 \end{equation*}
-where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star$ given by
+where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by
 \begin{align*}
@@
 \end{Theorem}
-\begin{proof}
-Following the idea that has been presented in \cite{Psymetrie}, 
-starting with the well known Cram\`{e}r-Wold method. For the sake of completeness we recall it below.
-\begin{Theorem}[Cram\`{e}r-Wold method, see, \textit{e.g.},  \cite{Billingsley}, p. 383]\label{Cramerwold}
-Let $\overline {X}^{\scriptscriptstyle m} = (X^{m}_{\scriptscriptstyle 1}, \cdots, X^{m}_{\scriptscriptstyle r})$ and $\overline {X} = (X_{\scriptscriptstyle 1}, \cdots, X_{\scriptscriptstyle r})$ be random vectors of dimension $r \geq 1$.
-Then, $\overline {X}^{\scriptscriptstyle m}$ converges in distribution to $\overline {X}$ if and only if
-\begin{center}
-$\sum_{i = 1}^{r} a_{i}X_{i}^{m} \xrightarrow[m \to + \infty]{d} \sum_{i = 1}^{r} a_iX_i,$\end{center}
-for each $(a_1, \cdots, a_r) \in \mathbb{R}^{r}$, \textit{i.e.}, if every fixed linear combination of the coordinates of $\overline{X}^{m}$ converges in distribution to the correspondent linear combination of coordinates of $\overline {X}$.
-\end{Theorem}
+\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalised case is done following the same procedure. Following the idea that has been presented in \cite{Psymetrie}, 
+using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have 
+\begin{align*}
+\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}\right)
+\end{align*}
+with $\sigma^{2} = \lim_{m \to \infty} \mathbb{V}\left( \frac{a_{1}}{m}\mathcal{P}^{\scriptscriptstyle (1)}(t) + \frac{a_{2}}{m}\mathcal{P}^{\scriptscriptstyle (2)}(t) \right)$.
 We first need to recall some notations that were introduced in the first section \eqref{fi}.
-Let $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$  for $i \in \{1,2\}$,  $a^{\scriptscriptstyle (i)}_{1}, \ldots, a^{\scriptscriptstyle (i)}_{r} \in \mathbb{R}$, $t^{\scriptscriptstyle (i)}_{1}, \ldots, t^{\scriptscriptstyle (i)}_{r} \in \mathbb{R}$, $x \in G_{m}$ and $j \in \{1,\ldots,r\}$.
+Let $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$  for $i \in \{1,2\}$,  $a_{1}, a_{2} \in \mathbb{R}$, $t \in \mathbb{R}$, $x \in \mathbb{G}_{m}$ and $j \in \{1,\ldots,r\}$.
 We recall as introduced in \eqref{fi}
 \begin{align*}
-f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t_j \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
-\end{align*}
-Note that $0 \leq f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) \leq 1$ \textit{a.s.} and $|f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x))| \leq 1$, \linebreak thus $|\sum^{2}_{i = 1}\sum_{j=1}^{r} a^{\scriptscriptstyle (i)}_j(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (i)}(x)))| \leq \sum_{i = 1}^{2}\sum_{j =1}^{r} |a^{\scriptscriptstyle (i)}_j|$.
-We note
-\begin{equation}
-\label{X}
-W_{x}^{m} =~\cfrac{1}{m}\sum_{j = 1}^{r}a^{\scriptscriptstyle (1)}_j\big[f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (1)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (1)}(x))) \big] + a^{\scriptscriptstyle (2)}_j\big[f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (2)}(x) - \mathbb{E}(f_{\scriptscriptstyle t_j}^{\scriptscriptstyle (2)}(x))) \big] ,
-\end{equation}
-and finally,
-\begin{equation*}
-S_m = \sum_{x: w_{i}(x) \subset \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}} W_{x}^{m} = \cfrac{1}{m}\sum_{j = 1}^{r}a^{\scriptscriptstyle (1)}_j(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) - \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j))) + a^{\scriptscriptstyle (2)}_j(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) - \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j))) .
-\end{equation*}
-Using the Cram\`{e}r-Wold method, we need to prove that
-\vspace{-0.2cm}
-\begin{equation*}
-S_{m} \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0, \, (\sigma^{\star}_{r})^{2} \right),
-\end{equation*}
-with $(\sigma^{\scriptscriptstyle \star}_{r})^{ \scriptscriptstyle 2} = \sum^{2}_{k = 1}\big[\sum_{j = 1}^{r}(a^{\scriptscriptstyle (k)}_{j})^{2}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(j,j) +  \sum_{0 \leq i < j \leq r} 2a^{\scriptscriptstyle (k)}_{i}a^{\scriptscriptstyle (k)}_{j}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(i,j)\big] + \sum_{0 \leq i < j \leq r}   2a^{\scriptscriptstyle (1)}_{i}a^{\scriptscriptstyle (2)}_{j}(\Sigma_{r}^{\scriptscriptstyle (1, 2)})^{\star}(i,j)$ with .
-To this purpose we use the following weaker version of Theorem 1 of \cite{Lothar} for bounded variables (see p.200 in \cite{Lothar} for details).
-\begin{Proposition}
-\label{tclbis}
-Let $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ for $i \in \{1,2\}$ and $\{X^{m}_{x}, x \in G_{m}\}$ be a sequence of $D$\hspace{-0.05cm}-dependent random field, and $S_m = \sum_{x \in G_{m}} X^{m}_{x}$.
-If the following three conditions are satisfied:
-\begin{enumerate}
-\item[(i)]  $\forall \epsilon > 0$, $\sum_{x \in G_m} \mathbb{P}(|X^{m}_{x}| \geq \epsilon) \xrightarrow[m \to  \infty]{} 0 $,
-\item[(ii)] $\sum_{x \in G_m} \mathbb{E}((X^{m}_{x})^{2}) \leq C < + \infty$,
-\item[(iii)] $\mathbb{E}(S_m) \xrightarrow[m \to  \infty]{} 0$ and $\text{Var}(S_m) \xrightarrow[m \to  \infty]{} \sigma^{2}$ with $\sigma^{2} \in (0,\infty)$,
-\end{enumerate}
-then, $S_m\xrightarrow[m \to  \infty]{d} \mathcal{N}(0, \sigma^{2})$.
-\end{Proposition}
-We start by showing that $\{W^{m}_{x}, x \in G_{m}\}$ satisfies \textit{(i)}. For $\epsilon > 0$, we get~that,
-\begin{align*}
-\sum_{x \in G_m} \mathbb{P}\left(\big|W_{x}^{m}\big| \geq \epsilon\right) & \leq \sum_{x \in G_m}  \cfrac{\mathbb{E}(\big|W_{x}^{m}\big|^{3})}{\epsilon^{3}} \\
-& \leq \cfrac{\left(\sum_{j=1}^{r}|a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{3}\times m(m-1)}{(m\epsilon)^3} \xrightarrow[m \to \infty]{}  0.
-\end{align*}
-To prove that $\{W^{m}_{x}, x\in G_{m}\}$ satisfies \textit{(ii)}, we write
-\begin{align*}
-\sum_{x \in G_m} \mathbb{E}\left(\left(W_{x}^{m}\right)^{2}\right) & \leq m(m-1) \left(\cfrac{1}{m} \sum_{j = 1}^{r} |a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{2}  \leq \left( \sum_{i = 1}^{r} |a^{\scriptscriptstyle (1)}_j| + |a^{\scriptscriptstyle (2)}_j|\right)^{2}.
-\end{align*}
-For \textit{(iii)} we observe that $\text{Var}(S_m) = \text{Var}\left( \sum^{r}_{j = 1}\frac{a^{\scriptscriptstyle (1)}_j}{m}\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) +\frac{a^{\scriptscriptstyle (2)}_j}{m}\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) \right)$ thus, as $m \to \infty$,
-$\text{Var}\left( \sum^{r}_{j = 1}\frac{a^{\scriptscriptstyle (1)}_j}{m}\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_j) +\frac{a^{\scriptscriptstyle (2)}_j}{m}\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_j) \right) \rightarrow \sum^{2}_{k = 1}\big[\sum_{j = 1}^{r}(a^{\scriptscriptstyle (k)}_{j})^{2}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(j,j) +  \sum_{0 \leq i < j \leq r} 2a^{\scriptscriptstyle (k)}_{i}a^{\scriptscriptstyle (k)}_{j}(\Sigma_{r}^{\scriptscriptstyle (k)})^{\star}(i,j)\big] + \sum_{0 \leq i < j \leq r}   2a^{\scriptscriptstyle (1)}_{i}a^{\scriptscriptstyle (2)}_{j}(\Sigma_{r}^{\scriptscriptstyle (1, 2)})^{\star}(i,j)$.
+f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
+\end{align*}
+Note that $0 \leq f_{t}^{\scriptscriptstyle (i)}(x) \leq 1$ \textit{a.s.}, let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$,
+\begin{align*}
+g_{t}\left(\mathbb{X}_{x_1, x_2}\right) & := a_{1}\mathbbm{1}_{\left\{\min\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right) < t \leq \max\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right)\right\}} \\
+& \hspace{1cm} + a_{2}\mathbbm{1}_{\left\{\min\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right) < t \leq \max\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right)\right\}}
+\end{align*}
+Considering the sum over all elements of the window, we get that 
+\begin{align*} 
+\sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) = a_{1}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) - a_{2}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right),
+\end{align*}
+Applying Theorem $2$ in \cite{arcones} we get that 
+\begin{align*}
+m^{-1} \sum_{(x_1, x_2) \in \mathbb{G}_{m}} f_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(f_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}\right),
+\end{align*}
+with 
+\begin{align*}
+\sigma^{2} := \mathbb{E}\left(\big[f_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{0})\right)\big]^{2}\right) \\
+& \hspace{-4cm}+ 2 \sum_{x_{1}, x_{2} = 1}^{\infty} \mathbb{E}\left(\big[f_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{0})\right)\big]\big[f_{t}(\mathbb{X}_{x_1,x_2}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{x_1, x_2})\right)\big]\right)
+\end{align*}
 \end{proof}
-In order to establish the isotropy test,we only need the CLT on the behavior of $ \check{\mathcal{P}}^{\scriptscriptstyle (1)}_{m}(t)$ and $ \check{\mathcal{P}}^{\scriptscriptstyle (2)}_{m}(t)$ at level $t$.To get this result we just need to assume that the field has a covariance kernel is exponentially decaying.
-
-\begin{Theorem}(Multi-directional CLT at level $t$). Let $t \in \mathbb{R}$ , $m \geq 2$, then
-\begin{equation*}
-\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) \end{pmatrix} - \begin{pmatrix} \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)  \\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma^{\star}_{2}\right),
-\end{equation*}
-where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma^{\star}\right)$ for the $2$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^{\star}_{2}$ given by
-\begin{align*}
-\Sigma^{\star}(i,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t), \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t) \right)
-\end{align*}
-\end{Theorem}
-For the proof of this Theorem the main ingredients can be found in \cite{RVY}.
-\begin{proof}
-\begin{Theorem}(CLT for exponentially quasi-local statistics of clustering spin clusters models) Let $G$ be a discrete Cayley graph (basically $\mathbb{Z}^{2}$) and together with $(\epsilon, \mathcal{P})$: if $G$ is $b$-amenable, $\mathcal{P}$ is a clustering spin model with summable $\Phi$, $\left(\sum_{x \in V}\Phi^{1/p}(c|x|) = \sum_{n \geq 0} |\partial W_n| \phi^{1/p}(cn) < \infty \right)$ and $\epsilon$ is a local score function.
-Then you get the CLT.
-\end{Theorem}
-\begin{Corollary}
-Let $\mathcal{H}$ be a stationary Gaussian field, on a discrete Cayley graph $G$ with $X(0)$ having unit variance.
-the level set $\mathcal{P}_{u}$ satisfy exponential clustering constant $C = 2^{12/5}k^{8/5}$, $c_{k} = 1$ and clustering function $\Phi(t) = w(O,x)$.
-\end{Corollary}
-\begin{Definition}
-\end{Definition}(Clustering spin models) We say that $\mathcal{P}$ is a clustering spin model if for all $p,q \geq 1$ there exists constant $C_{p+q}, c_{p+q}$ and a fast decreasing function $\Phi$ ($\Phi \leq 1$,  decreasing and $\lim_{s \to \infty}s^{m}\Phi(s) = 0$ for all $m\geq 1$) such that for all distinct $x_{1}, \ldots, x_{p+q} \in V$ (vertices) we have
-$$|\mathbb{P}\left(\{x_{1}, \ldots, x_{p+q}\} \subset \mathcal{P}\right) - \mathbb{P}\left(\{x_{1}, \ldots, x_{p}\}\subset \mathcal{P}\right)\mathbb{P}\left(\{x_{p+1}, \ldots, x_{p+q}\}\subset \mathcal{P}\right)| \leq C_{p+q}\Phi\left(c_{p+q}s\right)$$
-where $s = d\left(\{x_{1}, \ldots, x_{p}\}, \{x_{p+1}, \ldots, x_{p+q}\}\right)$
-$\rightarrow$ A spin model $\mathcal{P}$ is said to be \textbf{exponentially} if $\mathcal{P}$ is a \textbf{clustering spin} model with $c_{k} \geq c > 0$ and $C_{k} = O(k^{ak})$ for some $a \in [0,1)$and the clustering function satisfies the growth condition $\lim\sup_{t\to \infty}\frac{\log\Phi(t)}{t^{b}} < 0$.
-\end{proof}
+\begin{remark}
+It is possible to generalize the result for $r$-thresholds by applying the same procedure.
+\end{remark}
 \paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.
-
 Let us consider the null hypothesis
@@
 \end{center}
-and consider the following normality asymptotic result.
-
+and the following normality asymptotic result that is obtained by applying the delta method to Theorem (\textcolor{blue}{\ref{TCL}}).
 \begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
@@
 \end{equation*}
-with $\tilde{\sigma}^{2}(t) = \frac{\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t)(\mu^{\star}_{2}(t))^{2} - 2\mu^{\star}_{2}(t)\mu^{\star}_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t) +\tilde{\sigma}_{\scriptscriptstyle 2,2}^{2}(t)\mu^{\star}_{1}(t))^{2}}{\mu^{\star}_{2}(t)^4}$
+with $\tilde{\sigma}^{2}(t) \in (0, \infty)$.
+% with $\tilde{\sigma}^{2}(t) = \frac{\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t)(\mu^{\star}_{2}(t))^{2} - 2\mu^{\star}_{2}(t)\mu^{\star}_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t) +\tilde{\sigma}_{\scriptscriptstyle 2,2}^{2}(t)\mu^{\star}_{1}(t))^{2}}{\mu^{\star}_{2}(t)^4}$
 Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }(t)}$. Then, under $H_{0}$, it holds that
@@
 \end{equation} 
-and $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu^{\star}_{2}(t)^2}$
+% $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu^{\star}_{2}(t)^2}$
 \end{Proposition}
@@
 Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$.
-We define the symmetric accessible test $\hat{\phi}(t)_{m}$ with asymptotic level $\alpha$ as
+We define the symmetric accessible test $\hat{\phi}_{m}(t)$ with asymptotic level $\alpha$ as
 \begin{equation}
 \label{phihat}
-\hat{\phi}(t)_{m}= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|\left(R_{m}(t) - 1 \right)\right| \geq q_{1- \frac{\alpha}{2}} \right\}}
+\hat{\phi}_{m}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|\left(R_{m}(t) - 1 \right)\right| \geq q_{1- \frac{\alpha}{2}} \right\}}
 \end{equation}
@@
 \appendix 
-\section{Three cell configuration}
+\section{Computation of the covariance for the three cell configuration}
+Let us consider the particular case where $x \in \left\{-e_1, e_1, -e_2, e_2 \right\}$, and consider the Gaussian vector $\left(X_{0}, X_{e_1}, X_{x}, X_{x+e_i} \right)$ and its associated transformation $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{x} \right)$ of covariance matrix $\tilde{\Sigma}_{3}(x)$ again assuming that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\sigma}_{3}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},X_{x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W\right) \sim \mathcal{N}\left(0,I_{3}\right)$.
+We get the following decomposition \\
+$\left\{
+\begin{array}{rlc}
+\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+S^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x} & = &  \pi^{\scriptscriptstyle(i)}_{U}(x)U +  \pi^{\scriptscriptstyle(i)}_{V}(x) V +  \pi^{\scriptscriptstyle(i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+\end{array}\right.$ \\
+% with 
+%  $\left\{
+%  \begin{array}{rlc}
+%  \pi_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\rho(x-e_1) - \rho(x)\right) \\
+%  \pi_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(\rho(x-e_1) + \rho(x)\right)  \\
+%  \pi_{W}(x)& = & \left(1 - \pi_{U}(x)^{2} - \pi_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ 
+Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{0}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{0}) \right\}}\right)\\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}+ X_{e_1}, X_{0} + X_{e_1}) \leq s + X_{e_1}\leq \max(X_{\scriptscriptstyle x} + X_{e_1}, X_{0} + X_{e_1}) \right\}}\right).
+\\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{\min(S^{(1)}_{x}, S^{(1)}_{0}) \leq s + \frac{S^{(1)}_{0} + \Delta^{(1)}_{0}}{2}\leq \max(S^{(1)}_{x}, S^{(1)}_{0}) \right\}}\right) \\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \right| \leq \left|S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right|\right\}}\right).
+\end{align*}}
+besides, 
+\begin{align*}
+\mathbbm{1}_{\left\{ \left|2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \right| \leq \left|S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right|\right\}} &= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq  \max\left(s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}, S^{\scriptscriptstyle (1)}_{0}\right) \right\}} \\
+& + \mathbbm{1}_{\left\{  2s + \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  \min\left(s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}, S^{\scriptscriptstyle (1)}_{0}\right) \right\}} \\
+&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s + \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  S^{\scriptscriptstyle (1)}_{0} \right\}} \\
+\end{align*} 
+% \begin{align*}
+% \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \geq 0 \right\}} \mathbbm{1}_{\left\{  - S^{\scriptscriptstyle (1)}_{x} + S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \leq S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right\}} & =\\
+% & \hspace{-4.5cm} \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x}  \geq S^{\scriptscriptstyle (1)}_{0}\right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}}\mathbbm{1}_{\left\{ 2s + \Delta^{(1)}_{0}  + S^{\scriptscriptstyle (1)}_{0} \leq 2S^{\scriptscriptstyle (1)}_{x} \right\}}\\
+% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \geq  - \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right\}}\\
+% & \hspace{1cm} \mathbbm{1}_{\left\{ 2s + \left(\sigma^{(-)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\sigma^{(+)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{V}(x)\right) \leq 2\pi^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
+% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \\
+% & \hspace{-4cm} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W  \geq  \max(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right) \right\}}\\
+% \end{align*}
+
+% \begin{align*}
+% \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \leq 0 \right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \leq -S^{\scriptscriptstyle (1)}_{x} + S^{\scriptscriptstyle (1)}_{0}\right\}} & =\\
+% & \hspace{-4.5cm} \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x}  \leq S^{\scriptscriptstyle (1)}_{0}\right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}}\mathbbm{1}_{\left\{ 2s + \Delta^{(1)}_{0}  + S^{\scriptscriptstyle (1)}_{0} \geq 2S^{\scriptscriptstyle (1)}_{x} \right\}}\\
+% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \leq  - \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right\}}\\
+% & \hspace{-1.7cm} \mathbbm{1}_{\left\{ 2s + \left(\sigma^{(-)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\sigma^{(+)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{V}(x)\right) \geq 2\pi^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
+% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}} \\
+% & \hspace{-4cm} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \leq  \min(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right) \right\}}\\
+% \end{align*}
+Thus, putting everything together, we get 
+{\small 
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{x}, X_{0}) \leq s \leq \max(X_{x}, X_{0}) \right\}}\right) = \\
+& \hspace{-10cm} \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s + \sigma^{(-)}_{1}U\right\}} \left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s + \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right)\right)\\
+& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s + \sigma^{(-)}_{1}U\right\}}\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right) \right)\\\
+\end{align*}
+}
+The second configuration would be to have
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{e_1}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{e_1}) \right\}}\right)\\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}+ X_{0}, X_{e_1} + X_{0}) \leq s + X_{0}\leq \max(X_{\scriptscriptstyle x} + X_{0}, X_{0} + X_{e_1}) \right\}}\right).
+\\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{\min(S^{(1)}_{x}, S^{(1)}_{0}) \leq s + \frac{S^{(1)}_{0} - \Delta^{(1)}_{0}}{2}\leq \max(S^{(1)}_{x}, S^{(1)}_{0}) \right\}}\right) \\
+& \hspace{-6cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \right| \leq \left|S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right|\right\}}\right).
+\end{align*}}
+besides, 
+besides, 
+\begin{align*}
+\mathbbm{1}_{\left\{ \left|2s - \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \right| \leq \left|S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right|\right\}} 
+&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s - \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} - \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s - \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  S^{\scriptscriptstyle (1)}_{0} \right\}} \\
+\end{align*} 
+Thus, putting everything together, we get 
+{\small 
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{x}, X_{0}) \leq s \leq \max(X_{x}, X_{0}) \right\}}\right) = \\
+& \hspace{-10cm}\mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s - \sigma^{(-)}_{1}U\right\}}\right. \\
+& \hspace{-10cm}\left.
+\left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(\max\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s - \left(\frac{1}{2}\sigma^{(-)}_{1}+ \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right) \right)\right)\\
+& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s + \sigma^{(-)}_{1}U\right\}}\right. \\
+& \hspace{-10cm}\left.
+\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(\min\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s - \left(\frac{1}{2}\sigma^{(-)}_{1}+ \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right) \right)\\\
+\end{align*}
+}
+
 Regarding the three cell configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.
@@
 \left(\Phi_{\alpha^{(1)}(e_1)}\left(\min\left(\frac{1 + \rho(2e_1) + 2\rho(e_1)}{\sqrt{2(1-\rho(e_1))}}U + \frac{1-\rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V, s - \frac{\rho(e_1) - \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}} U - \frac{\rho(e_1) + \rho(2e_1)}{\sqrt{2(1+\rho(e_1))}}V \right) \right)\right)\right),
-\end{align}}then if the Gaussian field $\left(X(x)\right)_{x \in G_{m}}$ is such that all the variables are independent, then $\rho(2e_1) = \rho(e_1) = 0$, thus Equation \eqref{IIDCase} becomes 
+\end{align}}then if the Gaussian field $\left(X(x)\right)_{x \in \mathbb{G}_{m}}$ is such that all the variables are independent, then $\rho(2e_1) = \rho(e_1) = 0$, thus Equation \eqref{IIDCase} becomes
 {\small

### 2022-12-06 Draft_GFC.tex
avant modif

@@
 }
+ \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}
 \begin{document}
@@
 They also present an application of the method to  the flow of seawater through the Strait of Gibraltar.
-Tools : a parametric procedure based on the calculation of standard and confidence ellipses, well how do they do that ?
-and what is that.
+Tools : a parametric procedure based on the calculation of standard and confidence ellipses.
 Well, It's pretty weird, they start by considering a sub image $Z_{l,l}$ of the image $Z$ and $Z(s)$ the random variable (yep nothing more on this mystery variable ), from $Z_{l,l}$ they draw $N=\{z_{1}, \ldots, z_{m}\}$ a random sample of $m$ elements, nothing is being said about this random sample.
@@
 \end{cases}
-\end{equation*}We debi
+\end{equation*}
 By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$.
@@
 Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares.
-We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in \mathbb{G}_{m}$, we define $C_{m}(x)$ as
-\begin{equation*}
-C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
-\end{equation*}
-The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
-We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
-Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
+We denote by
+\begin{itemize}
+\item $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ the set of points in $S$
+\item $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$,
+\item for $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.$
+\end{itemize}
+The $C_{m}(x)$ will be referred to as \textit{cells}.
+To ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$ and $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$.
+Each $w \in \mathbb{E}^{(i)}_{m}$ is a segment of length $1$. 
+\begin{remark} The cardinality of the set $\mathbb{E}^{\scriptscriptstyle  (i)}_{m}$
+\label{cardEm}
+\begin{itemize}
+\item 
+$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_1)\subset (0,m)^{2} \right\} $\\ 
+ \hspace*{4.25cm}$ =  \left\{ 1, m - 1\right\}\times\left\{ 0, m-1 \right\},$
+\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_2)\subset (0,m)^{2} \right\} $\\ 
+ \hspace*{4.25cm}$ = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},$
+\end{itemize}
+\end{remark}
+Figure \ref{fig1} shows an example of a square tiling with~$m = 4$.
 \begin{figure}[h]
@@
 \end{figure}
-
+\vspace{-0.5cm}
 \paragraph{Discrete setting}
@@
     \vspace{-2cm}
- \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
+ \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
 \label{fig22}
 \end{figure}
-Let us consider a threshold parameter $t \in \mathbb{R}$.
-We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$.
+Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$.
 \subsection{Perimeter of a binary image}\label{methods}
-For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$.
+For $t \in \mathbb{R}$, let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image at that given threshold $t \in \mathbb{R}$.
 Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$.
@@
 \label{propFisrtmoment}
-We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
-The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and
+We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field.
+Let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
+The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$ where
 \begin{itemize}
@@
 with $N \sim \mathcal{N}(0,1)$. 
-\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(\max\left(0,t\right)\right)\right).$
+\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(|t|\right)\right).$
   \end{itemize}
@@
 \begin{proof}
-Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis, since
-\begin{align*}
-\left\{ x \in \mathbb{G}_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 
-& = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},
-\end{align*}
-one can write that, 
+Let us assume that $\rho(e_{i}) \in ]-1,1]$.
+Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis and Remark \ref{cardEm} one can write that,
 \begin{equation*}
@@
 \end{equation*}
- with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. \\
- We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}\end{equation*}
-Let us introduce the following Lemma, 
-\begin{Lemma}
+ with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$.
+Before going any further, let us first make the following remark,
+ \begin{remark}
 \label{lemmasommediff}
 Let $a,b,t \in \mathbb{R}$, then 
-$$\min(a,b) \leq t \leq \max(a,b) \iff\left|t - \frac{a+b}{2}\right| \leq \left| \frac{ b-a }{2}\right| $$
-\end{Lemma}
+$$\min(a,b) \leq t \leq \max(a,b) \iff\left|2t - (a+b))\right| \leq \left| b-a \right| $$
+\end{remark}
 \begin{proof}
@@
 \draw (8, 0.6) -- (7.75,0.5);
-\node[text width= 1.6cm, font=\large] at (4,1) {$\frac{|b-a|}{2}$};
+\node[text width= 1.6cm, font=\large] at (4,1) {$|b-a|$};
 \node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{b+a}{2}|$};
@@
 \end{figure}
-
 \end{proof}
-Thus, applying the Lemma we get 
-{\small
-\begin{align*}
-\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
-\end{align*}}Besides, the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
+We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}, \end{equation*}
+the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
 -1 & 1 \\
@@
 \end{pmatrix}.$ \\
-Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent, we get the following system
+Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent.
+Hence, we can write
 $\left\{
  \begin{array}{rlc}
-  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \textcolor{white}{(1-\rho(e_i))U + }\\
-  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \textcolor{white}{(1-\rho(e_i))U + } \sqrt{2(1+\rho(e_i)}V, 
+  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1-\rho(e_i))}U, \\
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} & = & \sqrt{2(1+\rho(e_i)}V, 
 \end{array}
-\right.$
+\right.$ \linebreak with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 
+{\small
+\begin{align*}
+\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
+\end{align*}}
 {\small
@@
 \end{align*}}  
-with $U, V \sim \mathcal{N}(0,I_{2})$, thus 
+with $(U, V) \sim \mathcal{N}(0,I_{2})$, thus 
 $$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
@@
 \label{iidCase}
-In the independent case, $\rho(e_i) = 0$, we can write
+In the independent case \textit{i.e.} $\text{Cov}\left(X_{0}, X_i\right) = 0$, we can write
 {\small
@@
 \end{align*}}
-by applying a variable change {\small$\left\{\begin{array}{rcl}
+by applying the variable change {\small$\left\{\begin{array}{rcl}
 u & = & \frac{y - z}{\sqrt{2}} \\
@@
 \begin{remark}
-\label{decreasingrho}
-Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter of the nodal curve ($t=0$).
-\begin{equation*}
- \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(0)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(0)\right),
-\end{equation*}
-where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
-\end{remark}
-\begin{proof}
-One has $\mathbb{E}\left(f^{(i)}(0)\right) = \mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) - \mathbb{E}\left(-\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) = 2\mathbb{E}\left(\frac{\sqrt{1-\rho(e_i)}}{\sqrt{1+\rho(e_i)}}|N|\right) -~1$.
-Since $\rho \mapsto \frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}$ is strictly decreasing, we see that $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is also strictly decreasing.
-\end{proof}
-\begin{remark}
 Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter at level $t$:
 \begin{equation*}
- \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
+ \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
 \end{equation*}
@@
 \begin{proof}
-Let $t \in \mathbb{R}$ and $X$, $Y$ two centered with unit variance Gaussian random fields on $\mathbb{Z}^{2}$ of covariance stucture respectively $\tilde{\rho}$ and $\bar{\rho}$.
-We assume that $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$, and consider the Gaussian vectors $\left(X_{0}, X_{e_1}\right)$ and $\left(Y_{0}, Y_{e_1}\right)$, $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$ implies that $\mathbb{E}\left(X_{0}X_{e_1}\right) < \mathbb{E}\left(Y_{0}Y_{e_1}\right)$, we can write that
-\begin{align*}
-\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) = \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right) - \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right),
-\end{align*}
-according to Slepian's lemma, $\mathbb{P}\left(X_{\scriptscriptstyle 0} < t,  X_{e_1} < t\right) \leq \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right)$, \linebreak besides,~$\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right)=\mathbb{P}\left(X_{\scriptscriptstyle 0} < t\right)$ thus,
-\begin{align*}
-\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) \leq \mathbb{P}\left(X_{\scriptscriptstyle 0} < t \leq  X_{e_1}\right)
-\end{align*}
-and,
-\begin{align*}
-\mathbb{P}\left(\min\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right) < t \leq \max\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right)\right)  \leq \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_1}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_1}\right)\right)
-\end{align*}
-thus, 
-\begin{align*}
-\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
-\end{align*}
+Let $t \in \mathbb{R}$ we can prove this result by considering  the function $$h:x\mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right).
+$$
+with $N \sim \mathcal{N}\left(0,1\right)$, its derivative is equal to 
+\begin{align*}
+h'(x) &= \frac{2\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
+& \int_{0}^{\infty}\exp\left(-\frac{N^{2}}{(1+x)}\right)\left(-4N\cosh\left(\frac{t\sqrt{2(1-x)}}{1+x}\right) + 2t\sqrt{2(1-x)}\sinh\left( \frac{t\sqrt{2(1-x)}}{1+x}\right)\right)dN \\
+& = \frac{-2\exp(-t^2/(1+x))(1+x)}{\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
+& = \frac{-2}{\sqrt{2\pi(1-x^2)}}\exp(-t^2/(1+x)),
+\end{align*}
+for all $|x| < 1, \; h'(x) < 0$, thus, $h$ is a strictly decreasing function. 
 \end{proof}
-\begin{remark}
-Considering the contraposition of this result, we get the following 
-\begin{equation*}
- \text{if} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right)   \hspace{0.5cm} \text{then}  \hspace{0.5cm} \tilde{\rho}(e_i) \neq \bar{\rho}(e_i) \hspace{0.5cm}.
-\end{equation*} 
-\end{remark}
 \subsection{Covariance of the perimeter for two thresholds}
-Let $s, t \in \mathbb{R}$ such that $t \leq s$.
 Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
 \begin{Lemma} 
+Let $s, t \in \mathbb{R}$, 
 \label{CovLemma}
 \begin{align}
-\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \\
-& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) .
+\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \nonumber \\
+& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)),
 \label{covariance}
 \end{align} 
-With 
+with 
 \begin{align*}
@@
 \text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (2)}(s) \right) 
-& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)
+& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right).
 \end{align*}
 \end{Lemma}
-
 \begin{proof}
-Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$, $i = 1$for $t \leq s$. 
+Let us start with the computation of $\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s))$. 
 \begin{align*}
@@
 \begin{align*}
-\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right)
-\end{align*}
-For the second part of \eqref{covariance}, we have still by stationarity
+\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right).
+\end{align*}
+For the last part of \eqref{covariance}, we have still by stationarity
 \begin{align*}
@@
 \end{proof}
-Getting the value of the covariance requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three and four cell structure.
-Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and position on the grid $x$. 
+Getting the value of the covariance $\text{Cov}\left(\mathcal{P}_{m}(t),\mathcal{P}_{m}(s)\right)$ requires the computation of all the \linebreak elements~$\text{Cov}\left(f_{t}^{\scriptscriptstyle (j)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right)$, $i,j \in\{1,2\}$ which has a two, three or four cells structure, depending on the cardinality of the set $\{C_{m}(0), C_{m}(e_1), C_{m}(x), C_{m}(x+e_i)\}$.
+Figure \ref{configurations} below shows the five types of configurations depending on the orientation $i$ and the position of $x$ on the grid. 
 \begin{figure}[H]
@@
 \end{center}
-\caption{Illustration of the two three and four cells configuration involved in the study of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
+\caption{Illustration of the two, three and four cells configuration involved in the computation of $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right)$ in Lemma \ref{CovLemma}.}
 \label{configurations}
 \end{figure}
-Let us first start with the two cell case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, in order to compute it, we just have to apply the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}.
-Thus, We get the next result.
+Let us first start with the two cells case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$.
+Applying the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}, we get the next result.
 \\
@@
 \end{Lemma}
-Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
-\rho(e_1) & 1 & \rho(x-e_1) &  \rho(x+e_i- e_1) \\ 
-\rho(x) & \rho(x-e_1) & 1 & \rho(e_i) \\
-\rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$ 
-Let us define the following quantity  \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
-$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$.
-The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}_{i}(x)~= M\Sigma_{i}(x) M^{\star}}$ with {\small $M = \begin{pmatrix}
--1 & 1 & 0 &  0 \\
-1 & 1 & 0 &  0 \\
-0& 0 & -1 &  1 \\
-0 & 0 & 1 & 1
-\end{pmatrix}$}. Then $\tilde{\Sigma}_{i}(x) = \begin{pmatrix} A_{1} & B_{i}(x) \\ B^{\star}_{i}(x) & A_{i} \end{pmatrix}$
-with 
-$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ and \linebreak {\small $B_{i}(x) =~\begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\
- S\rho(x+e_i)- S\rho(x) &  S\rho(x) + S\rho(x+e_i) 
- \end{pmatrix}$}. The quantity we aim to compute is 
+\begin{Proposition}
+\label{PropositionFourCell}
+Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance of covariance sturcture given by $\rho$, such that $|\rho(e_i)| < 1$
+\vspace{-0.5cm} 
  {\small 
 \begin{align}
-\label{covconf}
-\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right) & = \nonumber \\
-& \hspace{-2.7cm} \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber\\
-& \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
-\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right)\\
-& \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
-\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
-We get the following decomposition \\
-$\left\{
-  \begin{array}{rlc}
-  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z,
-\end{array}\right.$ \\
-with 
+\label{Thisthofour}
+\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right.
+\nonumber\\
+& \hspace{-6cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
+\right.
+\nonumber \\
+& \hspace{-4cm}\left.
+\left.
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
+\end{align}
+}with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$, and \\ 
 $\left\{
@@
  \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
- \end{array}\right.$ 
+ \end{array}\right.$ \\
  $\left\{
@@
 \end{array}\right.$
-\begin{Proposition}
-\label{PropositionFourCell}
-Considering the assumptions above we get 
-{\small 
-\begin{align}
-\label{Thisthofour}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right.
-\nonumber\\
-& \hspace{-6cm} \left.
-\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
-\right.
-\nonumber \\
-& \hspace{-4cm}\left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
-\end{align}
-}with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$.
+
 \end{Proposition}
 \begin{proof}(Proof of Proposition \ref{PropositionFourCell})
-Let us first consider the following indicator function
+Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
+\rho(e_1) & 1 & \rho(x-e_1) &  \rho(x+e_i- e_1) \\ 
+\rho(x) & \rho(x-e_1) & 1 & \rho(e_i) \\
+\rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$ 
+Let us define the following quantities   \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
+\begin{center}
+$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$.
+\end{center}
+The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}_{i}(x)~= M\Sigma_{i}(x) M^{\star}}$ with {\small $M = \begin{pmatrix}
+-1 & 1 & 0 &  0 \\
+1 & 1 & 0 &  0 \\
+0& 0 & -1 &  1 \\
+0 & 0 & 1 & 1
+\end{pmatrix}$}. Then $\tilde{\Sigma}_{i}(x) = \begin{pmatrix} A_{1} & B_{i}(x) \\ B^{\star}_{i}(x) & A_{i} \end{pmatrix}$
+with 
+$A_{i} = \begin{pmatrix} 2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i))\end{pmatrix}$ and \linebreak {\small $B_{i}(x) =~\begin{pmatrix} \Delta \rho(x+e_i) - \Delta \rho(x)&    \Delta \rho(x) + \Delta \rho(x+e_i) \\
+ S\rho(x+e_i)- S\rho(x) &  S\rho(x) + S\rho(x+e_i) 
+ \end{pmatrix}$}. The quantity we aim to compute is 
+{\small
+\begin{align}
+\label{covconf}
+\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right) & = \nonumber \\
+& \hspace{-2.7cm} \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber\\
+& \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
+\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right)\\
+& \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
+\end{align*}} We know that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
+We get the following decomposition \\
+$\left\{
+  \begin{array}{rlc}
+  \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V  } \\
+  S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V,
+  \end{array}\right.$
+  \hspace{-0.9cm} and 
+  $\left\{
+  \begin{array}{rlc}
+  \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z,
+\end{array}\right.$ \\
+with 
+$\left\{
+ \begin{array}{rlc}
+ \sigma^{\scriptscriptstyle (-)}_{1} & = &  \sqrt{2(1-\rho(e_1))} \\
+ \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
+ \end{array}\right.$ \\
+ $\left\{
+ \begin{array}{rlc}
+   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right) \\
+   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ \\
+    $\left\{
+ \begin{array}{rlc}
+   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
+    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
+     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
+   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}.
+\end{array}\right.$ \\
+Developing the indicator function, we get the following expression
 {\small
@@
 _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}\right)\\
-& \hspace{-6.5cm} \text{The variable}\; Z \sim \mathcal{N}\left(0, \pi^{\scriptscriptstyle(+, i)}_{Z}(x)^{2}\right) \text{and} \; \text{$\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ being an increasing function,}\\
-& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
+& \hspace{-6.5cm} \text{The variable}\; \pi^{\scriptscriptstyle(+, i)}_{Z}Z \; \text{follows a} \; \mathcal{N}\left(0, \pi^{\scriptscriptstyle(+, i)}_{Z}(x)^{2}\right) \text{and} \; \text{$\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ being an increasing function, we get}\\
+& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right. \\
 &\hspace{-4cm} \left.
@@
 - \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - \Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x} \right)  \right| \right) \\
-& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
+& \hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right. \\
 &\hspace{-6.2cm} \left.
@@
 \end{proof}
-\begin{remark} In the third cell configuration,the matrix $\Sigma_{i}(x)$ is not positive-definite, thus the Cholesky decomposition does not apply, we have to proceed a differently, but this case is not relevant to the establishment of the Central Limit Theorem, therefor its computations will be presented in the Appendix.
+\begin{remark} In the three cells configuration, the matrix $\Sigma_{i}(x)$ is not positive-definite, thus the Cholesky decomposition does not apply, we have to proceed a differently, but this case is not relevant to the establishment of the Central Limit Theorem, therefor its computations will be presented in the Appendix.
 \end{remark}
 \subsubsection{Spatial independent case} 
-Let us start by considering the four cell configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
-$\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(+, i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thistho} becomes
+Let us start by considering the four cells configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
+$\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(+, i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thisthofour} becomes
 {\small
@@
 \begin{Lemma}
-Let $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$, there exist a constant $C \in \mathbb{R}^{+}$, for all $x \in \mathbb{G}_{m}$
+Let $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$, there exist a constant $C \in \mathbb{R}^{+}$, such that for all $x \in \mathbb{G}_{m}$, we get
 \begin{align*}
@@
 \begin{proof}
-Let us begin by reconsidering the previous quantities and 
-\begin{table}[H]
-\centering 
-\begin{tabularx}{\textwidth}{|P{3.5cm}|P{11.85cm}|}
-\hline
-Variable & upper bound \\ \hline
-$\left|\pi^{\scriptscriptstyle(-, i)}_{U}(x)\right|$ & $\frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$ \\  \hline
-$\left|\pi^{\scriptscriptstyle(-, i)}_{V}(x)\right|$ & $\frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  \\  \hline
-$\left|\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \sigma^{(-)}_{i}\right|$ & $ \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)$ \\ 
-\hline
-$|\pi^{\scriptscriptstyle(+, i)}_{U}(x)|$ &  $\frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}$   \\ \hline
-$|\pi^{\scriptscriptstyle(+, i)}_{V}(x)|$ &   $\frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}$  \\ \hline 
-$ \left|\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right| $ & $16r(x)^{2}\left(\sigma^{(-)}_{i} -  \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\right)^{-1}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)$\\ \hline
-$\left|\pi^{\scriptscriptstyle(+, i)}_{Z}(x) - \sigma^{(+)}_{i}\right|$ & $\frac{16r^{2}(x)}{\sigma^{(+)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} +  \frac{\pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}{16r^{2}(x)} \right)$\\\hline
-\end{tabularx}
-\end{table}
+Let us begin by reconsidering the previous quantities, 
+\begin{itemize}
+  \item if $r(x) = 0$, then, $\pi^{\scriptscriptstyle(-, i)}_{U}(x) = \pi^{\scriptscriptstyle(+, i)}_{U}(x) = \pi^{\scriptscriptstyle(-, i)}_{V}(x) = \pi^{\scriptscriptstyle(+, i)}_{V}(x) = 0$, $\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sigma^{(-)}_{i}$ and~$\pi^{\scriptscriptstyle(+, i)}_{W}(x) = \sigma^{(+)}_{i}$.
+  \item else, reconsidering the expressions above recalling that \linebreak and $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$ we get 
+  \begin{align}
+  \label{nine}
+   \left|\pi^{\scriptscriptstyle(\pm, i)}_{U}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}, \hspace{0.5cm} \left|\pi^{\scriptscriptstyle(-, i)}_{V}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}},
+   \end{align}
+   substracting $\sigma^{(-)}_{i}$ and applying inequality \eqref{nine} we get, 
+   \begin{align}
+   \label{ten}
+   \left|\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \sigma^{(-)}_{i}\right| & \leq \sigma^{(-)}_{i}\left| \left(1 - \frac{\pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2}}{\left(\sigma^{(-)}_{i}\right)^{2}} - \frac{\pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}}{\left(\sigma^{(-)}_{i}\right)^{2}}\right)^{\scriptscriptstyle (1/2)} - 1  \right| \nonumber \\
+   & \leq \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)
+   \end{align}
+   from \eqref{nine} and \eqref{ten}, we also get
+   \begin{align}
+   \label{eleven}
+  \left|\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right| & = \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \nonumber \\
+  &\leq 16r(x)^{2}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\left(\sigma^{(-)}_{i} -  \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\right)^{-1}
+  \end{align}
+ finally, from \eqref{nine} and \eqref{eleven}
+  \begin{align}
+  \left|\pi^{\scriptscriptstyle(+, i)}_{Z}(x) - \sigma^{(+)}_{i}\right| \leq \frac{16r^{2}(x)}{\sigma^{(+)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} +  \frac{\pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}{16r^{2}(x)} \right)
+  \end{align}
+\end{itemize} 
 Let, $R_{1}(x) = \frac{2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)} - \frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}}$ and $ R_{2}(x) = \frac{2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+\pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) +\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W}{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)} - \frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} $.
@@
 Reconsidering Equation~(\ref{Thisthofour}) we get,
-{\small
-\begin{align*}
- \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) & =  \\ 
- & \hspace{-2.5cm} \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\right. \\
-&\hspace{-2.5cm} \left.
+\pagebreak
+{\small
+\begin{align*}
+ \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) & =  \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right.
+\\
+&\hspace{-3cm} \left.
 \left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right.
@@
 \nonumber \\
-& \hspace{-2.5cm}\left.
+& \hspace{-3cm}\left.
 \left.
 - \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+ \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+ \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V   - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right) \\
-& \hspace{-2.5cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}}\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right|\right)\\
-& \hspace{-2.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sigma^{\scriptscriptstyle (+)}_{1}V}{2}| \leq |\frac{\sigma^{\scriptscriptstyle (-)}_{1}U}{2}|\right\}} \left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{1}(x)) \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right| \right.
+& \hspace{2cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right|\right)\\
+& \hspace{-3cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}} \left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{1}(x)) \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right| \right.
 \right.
 \\
-& \hspace{4.75cm} \left.\left.
+& \hspace{4cm} \left.\left.
 -  \left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} \right)\right| \right)\right),
@@
 \left.+ \Phi\left(\frac{2s - \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) - \Phi\left(\frac{2s -\sigma^{\scriptscriptstyle (-)}_{i}W }{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{2}(x))\right)\right|\right) \\
- & \leq \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + |R_{1}(x)| \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right| \right.
+ & \leq \mathbb{E}\left(\left|\Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} + R_{1}(x) \right)  - \Phi\left(\frac{2s + \sigma^{\scriptscriptstyle (-)}_{i}W}{\sigma^{\scriptscriptstyle (+)}_{i}} \right) \right| \right.
 \\
@@
 \begin{align*}
- |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq C\mathbb{E}\left(|R_{1}(x)| + |R_{2}(x)|\right) \\
+ |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq C\mathbb{E}\left(|R_{1}(x)| + |R_{2}(x)|\right). \\
 & \leq Cr(x)
 \end{align*}
-Considering the series $\sum_{x \in \mathbb{Z}^{2}}\left(\mathbbm{1}_{x_{1} \in [2-m, m-2]}\mathbbm{1}_{x_{2} \in [1-m, m-1]} \frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) \right)$
-The limit of the general term as $m$ goes to infinity is
-\begin{align*}
-\lim_{m \to \infty}\frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{x_{1} \in [2-m, m-2]\cap \mathbb{Z}}\mathbbm{1}_{x_{2} \in [1-m, m-1]\cap \mathbb{Z}} \\
-& \hspace{-7cm} =\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{x \in \mathbb{Z}^{2}} 
-\end{align*}
-Besides, we just proved that for $m \in \mathbb{N}$, for all $x\in \mathbb{Z}^{2}$, $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x)\right) \leq Cr(x)$, thus applying the dominated convergence theorem, $\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (i)}(s) \right)$ exists.
+We will prove the result for $i =1$, the other cases can be proven using the same arguments, let $x \in \mathbb{Z}^{2}$, considering the serie $\sum_{x \in \mathbb{Z}^{2}}\left(\mathbbm{1}_{|x_{1}| \leq m-2]}\mathbbm{1}_{|x_{2}| \leq m-1} \frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right) \right)$,
+the limit of the general term as $m$ goes to infinity is
+\begin{align*}
+\lim_{m \to \infty}\cfrac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{|x_{1}| \leq m-2]}\mathbbm{1}_{|x_{2}| \leq m-1}  \\
+& \hspace{-7cm} =\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right)
+\end{align*}
+Besides, we just proved that for $m \in \mathbb{N}$, for all $x\in \mathbb{Z}^{2}$, $\left|\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x)\right)\right| \leq Cr(x)$, thus applying the dominated convergence theorem, $\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right)$ exists.
 \end{proof}
-Now that we know more about how the covariance behaves, we can construct a Multi-directional multivariate CLT that will lead us to an isotropy test.
-\vspace{-0.5cm}{}
+Now that we know more about the second moment of the perimeter, we can construct a Multi-directional multivariate CLT that will lead us to an isotropy test, the following Central Limit Theorem is proved with a lesser condition on the covariance of the field.
+\vspace{-0.5cm}
 \subsection{Isotropy test using the oriented perimeter}
@@
 \begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
-We consider taht $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
+We consider that $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
 \begin{equation*}
@@
 \label{phihat}
-\hat{\phi}_{m}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|\left(R_{m}(t) - 1 \right)\right| \geq q_{1- \frac{\alpha}{2}} \right\}}
+\hat{\phi}_{m}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|R_{m}(t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
 \end{equation}
-\begin{remark}(Power of the statistical test for the level $t = 0$) In Remark \ref{decreasingrho} we showed that the function $\rho \mapsto 2\mathbb{E}\left(\frac{\sqrt{1-\rho}}{\sqrt{1+\rho}}|N|\right) - 1 $ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(0)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(0)\right)} \neq 1$.
+\begin{remark}(Power of the statistical test at a level $t$) In Remark \ref{decreasingrho} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(t)\right)} \neq 1$.
 \end{remark}
@@
   \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent $p_{\text{value}}$  of the test see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+\begin{displaymath}
+  \renewcommand{\arraystretch}{1.5}
+\begin{array}{|C{0.4cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|}
+\hline
+b & 0.1190 &  0.3571 &  0.5952 &  0.8333 &  1.0714 &  1.3095 &  1.5476 &  1.7857 &  2.0238 &  2.2619 &  2.5 \\ \hline
+1  & 0.9971 &  0.9879 &  0.9547 &  0.9956 &  0.9800 &  0.9973 &  0.9997 &  0.9897 &  0.9737 &  0.9858 &  0.9816  \\ \hline
+1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007 &  0.0052 &  0.0325 &  0.1036 \\ \hline
+1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0001 &  0.0035 \\ \hline 
+1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 \\ \hline
+2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 \\ \hline
+\end{array}
+\end{displaymath}
+
+\begin{figure}[H]
+  \centering
     {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
@@
 \appendix 
-\section{Computation of the covariance for the three cell configuration}
-Let us consider the particular case where $x \in \left\{-e_1, e_1, -e_2, e_2 \right\}$, and consider the Gaussian vector $\left(X_{0}, X_{e_1}, X_{x}, X_{x+e_i} \right)$ and its associated transformation $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{x} \right)$ of covariance matrix $\tilde{\Sigma}_{3}(x)$ again assuming that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\sigma}_{3}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},X_{x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W\right) \sim \mathcal{N}\left(0,I_{3}\right)$.
+\section{Computation of the covariance for the three cells configuration}
+Let us consider the particular case where $\left\{ X_{0}, X_{e_1}\right\} \cap \left\{ X_{x}, X_{x+e_i}\right\} \neq \emptyset $,
+ % $x \in \left\{-e_1, e_1, -e_2, e_2, (1,-1) \right\}$, 
+ we associate to the Gaussian vector $\left(X_{0}, X_{e_1}, X_{x}, X_{x+e_i} \right)$ and the transformed vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{x} \right)$ of covariance matrix $\tilde{\Sigma}_{3}(x)$ again assuming that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{3}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},X_{x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W\right) \sim \mathcal{N}\left(0,I_{3}\right)$.
 We get the following decomposition \\
@@
 \end{array}\right.$ \\
-% with 
-%  $\left\{
-%  \begin{array}{rlc}
-%  \pi_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\rho(x-e_1) - \rho(x)\right) \\
-%  \pi_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(\rho(x-e_1) + \rho(x)\right)  \\
-%  \pi_{W}(x)& = & \left(1 - \pi_{U}(x)^{2} - \pi_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ 
 Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
@@
 & + \mathbbm{1}_{\left\{  2s + \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  \min\left(s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}, S^{\scriptscriptstyle (1)}_{0}\right) \right\}} \\
-&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s + \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  S^{\scriptscriptstyle (1)}_{0} \right\}} \\
-\end{align*} 
-% \begin{align*}
-% \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \geq 0 \right\}} \mathbbm{1}_{\left\{  - S^{\scriptscriptstyle (1)}_{x} + S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \leq S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right\}} & =\\
-% & \hspace{-4.5cm} \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x}  \geq S^{\scriptscriptstyle (1)}_{0}\right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}}\mathbbm{1}_{\left\{ 2s + \Delta^{(1)}_{0}  + S^{\scriptscriptstyle (1)}_{0} \leq 2S^{\scriptscriptstyle (1)}_{x} \right\}}\\
-% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \geq  - \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right\}}\\
-% & \hspace{1cm} \mathbbm{1}_{\left\{ 2s + \left(\sigma^{(-)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\sigma^{(+)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{V}(x)\right) \leq 2\pi^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \\
-% & \hspace{-4cm} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W  \geq  \max(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right) \right\}}\\
-% \end{align*}
-
-% \begin{align*}
-% \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \leq 0 \right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \leq -S^{\scriptscriptstyle (1)}_{x} + S^{\scriptscriptstyle (1)}_{0}\right\}} & =\\
-% & \hspace{-4.5cm} \mathbbm{1}_{\left\{ S^{\scriptscriptstyle (1)}_{x}  \leq S^{\scriptscriptstyle (1)}_{0}\right\}} \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}}\mathbbm{1}_{\left\{ 2s + \Delta^{(1)}_{0}  + S^{\scriptscriptstyle (1)}_{0} \geq 2S^{\scriptscriptstyle (1)}_{x} \right\}}\\
-% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \leq  - \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right\}}\\
-% & \hspace{-1.7cm} \mathbbm{1}_{\left\{ 2s + \left(\sigma^{(-)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\sigma^{(+)}_{1} - 2\pi^{\scriptscriptstyle(i)}_{V}(x)\right) \geq 2\pi^{\scriptscriptstyle(i)}_{W}(x) W \right\}} \\
-% & \hspace{-5cm} = \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \geq 2s + \Delta^{(1)}_{0}\right\}} \\
-% & \hspace{-4cm} \mathbbm{1}_{\left\{\pi^{\scriptscriptstyle(i)}_{W}(x) W \leq  \min(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right) \right\}}\\
-% \end{align*}
+&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s + \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s + \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} + \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0} \right\}} \\
+\end{align*} 
 Thus, putting everything together, we get 
@@
 \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{x}, X_{0}) \leq s \leq \max(X_{x}, X_{0}) \right\}}\right) = \\
-& \hspace{-10cm} \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s + \sigma^{(-)}_{1}U\right\}} \left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s + \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right)\right)\\
-& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s + \sigma^{(-)}_{1}U\right\}}\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right) \right)\\\
-\end{align*}
-}
-The second configuration would be to have
+& \hspace{-10cm} \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V\right| \leq  \left|\sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s + \sigma^{(-)}_{1}U\right\}} \left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right)\right)\\
+& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{\left|2t - \sigma^{(+)}_{1}V\right|\leq  \left|\sigma^{(-)}_{1}U\right|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s + \sigma^{(-)}_{1}U\right\}}\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s + \left(\frac{1}{2}\sigma^{(-)}_{1}- \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right) \right)\\\
+\end{align*}
+}
+For the second configuration, we would then have,
 {\small
@@
 besides,  
-besides, 
 \begin{align*}
 \mathbbm{1}_{\left\{ \left|2s - \Delta^{(1)}_{0} -  S^{\scriptscriptstyle (1)}_{x}  \right| \leq \left|S^{\scriptscriptstyle (1)}_{x} - S^{\scriptscriptstyle (1)}_{0}\right|\right\}} 
-&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s - \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} - \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s - \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  S^{\scriptscriptstyle (1)}_{0} \right\}} \\
+&= \mathbbm{1}_{\left\{  S^{\scriptscriptstyle (1)}_{0} \leq 2s - \Delta^{(1)}_{0}\right\}} \mathbbm{1}_{\left\{ S_{x} \geq s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} - \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0}\right\}} + \mathbbm{1}_{\left\{  2s - \Delta^{(1)}_{0} \leq S^{\scriptscriptstyle (1)}_{0} \right\}} \mathbbm{1}_{\left\{ S_{x} \leq  s+ \frac{1}{2}S^{\scriptscriptstyle (1)}_{0} - \frac{1}{2}\Delta^{\scriptscriptstyle (1)}_{0} \right\}} \\
 \end{align*} 
@@
 \begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{x}, X_{0}) \leq s \leq \max(X_{x}, X_{0}) \right\}}\right) = \\
-& \hspace{-10cm}\mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s - \sigma^{(-)}_{1}U\right\}}\right. \\
-& \hspace{-10cm}\left.
-\left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(\max\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s - \left(\frac{1}{2}\sigma^{(-)}_{1}+ \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right) \right)\right)\\
-& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V \leq  \sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s + \sigma^{(-)}_{1}U\right\}}\right. \\
-& \hspace{-10cm}\left.
-\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(\min\left(- \pi^{\scriptscriptstyle(i)}_{U}(x)U + \left(\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V, s - \left(\frac{1}{2}\sigma^{(-)}_{1}+ \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right) \right)\\\
-\end{align*}
-}
-
-Regarding the three cell configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.
+\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{x}, X_{e_1}) \leq s \leq \max(X_{x}, X_{e_1}) \right\}}\right) = \\
+& \hspace{-10cm} \mathbb{E}\left(\mathbbm{1}_{\left\{|2t - \sigma^{(+)}_{1}V\right| \leq  \left|\sigma^{(-)}_{1}U|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \leq 2s - \sigma^{(-)}_{1}U\right\}} \left(1 - \Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s - \left(\frac{1}{2}\sigma^{(-)}_{1} + \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1} - \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right)\right)\right)\\
+& \hspace{-10cm}+ \mathbb{E}\left(\mathbbm{1}_{\left\{\left|2t - \sigma^{(+)}_{1}V\right|\leq  \left|\sigma^{(-)}_{1}U\right|\right\}}\mathbbm{1}_{\left\{ \sigma^{(+)}_{1}V  \geq 2s - \sigma^{(-)}_{1}U\right\}}\Phi_{\pi^{\scriptscriptstyle(i)}_{W}(x) }\left(s - \left(\frac{1}{2}\sigma^{(-)}_{1} + \pi^{\scriptscriptstyle(i)}_{U}(x)\right)U  +  \left(\frac{1}{2}\sigma^{(+)}_{1}- \pi^{\scriptscriptstyle(i)}_{V}(x)\right)V\right) \right)\\\
+\end{align*}
+}
+
+Regarding the three cells configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.
 Thus, those computations would give us the following expression,

### 2022-12-16 Draft_GFC.tex
Version avant les vacances avec linkage des parties

@@
 \usepackage{relsize}
+\usepackage{diagbox}
 \newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
@@
 \usepackage{array}
+\usepackage{enumitem}
+\newcounter{Ax}
+\newcommand{\itemA}{%
+    \addtocounter{Ax}{1}
+    \item[A\theAx.]}
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of $Z^{\scriptscriptstyle (m)}$.
-\begin{Definition}[Perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
-For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x)$ the  sum of all vertical contributions for $i = 1$ and horizontal ones for $i = 2$.
-Then, the perimeter of the binary image $Z$ is given by
+\begin{Definition}[Directional perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
+For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical and horizontal).
+Then, the directional perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
 \begin{equation}
-\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t).
+\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).
  \label{eq:6}
 \end{equation}
+Then, the perimeter of $Z^{\scriptscriptstyle (m)}$ is given by $\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t)$.
 \end{Definition}
-\section{Statistics of the perimeter} 
+\section{Statistics of the oriented perimeter} 
 \subsection{First moment}
-Let us start this study by investigating the first moment of the perimeter.
-\begin{Proposition}[First moment of the perimeter] 
+Let us start this study by investigating the first moment of the oriented perimeter.
+\begin{Proposition}[First moment of the directional perimeter] 
 \label{propFisrtmoment}
 We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field.
-Let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$.
-The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$ where
+Let $i \in \{1,2\}$ and let us denote by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in [-1, 1]$.
+The expected value of the perimeter in \eqref{eq:6} is  given by $$\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)\right) = m(m-1)\mathbb{E}\left(f^{(i)}(t) \right)$$ where
 \begin{itemize}
@@
 & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
-\end{align*}}
-{\small
-\begin{align*}
-\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq 2t - \sqrt{2(1+\rho(e_i)}V \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\
+\\
+& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq  \sqrt{2(1+\rho(e_i)}V -2t \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\
 & = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}  \leq V \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right), 
 \end{align*}}  
-with $(U, V) \sim \mathcal{N}(0,I_{2})$, thus 
+thus,
 $$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
@@
 \begin{remark}
-In order to have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window ($m^2$), considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.
+To have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window $S$, ($m^2$), thus considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.
 \end{remark}
-The total variation of an image $u \in L^{1}_{loc}(\Omega)$ is given by $\int_{\Omega}|\nabla u|dx$ which is equal by the coarea formula to $\int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$ .
+\textcolor{red}{
+It is possible to link the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ to its perimeter, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.}
 \begin{Proposition}
@@
 \end{remark}
+\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance~$\rho$.}
 \begin{remark}
-Considering $\tilde{\rho}(e_i), \bar{\rho}(e_i)$ two covariance, we  have the following result concerning the expected perimeter at level $t$:
+\label{powertest}
+\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure, we  have the following result regarding their associated expected oriented perimeter at level $t$:}
 \begin{equation*}
@@
 \end{equation*}
-Where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance $\tilde{\rho}$. 
 \end{remark}
 \begin{proof}
-Let $t \in \mathbb{R}$ we can prove this result by considering  the function $$h:x\mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right).
-$$
+Let $t \in \mathbb{R}$ we can prove this result by considering  the function \begin{align*} 
+h: (-1,1) &\longrightarrow \mathbb{R}, \\
+x & \longmapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right),
+\end{align*}
 with $N \sim \mathcal{N}\left(0,1\right)$, its derivative is equal to 
 \begin{align*}
-h'(x) &= \frac{2\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
-& \int_{0}^{\infty}\exp\left(-\frac{N^{2}}{(1+x)}\right)\left(-4N\cosh\left(\frac{t\sqrt{2(1-x)}}{1+x}\right) + 2t\sqrt{2(1-x)}\sinh\left( \frac{t\sqrt{2(1-x)}}{1+x}\right)\right)dN \\
-& = \frac{-2\exp(-t^2/(1+x))(1+x)}{\sqrt{2\pi}(1-x)^{1/2}(1+x)^{3/2}}\\
-& = \frac{-2}{\sqrt{2\pi(1-x^2)}}\exp(-t^2/(1+x)),
-\end{align*}
-for all $|x| < 1, \; h'(x) < 0$, thus, $h$ is a strictly decreasing function. 
+h'(x) & = \mathbb{E}\left( \left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right. \\
+& \hspace{5cm} \left. - \left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right)\\
+& = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
+& \hspace{6cm}  \left. - \frac{2|N| - t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
+& = \frac{1}{2(1+x)\sqrt{1-x^2}}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
+& \hspace{5.5cm}  \left. - \left(2|N| - t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
+& = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
+&\hspace{0.5cm} \mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right. \\
+&\hspace{2cm}\left. - \left(2|N| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
+& = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}}\\
+&\hspace{0.5cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right. \\
+&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy \\ 
+& = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
+&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
+&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
+& = \frac{\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
+& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
+& = \frac{-2\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
+& = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}},
+\end{align*}
+for all $|x| < 1, \; h'(x) < 0$ thus, $h$ is a strictly decreasing function. 
 \end{proof}
-\subsection{Covariance of the perimeter for two thresholds}
+\textcolor{red}{Thus, the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, in particular if $\rho(e_1) \neq \rho(e_2) $\linebreak then~$\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$.\\
+Now, if the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$.
+Thus, having a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$  would allow us to construct an isotropy test using the oriented perimeter of the field $X$.}
+\subsection{Isotropy test using the oriented perimeter}
+In order to establish the CLT, we need to add some assumptions on $\rho$ the covariance structure of the field $X$.
+\begin{enumerate}
+  \itemA 
+ $\begin{aligned}[t]
+ \label{conditionTCL1}
+\lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y)\; \text{exists}.
+\end{aligned}$
+\itemA $\begin{aligned}[t]
+ \lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2}\; \text{exists}.
+\end{aligned}$
+\end{enumerate} 
+\textcolor{red}{TCL}
+\begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
+We consider that $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
+\begin{equation*}
+\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
+\end{equation*}
+where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by
+\begin{align*}
+\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
+\end{align*}
+\end{Theorem}
+\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalized case is made by following the same procedure.
+Using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have
+\begin{align*}
+\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right)
+\end{align*}
+with $\sigma^{2}(t) = \lim_{m \to \infty} \mathbb{V}\left( \frac{a_{1}}{m}\mathcal{P}^{\scriptscriptstyle (1)}(t) + \frac{a_{2}}{m}\mathcal{P}^{\scriptscriptstyle (2)}(t) \right)$.
+We first need to recall some notations that were introduced in the first section \eqref{fi}.
+We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ and let~$a_{1}, a_{2}, t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$.
+We recall as introduced in \eqref{fi}
+\begin{align*}
+f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
+\end{align*}
+Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 
+\begin{align*}
+g_{t}\left(\mathbb{X}_{x_1, x_2}\right) & := a_{1}\mathbbm{1}_{\left\{\min\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right) < t \leq \max\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right)\right\}} \\
+& \hspace{1cm} + a_{2}\mathbbm{1}_{\left\{\min\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right) < t \leq \max\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right)\right\}}
+\end{align*}
+Note that $0 \leq f_{t}^{\scriptscriptstyle (i)}(0) \leq 1$ \textit{a.s.}, thus, \textit{a.s.},$\mathbb{E}\left(g_{t}\left(\mathbb{X}_{\scriptscriptstyle  0, 0}\right)^{2}\right) < (a_{1} + a_{2})^{2}$.
+In order to apply Theorem $2$ in \cite{arcones} and get the convergence, \\
+\big[\textcolor{blue}{ $r^{(p,q )}(k) = \mathbb{E}\left(X^{p}_{m} X^{q}_{m+k}\right)$for $k\in Z$ and $1 < p, q < d$, where $m$ is any integer so large that $m, m + k > 1$. Suppose that \\
+$\lim_{n \to \infty} n^{-1} \sum_{j,k = 1}^{n}r^{(p,q )}(j-k) < \infty$ and $\lim_{m \to \infty} n^{-1}\sum_{j,k = 1}^{n}(r^{(p,q )}(j-k))^{2} < \infty$}\big]\\
+we should insure that 
+\begin{align*}
+\lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right) < \infty \; \text{and} \; \lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \left(\mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right)\right)^{2} < \infty,
+\end{align*} 
+with $\mathbb{X}^{(p)}_{x}$ being the $p$-coordinate of the $4$-dimensional vector $\mathbb{X}_{x}$, then applying the stationarity hypothesis it amounts to the following
+\begin{align*}
+\lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y) < \infty \;  \text{and} \; \lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2} < \infty.
+\end{align*} 
+Under $(A1)$ and $(A2)$, we can apply Theorem $2$ in \cite{arcones} we get that 
+\begin{align*}
+m^{-1} \sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right),
+\end{align*}
+with 
+\begin{align*}
+\sigma^{2}(t) := \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]^{2}\right) \\
+& \hspace{-4cm}+ 2 \sum_{x_{1}, x_{2} = 1}^{\infty} \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]\big[g_{t}(\mathbb{X}_{x_1,x_2}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{x_1, x_2})\right)\big]\right)
+\end{align*}
+Re-writing the sum we get
+\begin{align*} 
+\sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \\
+&=  a_{1}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) - a_{2}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right),
+\end{align*}
+Thus
+\begin{align*}
+\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right)
+\end{align*}
+\end{proof}
+\paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.
+Let us consider the null hypothesis
+\begin{center}
+  $H_{0}$ \, :\; The field $X$ is isotropic,
+\end{center}
+and the following normality asymptotic result that is obtained by applying the delta method to Theorem (\textcolor{blue}{\ref{TCL}}).
+\begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
+Let  $t \in \mathbb{R}$, and $\mathcal{P}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre} computed at level $t$ let us denote by $\mu_{i}(t)) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)$.
+Then, it holds that,
+\begin{equation*}
+\frac{1}{m}\left(\cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)} - \cfrac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)} \right)  \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t) \right),
+\end{equation*}
+with $\tilde{\sigma}^{2}(t) = \frac{(\tilde{\sigma}_{\scriptscriptstyle 1,1}(t)\mu_{2}(t))^{2} - 2\mu_{2}(t)\mu_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}(t)^{2} +(\tilde{\sigma}_{\scriptscriptstyle 2,2}(t)\mu_{1}(t))^{2}}{\mu_{2}(t)^4} \in (0, \infty)$.
+\\
+Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)}$. Then, under $H_{0}$, it holds that
+\begin{equation}\label{ratiounderH0}
+\frac{1}{m}\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
+\end{equation} 
+and $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu_{2}(t)^2}$.
+\end{Proposition}
+Consider the consistent empirical estimator $\hat{\sigma}_{m,n}(t):= \frac{1}{m^2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m, n}(t)\right)}$ is the empirical variance of the considered ratio computed with Montecarlo $= n$.
+Then, from \ref{deltamethodgeneralprop}, it holds that
+$$ \frac{1}{m\sqrt{\hat{\sigma}_{m,n}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
+Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$.
+We define the symmetric accessible test $\hat{\phi}_{m, n}(t)$ with asymptotic level $\alpha$ as
+\begin{equation}
+\label{phihat}
+\hat{\phi}_{m,n}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}\left|R_{m}((t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
+\end{equation}
+\begin{remark}(Power of the statistical test at a level $t$) In Remark \ref{powertest} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(t)\right)} \neq 1$.
+\end{remark}
+\section{Numerical studies}
+\subsection{Numerical studies of moments of the estimated perimeter}
+Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/3C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
+Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
+\begin{equation}
+A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
+\end{equation}
+with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{X}(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C},$, note that $a\neq b$ if and only if $Y$ is anisotropic.
+We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$.
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
+}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{Testanisotropy2.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
+    \hspace{0.2cm} 
+ \caption{$p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+\diagbox{b}{t} & 0.2 &  0.3 &  0.4 &  0.5 &  0.6 &  0.7 &  0.8 &  0.9  \\ \hline
+1  & 0.9866 &   0.9638 &  0.9971 &  0.9867 &  0.9674 &  0.9951 &  0.9754 &  0.9918  \\ \hline
+1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007  \\ \hline
+1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline 
+1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline
+2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0  \\ \hline
+\end{tabular}
+\end{center}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/3, \pi/4, \pi/5, \pi/6, \pi/8 $ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.2]{TestaniRatiovsRHO.pdf}}
+    {\includegraphics[scale=0.2]{TestaniRatiovsTVA.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{imageU.pdf}}
+    \hspace{3cm}
+    {\includegraphics[scale=0.3]{levelset30000.pdf}}
+    \hspace{0.2cm}
+ \caption{ Image of level $30000$}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.25]{ConfidenceIntervalRDStD.pdf}}
+    {\includegraphics[scale=0.25]{BoxplotRDStD.pdf}}
+    \hspace{0.2cm}
+ \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.25]{ConfidenceIntervalRDAu.pdf}}
+    {\includegraphics[scale=0.25]{BoxplotRDAu.pdf}}
+    \hspace{0.2cm}
+ \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
+\label{fig2}
+\end{figure}
+\subsection{Theroretical and numerical study of the covariance of the perimeter}
 Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
@@
 \label{CovLemma}
-\begin{align}
-\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)) + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (1)}(s)) \nonumber \\
-& + \text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (2)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (2)}(s)),
-\label{covariance}
-\end{align} 
+\begin{align*}
+\text{Cov}(\mathcal{P}_{m}(t), \mathcal{P}_{m}(s))  & = \sum_{1\leq i,j\leq 2}\text{Cov}(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t), \mathcal{P}_{m}^{\scriptscriptstyle (j)}(s)) 
+\end{align*} 
 with 
@@
 Reconsidering Equation~(\ref{Thisthofour}) we get,
-\pagebreak
 {\small
@@
 \end{proof}
-Now that we know more about the second moment of the perimeter, we can construct a Multi-directional multivariate CLT that will lead us to an isotropy test, the following Central Limit Theorem is proved with a lesser condition on the covariance of the field.
-\vspace{-0.5cm}
-\subsection{Isotropy test using the oriented perimeter}
-In order to get the CLT we have to add some assumptions on the covariance structure of the field, we will need the following  assumptions 
-\begin{itemize}
-\item \textbf{$(A_{1})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y)$ exists.
-\item \textbf{$(A_{2})$} $\lim_{n \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2}$ exists.
-\end{itemize} 
-\begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
-We consider that $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
-\begin{equation*}
-\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
-\end{equation*}
-where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by
-\begin{align*}
-\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
-\end{align*}
-\end{Theorem}
-\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalised case is done following the same procedure. Following the idea that has been presented in \cite{Psymetrie}, 
-using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have 
-\begin{align*}
-\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}\right)
-\end{align*}
-with $\sigma^{2} = \lim_{m \to \infty} \mathbb{V}\left( \frac{a_{1}}{m}\mathcal{P}^{\scriptscriptstyle (1)}(t) + \frac{a_{2}}{m}\mathcal{P}^{\scriptscriptstyle (2)}(t) \right)$.
-We first need to recall some notations that were introduced in the first section \eqref{fi}.
-Let $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$  for $i \in \{1,2\}$,  $a_{1}, a_{2} \in \mathbb{R}$, $t \in \mathbb{R}$, $x \in \mathbb{G}_{m}$ and $j \in \{1,\ldots,r\}$.
-We recall as introduced in \eqref{fi}
-\begin{align*}
-f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
-\end{align*}
-Note that $0 \leq f_{t}^{\scriptscriptstyle (i)}(x) \leq 1$ \textit{a.s.}, let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$,
-\begin{align*}
-g_{t}\left(\mathbb{X}_{x_1, x_2}\right) & := a_{1}\mathbbm{1}_{\left\{\min\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right) < t \leq \max\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right)\right\}} \\
-& \hspace{1cm} + a_{2}\mathbbm{1}_{\left\{\min\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right) < t \leq \max\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right)\right\}}
-\end{align*}
-Considering the sum over all elements of the window, we get that 
-\begin{align*} 
-\sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) = a_{1}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) - a_{2}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right),
-\end{align*}
-Applying Theorem $2$ in \cite{arcones} we get that 
-\begin{align*}
-m^{-1} \sum_{(x_1, x_2) \in \mathbb{G}_{m}} f_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(f_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}\right),
-\end{align*}
-with 
-\begin{align*}
-\sigma^{2} := \mathbb{E}\left(\big[f_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{0})\right)\big]^{2}\right) \\
-& \hspace{-4cm}+ 2 \sum_{x_{1}, x_{2} = 1}^{\infty} \mathbb{E}\left(\big[f_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{0})\right)\big]\big[f_{t}(\mathbb{X}_{x_1,x_2}) - \mathbb{E}\left(f_{t}(\mathbb{X}_{x_1, x_2})\right)\big]\right)
-\end{align*}
-\end{proof}
-\begin{remark}
-It is possible to generalize the result for $r$-thresholds by applying the same procedure.
-\end{remark}
-\paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.
-Let us consider the null hypothesis
-\begin{center}
-  $H_{0}$ \, :\; The field $X$ is isotropic,
-\end{center}
-and the following normality asymptotic result that is obtained by applying the delta method to Theorem (\textcolor{blue}{\ref{TCL}}).
-\begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
-Let  $t \in \mathbb{R}$, and $\check{\mathcal{P}}^{\scriptscriptstyle  (i) }(\cdot)$ be the scaled oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre} computed at level $t$.
-Then, it holds that,
-\begin{equation*}
-\frac{1}{m}\left(\cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)} - \cfrac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)\right)} \right)  \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t) \right),
-\end{equation*}
-with $\tilde{\sigma}^{2}(t) \in (0, \infty)$.
-% with $\tilde{\sigma}^{2}(t) = \frac{\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t)(\mu^{\star}_{2}(t))^{2} - 2\mu^{\star}_{2}(t)\mu^{\star}_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t) +\tilde{\sigma}_{\scriptscriptstyle 2,2}^{2}(t)\mu^{\star}_{1}(t))^{2}}{\mu^{\star}_{2}(t)^4}$
-Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }(t)}$. Then, under $H_{0}$, it holds that
-\begin{equation}\label{ratiounderH0}
-\frac{1}{m}\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
-\end{equation} 
-% $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu^{\star}_{2}(t)^2}$
-\end{Proposition}
-Consider the consistent empirical estimator $\hat{\sigma}(t):= \frac{1}{m^2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m}(t)\right)}$ is the empirical variance of the considered ratio.
-Then, from \ref{deltamethodgeneralprop}, it holds that
-$$ \frac{1}{m\sqrt{\hat{\sigma}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
-Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$.
-We define the symmetric accessible test $\hat{\phi}_{m}(t)$ with asymptotic level $\alpha$ as
-\begin{equation}
-\label{phihat}
-\hat{\phi}_{m}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left|R_{m}(t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
-\end{equation}
-\begin{remark}(Power of the statistical test at a level $t$) In Remark \ref{decreasingrho} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(t)\right)} \neq 1$.
-\end{remark}
-\section{Numerical studies}
-\subsection{Numerical studies of moments of the estimated perimeter}
-
-Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/3C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
-Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
-\begin{equation}
-A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
-\end{equation}
-with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{X}(x) = (1 -3||Ax||_{2}/3C + (||Ax||_{2}/2C)^{3})\mathbbm{1}_{||Ax||_{2} < C},$, note that $a\neq b$ if and only if $Y$ is anisotropic.
-We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$.
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
-}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
 \begin{figure}[H]
@@
 }
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{Testanisotropy2.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent $p_{\text{value}}$  of the test see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-\begin{displaymath}
-  \renewcommand{\arraystretch}{1.5}
-\begin{array}{|C{0.4cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|}
-\hline
-b & 0.1190 &  0.3571 &  0.5952 &  0.8333 &  1.0714 &  1.3095 &  1.5476 &  1.7857 &  2.0238 &  2.2619 &  2.5 \\ \hline
-1  & 0.9971 &  0.9879 &  0.9547 &  0.9956 &  0.9800 &  0.9973 &  0.9997 &  0.9897 &  0.9737 &  0.9858 &  0.9816  \\ \hline
-1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007 &  0.0052 &  0.0325 &  0.1036 \\ \hline
-1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0001 &  0.0035 \\ \hline 
-1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 \\ \hline
-2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0 \\ \hline
-\end{array}
-\end{displaymath}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.2]{TestaniRatiovsRHO.pdf}}
-    {\includegraphics[scale=0.2]{TestaniRatiovsTVA.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{imageU.pdf}}
-    \hspace{3cm}
-    {\includegraphics[scale=0.3]{levelset30000.pdf}}
-    \hspace{0.2cm}
- \caption{ Image of level $30000$}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.25]{ConfidenceIntervalRDStD.pdf}}
-    {\includegraphics[scale=0.25]{BoxplotRDStD.pdf}}
-    \hspace{0.2cm}
- \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.25]{ConfidenceIntervalRDAu.pdf}}
-    {\includegraphics[scale=0.25]{BoxplotRDAu.pdf}}
-    \hspace{0.2cm}
- \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
 \label{fig2}

### 2022-12-22 Draft_GFC.tex
Derniere version

@@
 \newtheorem{Definition}[Theorem]{Definition}
+\theoremstyle{definition}
 \newtheorem{remark}{Remark}
@@
 So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability
-
 \section{Mathematical framework}\label{section1}
@@
 Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares.
-We denote by
+We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and
 \begin{itemize}
-\item $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ the set of points in $S$
-\item $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$,
-\item for $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.$
-\end{itemize}
-The $C_{m}(x)$ will be referred to as \textit{cells}.
-To ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$ and $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$.
-Each $w \in \mathbb{E}^{(i)}_{m}$ is a segment of length $1$. 
-\begin{remark} The cardinality of the set $\mathbb{E}^{\scriptscriptstyle  (i)}_{m}$
-\label{cardEm}
+ \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ the set of points in $S$, to ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
+ \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S$, the $C_{m}(x)$ will be referred to as \textit{cells}.
+\item[$\bullet$] And finally, we denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, for each $x \in \mathbb{G}_{m}$,  $i \in \{1, 2\}$, the edge $w_{i}(x)$ is a segment of length $1$ and belongs to~$C_{m}(x) \cap C_{m}(x+e_{i})$.
+The cardinality of the sets of edges
 \begin{itemize}
 \item 
-$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_1)\subset (0,m)^{2} \right\} $\\ 
+$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{1}(x) \in C_{m}(x) \cap C_{m}(x+e_{1})\right\} $\\ 
  \hspace*{4.25cm}$ =  \left\{ 1, m - 1\right\}\times\left\{ 0, m-1 \right\},$
-\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_2)\subset (0,m)^{2} \right\} $\\ 
+\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{2}(x) \in C_{m}(x) \cap C_{m}(x+e_{2}) \right\} $\\
  \hspace*{4.25cm}$ = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},$
 \end{itemize}
-\end{remark}
-Figure \ref{fig1} shows an example of a square tiling with~$m = 4$.
+\end{itemize}
+Figure \ref{figure1} shows an example of a square tiling with~$m = 4$.
 \begin{figure}[h]
@@
 \caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
-\label{fig1}
-\end{figure}
-\vspace{-0.5cm}
-\paragraph{Discrete setting}
+\label{figure1}
+\end{figure}
+\vspace{-1cm}
+\paragraph{Discrete setting and binary image}
 Using the previous square tiling, we write $S =  \underset{x \in \mathbb{G}_{m}}{\cup}  C_{m}(x)$.
@@
 \end{figure}
-Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$.
+Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} \leq t$.
 \subsection{Perimeter of a binary image}\label{methods}
@@
 Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical.
-Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
 \begin{figure}[H]
@@
 \vspace{-0.25cm}
-\caption{The edge $w_{1} = (1,1)$ in red belongs to $C_{2}(0,0) \cap C_{2}(1, 0)$, with the cell $C_{2}(0,0)$ colored in black and $C_{2}(1, 0)$ in gray dashed stripes.}
+\caption{The edge $w_{1}(0,0)$ in red belongs to $C_{2}(0,0) \cap C_{2}(1, 0)$, with the cell $C_{2}(0,0)$ colored in black and $C_{2}(1, 0)$ in gray dashed stripes.}
 \label{fig1}
@@
 \end{equation}
-to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of $Z^{\scriptscriptstyle (m)}$.
-\begin{Definition}[Directional perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
-For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical and horizontal).
-Then, the directional perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
-\begin{equation}
-\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).
- \label{eq:6}
-\end{equation}
-Then, the perimeter of $Z^{\scriptscriptstyle (m)}$ is given by $\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t)$.
-\end{Definition}
-\section{Statistics of the oriented perimeter} 
-\subsection{First moment}
-Let us start this study by investigating the first moment of the oriented perimeter.
-\begin{Proposition}[First moment of the directional perimeter] 
-\label{propFisrtmoment}
-We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field.
-Let $i \in \{1,2\}$ and let us denote by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in [-1, 1]$.
-The expected value of the perimeter in \eqref{eq:6} is  given by $$\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)\right) = m(m-1)\mathbb{E}\left(f^{(i)}(t) \right)$$ where
-\begin{itemize}
-  \item if $\rho(e_{i}) \in ]-1,1]$, 
-    {\small
-  \begin{align}
-  \label{propEquationFisrtmoment}
-  \mathbb{E}\left(f^{(i)}(t) \right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)
-  \end{align}}
-with $N \sim \mathcal{N}(0,1)$. 
-\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(|t|\right)\right).$
-  \end{itemize}
-\end{Proposition}
-\begin{remark}
-Note that $\mathbb{E}\left(f^{(i)}(t) \right) = 0$ in the case where $\rho(e_i) = 1$ 
-\end{remark}
-\begin{proof}
-Let us assume that $\rho(e_{i}) \in ]-1,1]$.
-Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis and Remark \ref{cardEm} one can write that,
-\begin{equation*}
-\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right).
-\label{covarianeproof}
-\end{equation*}
- with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$.
-Before going any further, let us first make the following remark,
+to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of~$Z^{\scriptscriptstyle (m)}$.
+Before stating the definition of the oriented perimeter let us first make an observation that will appear very useful in the rest of the paper.
 \begin{remark}
@@
 \draw (8,0) node[below]{$\max(a,b)$};
-\draw (4,0) node[below]{$\frac{b+a}{2}$};
+\draw (4,0) node[below]{$\frac{a+b}{2}$};
 \draw (2.5,0) node[below]{$t$};
@@
 \node[text width= 1.6cm, font=\large] at (4,1) {$|b-a|$};
-\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{b+a}{2}|$};
+\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{a+b}{2}|$};
 \end{tikzpicture}
 \end{figure}
+\vspace{-1cm}
 \end{proof}
-We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}, \end{equation*}
-the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
+\begin{Definition}[Oriented perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
+For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$).
+Then, the oriented perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
+\begin{equation}
+\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x \in \mathbb{G}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).
+ \label{eq:6}
+\end{equation}
+Then, the perimeter of $Z^{\scriptscriptstyle (m)}$ is given by $\mathcal{P}_{m}(t) := \mathcal{P}_{m}^{\scriptscriptstyle (1)}(t) + \mathcal{P}_{m}^{\scriptscriptstyle (2)}(t)$.
+\end{Definition}
+\section{Statistics of the oriented perimeter} 
+\subsection{First moment}
+Let us start this study by investigating the first moment of the oriented perimeter.
+\begin{Proposition}[First moment of the oriented perimeter] 
+\label{propFisrtmoment}
+We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field.
+Let $i \in \{1,2\}$ and let us denote by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in [-1, 1]$.
+The expected value of the perimeter in \eqref{eq:6} is  given by $$\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)\right) = m(m-1)\mathbb{E}\left(f^{(i)}(t) \right)$$ where
+\begin{itemize}
+  \item if $\rho(e_{i}) \in ]-1,1]$, 
+    {\small
+  \begin{align}
+  \label{propEquationFisrtmoment}
+  \mathbb{E}\left(f^{(i)}(t) \right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)
+  \end{align}}
+with $N \sim \mathcal{N}(0,1)$ and $\Phi$ being the cumulative distribution function of the standard Gaussian. 
+\item if $\rho(e_i) = -1, \; \mathbb{E}\left(f^{(i)}(t) \right)= 2\left(1 - \Phi\left(|t|\right)\right).$
+  \end{itemize}
+\end{Proposition}
+\begin{proof}
+Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis one can write that, 
+\begin{equation*}
+\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right),
+\label{covarianeproof}
+\end{equation*}
+ with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$.
+We start by applying the following transformation to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$,  \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}.
+\end{equation*}
+The covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}
 -1 & 1 \\
@@
 \rho(e_i) & 1  \\ 
-\end{pmatrix}.$ \\
-Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent.
+\end{pmatrix}.$ Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent.
 Hence, we can write
@@
 \end{array}
-\right.$ \linebreak with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 
-{\small
-\begin{align*}
-\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\
+\right.$ with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 
+{\small
+\begin{align*}
+\mathbb{E}\left(f^{(i)}(t)\right) 
 & = \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right|\right\}}\right).
 \\
-& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq  \sqrt{2(1+\rho(e_i)}V -2t \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\
 & = \mathbb{E}\left(\mathbbm{1}_{\left\{\frac{2t - \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}  \leq V \leq \frac{2t + \sqrt{2(1-\rho(e_i))}|U|}{\sqrt{2(1+\rho(e_i))}}\right\}}\right), 
@@
 thus,
-$$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
+$$\mathbb{E}\left(f^{\scriptscriptstyle (i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$
 Let us now consider the case where $\rho(e_i) = -1$.
@@
 \begin{align*}
-\mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\
+\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\
 & = \mathbb{P}\left(|t| \leq |N|\right) = 2\left(1 - \Phi\left(|t|\right)\right).
@@
 \end{proof}
-Note that this result extends those given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 
-\begin{remark}
-\label{iidCase}
-In the independent case \textit{i.e.} $\text{Cov}\left(X_{0}, X_i\right) = 0$, we can write
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) & = m(m-1)\mathbb{E}\left(\Phi\left(\sqrt{2}t + |Z|\right) - \Phi\left(\sqrt{2}t - |Z|\right)\right) = 2m(m-1)\Phi(t)\left(1-\Phi(t)\right)
-\end{align*}}
-by applying the variable change {\small$\left\{\begin{array}{rcl}
-u & = & \frac{y - z}{\sqrt{2}} \\
-v & = & \frac{y+z}{\sqrt{2}} \\
-\end{array}\right.$}, we get the same result as in \cite{Psymetrie} (Proposition \textcolor{blue}{3.1}).
+This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 
+\begin{remark}(Degenerate dependence cases.)
+\begin{itemize}
+\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, note that $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
+\item In the independent case, \textit{i.e.} $\rho(e_{i}) = \text{Cov}\left(X_{0}, X_{e_i}\right) = 0$, we can write
+{\small
+\begin{align*}
+\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) & = m(m-1)\mathbb{E}\left(\Phi\left(\sqrt{2}t + |N|\right) - \Phi\left(\sqrt{2}t - |N|\right)\right) = 2m(m-1)\Phi(t)\left(1-\Phi(t)\right),
+\end{align*}}by applying the variable change $ (y, z) \mapsto (\frac{y-z}{\sqrt{2}}, \frac{y+z}{\sqrt{2}})$ to get the second identity.
+We get the same result as in \cite{Psymetrie} (Proposition \textcolor{blue}{3.1}).
+\\ As in \cite{Psymetrie} in order to converge towards a non degenerate quantity when $m$ goes to infinity, we have to consider a normalized perimeter thus, dividing the perimeter by the area of the window $S$, considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.
+\end{itemize}
 \end{remark}
-\begin{remark}
-To have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window $S$, ($m^2$), thus considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.
-\end{remark}
+\paragraph{Total variation.}
 \textcolor{red}{
-It is possible to link the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ to its perimeter, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.}
+In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object.
+It is possible to link this quantity the perimeter of $u$, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.
+In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.}
 \begin{Proposition}
+\label{Variationtotal}
 Under the assumptions stated in Proposition \ref{propFisrtmoment}, we get 
@@
 \end{remark}
-\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance~$\rho$.}
-\begin{remark}
+\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$.
+This result allows us to state that the oriented perimeter is a strictly decreasing function with respect to $\rho$.
+}
+\begin{Proposition}
 \label{powertest}
-\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure, we  have the following result regarding their associated expected oriented perimeter at level $t$:}
+\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure.
+For any level $t$, we  have the following result:}
 \begin{equation*}
@@
 \end{equation*}
-\end{remark}
+\end{Proposition}
 \begin{proof}
-Let $t \in \mathbb{R}$ we can prove this result by considering  the function \begin{align*} 
+Let $t \in \mathbb{R}$, We consider the function $h$ defined as follow \begin{align*} 
 h: (-1,1) &\longrightarrow \mathbb{R}, \\
@@
 \end{align*}
-with $N \sim \mathcal{N}\left(0,1\right)$, its derivative is equal to 
+with $N \sim \mathcal{N}\left(0,1\right)$. The derivative of $h$ is equal to 
 \begin{align*}
@@
 & = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
-&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
-&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
-& = \frac{\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
-& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
-& = \frac{-2\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
-& = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}},
-\end{align*}
-for all $|x| < 1, \; h'(x) < 0$ thus, $h$ is a strictly decreasing function. 
+&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
+&\hspace{5cm}\left. - \left(2y - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
+& = \frac{-\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
+& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
+& = \frac{-\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
+& = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
+\end{align*}
+Since for all $|x| < 1, \; h'(x) < 0$, $h$ is a strictly decreasing function. 
 \end{proof}
-\textcolor{red}{Thus, the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, in particular if $\rho(e_1) \neq \rho(e_2) $\linebreak then~$\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$.\\
-Now, if the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$.
-Thus, having a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$  would allow us to construct an isotropy test using the oriented perimeter of the field $X$.}
+\begin{remark}
+\label{remarkesperancetest}
+\textcolor{red}{The function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ being strictly decreasing, if $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$ then~$\rho(e_1) \neq \rho(e_2) $.
+Now, assume that the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$.
+Then, the ratio $\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)$ would be distributed around $1$ in the case of isotropy.
+This consideration will be crucial for the proposed local isotropy testing procedure in the next section.}
+\end{remark}
 \subsection{Isotropy test using the oriented perimeter}
-In order to establish the CLT, we need to add some assumptions on $\rho$ the covariance structure of the field $X$.
+\label{isotest}
+In order to construct a local isotropy test using the oriented perimeter of the field $X$, we first  establish a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$.
+To do that, we have to add some assumptions on $\rho$ the covariance structure of the field $X$.
 \begin{enumerate}
@@
 \begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
-We consider that $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
+We consider that $(X_{x})_{x\in \mathbb{G}_{m}}$ is a centered stationary standard Gaussian field.
+Let $r$ be a positive integer and $t_{1}, \cdots,t_{r} \in \mathbb{R}$.
+Then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
 \begin{equation*}
@@
 where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by
-\begin{align*}
+\begin{align}
+\label{CovTCL}
 \Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
-\end{align*}
+\end{align}
 \end{Theorem}
-\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalized case is made by following the same procedure.
-Using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have
-\begin{align*}
-\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right)
-\end{align*}
-with $\sigma^{2}(t) = \lim_{m \to \infty} \mathbb{V}\left( \frac{a_{1}}{m}\mathcal{P}^{\scriptscriptstyle (1)}(t) + \frac{a_{2}}{m}\mathcal{P}^{\scriptscriptstyle (2)}(t) \right)$.
-We first need to recall some notations that were introduced in the first section \eqref{fi}.
-We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ and let~$a_{1}, a_{2}, t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$.
-We recall as introduced in \eqref{fi}
-\begin{align*}
-f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}
-\end{align*}
-Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 
-\begin{align*}
-g_{t}\left(\mathbb{X}_{x_1, x_2}\right) & := a_{1}\mathbbm{1}_{\left\{\min\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right) < t \leq \max\left(X_{x_1, x_2}, X_{\scriptscriptstyle x_1 +  1, \scriptscriptstyle x_2}\right)\right\}} \\
-& \hspace{1cm} + a_{2}\mathbbm{1}_{\left\{\min\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right) < t \leq \max\left(X_{x_2, x_1}, X_{\scriptscriptstyle x_2, x_1 + 1}\right)\right\}}
-\end{align*}
-Note that $0 \leq f_{t}^{\scriptscriptstyle (i)}(0) \leq 1$ \textit{a.s.}, thus, \textit{a.s.},$\mathbb{E}\left(g_{t}\left(\mathbb{X}_{\scriptscriptstyle  0, 0}\right)^{2}\right) < (a_{1} + a_{2})^{2}$.
-In order to apply Theorem $2$ in \cite{arcones} and get the convergence, \\
-\big[\textcolor{blue}{ $r^{(p,q )}(k) = \mathbb{E}\left(X^{p}_{m} X^{q}_{m+k}\right)$for $k\in Z$ and $1 < p, q < d$, where $m$ is any integer so large that $m, m + k > 1$. Suppose that \\
-$\lim_{n \to \infty} n^{-1} \sum_{j,k = 1}^{n}r^{(p,q )}(j-k) < \infty$ and $\lim_{m \to \infty} n^{-1}\sum_{j,k = 1}^{n}(r^{(p,q )}(j-k))^{2} < \infty$}\big]\\
-we should insure that 
-\begin{align*}
-\lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right) < \infty \; \text{and} \; \lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}_{m}}\sum_{y \in \mathbb{G}_{m}} \left(\mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right)\right)^{2} < \infty,
-\end{align*} 
-with $\mathbb{X}^{(p)}_{x}$ being the $p$-coordinate of the $4$-dimensional vector $\mathbb{X}_{x}$, then applying the stationarity hypothesis it amounts to the following
-\begin{align*}
-\lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-y) < \infty \;  \text{and} \; \lim_{m \to \infty} m^{-2}\sum_{x, y \in \mathbb{G}_{m}}\rho(x-~y)^{2} < \infty.
-\end{align*} 
-Under $(A1)$ and $(A2)$, we can apply Theorem $2$ in \cite{arcones} we get that 
-\begin{align*}
-m^{-1} \sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{\scriptscriptstyle t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right),
-\end{align*}
-with 
-\begin{align*}
-\sigma^{2}(t) := \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]^{2}\right) \\
-& \hspace{-4cm}+ 2 \sum_{x_{1}, x_{2} = 1}^{\infty} \mathbb{E}\left(\big[g_{t}(\mathbb{X}_{0}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{0})\right)\big]\big[g_{t}(\mathbb{X}_{x_1,x_2}) - \mathbb{E}\left(g_{t}(\mathbb{X}_{x_1, x_2})\right)\big]\right)
-\end{align*}
-Re-writing the sum we get
-\begin{align*} 
-\sum_{(x_1, x_2) \in \mathbb{G}_{m}} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1} g_{t}\left(\mathbb{X}_{x_1, x_2}\right) - \mathbb{E}\left(g_{t}\left(\mathbb{X}_{x_1, x_2}\right)\right) \\
-&=  a_{1}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) - a_{2}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right),
-\end{align*}
-Thus
-\begin{align*}
-\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right)
-\end{align*}
+\begin{proof} For the sake of simplicity, we will prove the theorem for $r=1$, the generalized case can be established by following the same procedure.
+Using the Cramèr-Wold method, we will prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have
+\begin{align*}
+\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right)
+\end{align*}
+with $\sigma^{2}(t) < \infty$. Let~$ t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$, we recall the notation introduced in \eqref{fi}
+\begin{align*}
+f_{t}^{\scriptscriptstyle (i)}(x) := \mathbbm{1}_{\left\{\min\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right) < t \leq \max\left(X_{x+e_{i}}, X_{\scriptscriptstyle x}\right)\right\}}.
+\end{align*}
+Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 
+\begin{align*}
+g_{t}\left(u,v, w, z\right) & := a_{1}\mathbbm{1}_{\left\{\min\left(u, v\right) < t \leq \max\left(u, v\right)\right\}} + a_{2}\mathbbm{1}_{\left\{\min\left(w, z\right) < t \leq \max\left(w, z\right)\right\}},
+\end{align*}
+so that, re-writing the sum we get
+\begin{align*} 
+\sum_{x \in \mathbb{G}^{(1)}_{m}} g_{t}\left(\mathbb{X}_{x}\right)  & = \sum_{x_1 = 0}^{m-2}\sum_{x_2 = 0}^{m-1} g_{t}\left(\mathbb{X}_{x_{1}, x_{2}}\right)  \\
+&=  a_{1}\mathcal{P}^{\scriptscriptstyle (1)}(t) + a_{2}\mathcal{P}^{\scriptscriptstyle (2)}(t).
+\end{align*}
+Note that $\left|g(t)\right| \leq \left|a_{1}\right| + \left|a_{2}\right|$, thus, $\mathbb{E}\left(g_{t}\left(\mathbb{X}_{\scriptscriptstyle  0, 0}\right)^{2}\right) < (|a_{1}| + |a_{2}|)^{2}$.
+In order to apply Theorem~$2$ in \cite{arcones} and get the convergence, we should insure that for all $1 \leq p,q \leq 4$,
+\begin{align*}
+\lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}^{\scriptscriptstyle (1)}_{m}}\sum_{y \in \mathbb{G}^{\scriptscriptstyle (1)}_{m}} \mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right) \; \text{and} \; \lim_{m \to \infty} m^{-2} \sum_{x \in \mathbb{G}^{\scriptscriptstyle (1)}_{m}}\sum_{y \in \mathbb{G}^{\scriptscriptstyle (1)}_{m}} \left(\mathbb{E}\left(\mathbb{X}^{(p)}_{x}\mathbb{X}^{(q)}_{y}\right)\right)^{2} exist,
+\end{align*} 
+with $\mathbb{X}^{(i)}_{x}$ being the $i$-coordinate of the $4$-dimensional vector $\mathbb{X}_{x}$. Applying the stationarity hypothesis it amounts to the following, for all $1 \leq i,j \leq 2$,
+\begin{align*}
+\lim_{m \to \infty} m^{-2}\sum_{x \in \mathbb{G}^{\scriptscriptstyle (i)}_{m}, y \in \mathbb{G}^{\scriptscriptstyle (j)}_{m} }\rho(x-y)  \;  \text{and} \; \lim_{m \to \infty} m^{-2}\sum_{x \in \mathbb{G}^{\scriptscriptstyle (i)}_{m}, y \in \mathbb{G}^{\scriptscriptstyle (j)}_{m} }\rho(x-~y)^{2} exist.
+\end{align*} 
+Then under $(A1)$ and $(A2)$, we can apply Theorem $2$ in \cite{arcones}, we get that 
+\begin{align*}
+m^{-1} \sum_{x \in \mathbb{G}^{\scriptscriptstyle (1)}_{m}} g_{\scriptscriptstyle t}\left(\mathbb{X}_{x}\right) - \mathbb{E}\left(g_{\scriptscriptstyle t}\left(\mathbb{X}_{x}\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right),
+\end{align*}
+which proves the theorem.
 \end{proof}
-\paragraph{A test statistic} Following the idea  in \cite{bierme2019}  we propose a method to test the isotropy of the field $X$.
+\textcolor{red}{We are now in position to construct the promised isotropy test.}
+\subsection{Perimeter based local isotropy test}
+As previously discussed in Remark \ref{remarkesperancetest}, we now aim to build a test using the specific structure of the mean perimeter in the case of local isotropy.
+Following the idea  in \cite{bierme2019}  we propose a method to test the local isotropy of the field $X$.
 Let us consider the null hypothesis
 \begin{center}
-  $H_{0}$ \, :\; The field $X$ is isotropic,
+  $H_{0}$ \, :\; $\rho(e_1) = \rho(e_2)$.
 \end{center}
-and the following normality asymptotic result that is obtained by applying the delta method to Theorem (\textcolor{blue}{\ref{TCL}}).
+Under $H_{0}$, let us remark that $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t) \right)= \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)\right)$ and $\mathbb{V}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t) \right)= \mathbb{V}\left(\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)\right)$ for all~$t$.
+Making use of Theorem \ref{TCL}, we have the following normality asymptotic result.
 \begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
-Let  $t \in \mathbb{R}$, and $\mathcal{P}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre} computed at level $t$ let us denote by $\mu_{i}(t)) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right)$.
-Then, it holds that,
+Let  $t \in \mathbb{R}$, and $\mathcal{P}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre}. Then, it holds that,
 \begin{equation*}
@@
 \end{equation*}
-with $\tilde{\sigma}^{2}(t) = \frac{(\tilde{\sigma}_{\scriptscriptstyle 1,1}(t)\mu_{2}(t))^{2} - 2\mu_{2}(t)\mu_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}(t)^{2} +(\tilde{\sigma}_{\scriptscriptstyle 2,2}(t)\mu_{1}(t))^{2}}{\mu_{2}(t)^4} \in (0, \infty)$.
-\\
-Let $t \in \mathbb{R}$  and  $R_{m}(t) := \cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)}$. Then, under $H_{0}$, it holds that
+with $\tilde{\sigma}^{2}(t) = \frac{(\tilde{\sigma}_{\scriptscriptstyle 1,1}(t)\mu_{2}(t))^{2} - 2\mu_{2}(t)\mu_{1}(t)\tilde{\sigma}_{\scriptscriptstyle 1,2}(t)^{2} +(\tilde{\sigma}_{\scriptscriptstyle 2,2}(t)\mu_{1}(t))^{2}}{\mu_{2}(t)^4}$, $\mu_{i}(t) = \mathbb{E}(f^{(i)}(t))$ as in \eqref{propEquationFisrtmoment} \linebreak and $\tilde{\sigma}_{\scriptscriptstyle 1,1}(t) = \Sigma^{\textcolor{white}{ }^{\star}}_{2}(1,i,1,j)$ as in \eqref{CovTCL}.
+\\
+Furthermore, under $H_{0}$, it holds that
 \begin{equation}\label{ratiounderH0}
-\frac{1}{m}\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}^{2}(t)  \right),
+\frac{1}{m}\left(\cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)} - 1 \right)  \xrightarrow[m \to \infty]{d, H_0} \mathcal{N}\left(0,  \tilde{\sigma}_{\scriptscriptstyle H_{0}}^{2}(t)  \right),
 \end{equation} 
-and $\tilde{\sigma}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu_{2}(t)^2}$.
+with $\tilde{\sigma}_{\scriptscriptstyle H_{0}}^{2}(t) = \frac{2\left(\tilde{\sigma}_{\scriptscriptstyle 1,1}^{2}(t) \, - \, \tilde{\sigma}_{\scriptscriptstyle 1,2}^{2}(t)\right)}{\mu_{2}(t)^2}$.
 \end{Proposition}
-Consider the consistent empirical estimator $\hat{\sigma}_{m,n}(t):= \frac{1}{m^2}\hat{\mathbb{V}\left(R_{m}(t)\right)}$ of $\tilde{\sigma}^{2}(t)$, where $\hat{\mathbb{V}\left(R_{m, n}(t)\right)}$ is the empirical variance of the considered ratio computed with Montecarlo $= n$.
-Then, from \ref{deltamethodgeneralprop}, it holds that
-$$ \frac{1}{m\sqrt{\hat{\sigma}_{m,n}(t)}}\left(R_{m}(t) - 1 \right) = \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m}(t)\right)}}}\left(R_{m}(t) - 1 \right)   \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
+\paragraph{Proposed test with asymptotic level $\alpha$.} Let $t \in \mathbb{R}$,  we denote the ratio by $R_{m}(t) =~\cfrac{\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t)}{\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)}$.
+Consider a consistent empirical estimator $\hat{\sigma}^{2}_{m}(t)$ of $\tilde{\sigma}^{2}(t)$. Then, from \ref{deltamethodgeneralprop}, it holds that 
+$$ \frac{1}{m\sqrt{\hat{\sigma}^{2}_{m}(t)}}\left(R_{m}(t) - 1 \right)  \xrightarrow[m \to \infty]{d, H_{0}} \mathcal{N}\left(0, 1 \right).$$
 Take a confidence level $\alpha \in (0,1)$ and set $q_{1-\frac{\alpha}{2}}$ such that $\mathbb{P}\left(|\mathcal{N}\left(0,1\right)| \leq  q_{1-\frac{\alpha}{2}} \right) = 1 - \frac{\alpha}{2}$.
-We define the symmetric accessible test $\hat{\phi}_{m, n}(t)$ with asymptotic level $\alpha$ as
+We define the symmetric accessible test $\hat{\phi}_{m}(t)$ with asymptotic level $\alpha$ as
 \begin{equation}
 \label{phihat}
-\hat{\phi}_{m,n}(t)= \mathbbm{1}_{\left\{ \frac{1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}\left|R_{m}((t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
+\hat{\phi}_{m}(t)= \mathbbm{1}_{\left\{ \frac{1}{m\sqrt{\hat{\sigma}^{2}_{m}(t)}}\left|R_{m}((t) - 1 \right| \geq q_{1- \frac{\alpha}{2}} \right\}}
 \end{equation}
-\begin{remark}(Power of the statistical test at a level $t$) In Remark \ref{powertest} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ thus $\frac{\mathbb{E}\left(\mathcal{P}^{1}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{2}(t)\right)} \neq 1$.
+Let us now study the consistency of the proposed test statistic, let $H_{1}$ be the alternative hypothesis
+\begin{center}
+$H_{1}$\, :\; $\rho(e_1) \neq \rho(e_2)$
+\end{center} 
+\begin{remark}(Consistency of the proposed isotropy test) In Remark \ref{powertest} we showed that the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, thus, if $\rho(e_1) \neq \rho(e_2)$ then $\frac{\mathbb{E}\left(\mathcal{P}^{1}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}_{m}^{2}(t)\right)} \neq 1$, which implies that $\mathbb{P}_{H_{1}}\left(\hat{\phi}_{m}(t) = 1\right) \to 1$ for $m\to \infty$.
 \end{remark}
@@
 \subsection{Numerical studies of moments of the estimated perimeter}
-Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/3C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
+Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/2C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
 Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
@@
 \subsection{Theroretical and numerical study of the covariance of the perimeter}
-Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$.
+Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$.
 \begin{Lemma} 
@@
 \\
-\begin{Lemma}
+\begin{Lemma}(Computation of the two cells contribution)
 \begin{align*}
@@
 \end{Lemma}
-\begin{Proposition}
-\label{PropositionFourCell}
-Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance of covariance sturcture given by $\rho$, such that $|\rho(e_i)| < 1$
-\vspace{-0.5cm} 
- {\small 
-\begin{align}
-\label{Thisthofour}
-\mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right.
-\nonumber\\
-& \hspace{-6cm} \left.
-\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
-\right.
-\nonumber \\
-& \hspace{-4cm}\left.
-\left.
-- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
-\end{align}
-}with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$, and \\ 
+Let $x \in \mathbb{Z}^{2}$ such that the covariance matrix $\Sigma_{i}(x)$ of the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ is invertible, 
+$$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
+\rho(e_1) & 1 & \rho(x-e_1) &  \rho(x+e_i- e_1) \\ 
+\rho(x) & \rho(x-e_1) & 1 & \rho(e_i) \\
+\rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$
+Let us define the following quantities   \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
+\begin{center}
+$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$.
+\end{center}
+\begin{Proposition}\label{PropositionFourCell}(Computation of the four cell contribution).
+Let $x \in \mathbb{Z}^{2}$ such that the covariance matrix $\Sigma_{i}(x)$ of the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ is invertible, we introduce the following quantities that are non zeros, \\
 $\left\{
@@
  \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right) \\
-   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
-   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ \\
+   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \hspace{-3cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = & \hspace{-3cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)}, \end{array}\right.$ \\
     $\left\{
  \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
-    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
-     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
-   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}
-\end{array}\right.$
-
+   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = & \hspace{-5cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
+    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \hspace{-5cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
+     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \hspace{-1.5cm} \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
+   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}.
+\end{array}\right.$ \\
+then,
+{\small
+ \begin{align}
+\label{covconf}
+\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (i)}(x)\right) & = 
+\mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right. \nonumber\\
+& \hspace{1cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
+\right.
+\nonumber \\
+& \hspace{1cm} \left.
+\left.
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right) \nonumber \\
+& \hspace{4cm}  - \mathbb{E}\left(f_{t}^{\scriptscriptstyle (1)}(0)\right)\mathbb{E}\left(f_{s}^{ \scriptscriptstyle (i)}(x)\right).
+\end{align}}
+% {\small 
+% \begin{align}
+% \label{Thisthofour}
+% \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle i}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right) & = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - \sigma^{\scriptscriptstyle (+)}_{1}V| \leq |\sigma^{\scriptscriptstyle (-)}_{1}U|\right\}}\right.
+\nonumber\\
+% & \hspace{-6cm} \left.
+\left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x) }{\sigma^{\scriptscriptstyle (-)}_{1}} U - \frac{2S\rho(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) -  \pi^{\scriptscriptstyle(-, i)}_{W}(x)\right) W \right) \right.
+\right.
+\nonumber \\
+% & \hspace{-4cm}\left.
+\left.
+- \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \frac{2\Delta \rho(x+e_i) }{\sigma^{\scriptscriptstyle (-)}_{1}}U - \frac{2S \rho(x+e_i) }{\sigma^{\scriptscriptstyle (+)}_{1}}V - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)
+% \end{align}
+% }
+with $\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}$ the cumulative distribution function of $Z \sim \mathcal{N}(0, (\pi^{\scriptscriptstyle(+, i)}_{Z}(x))^{2})$, 
 \end{Proposition}
@@
 & \hspace{-2.7cm} \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber\\
-& \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
+& \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
 \end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
@@
 & \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
-\end{align*}} We know that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
+\end{align*}} We know that $|\rho(e_1)| < 1$, and that $\tilde{\Sigma}_{i}(x)$ is invertible, thus, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
 We get the following decomposition \\
@@
   \end{array}\right.$
-  \hspace{-0.9cm} and 
+  \hspace{-0.9cm}\\
   $\left\{
@@
   \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z,
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, \text{with}
 \end{array}\right.$ \\
-with 
 $\left\{
@@
 \begin{Lemma}
-Let $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$, there exist a constant $C \in \mathbb{R}^{+}$, such that for all $x \in \mathbb{G}_{m}$, we get
+\label{lemmarx}
+Let $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$, there exists a constant $C \in \mathbb{R}^{+}$, such that for all $x \in \mathbb{G}_{m}$, we get
 \begin{align*}
@@
 \begin{proof}
-Let us begin by reconsidering the previous quantities, 
+Let us begin by reconsidering the previous quantities. 
 \begin{itemize}
-  \item if $r(x) = 0$, then, $\pi^{\scriptscriptstyle(-, i)}_{U}(x) = \pi^{\scriptscriptstyle(+, i)}_{U}(x) = \pi^{\scriptscriptstyle(-, i)}_{V}(x) = \pi^{\scriptscriptstyle(+, i)}_{V}(x) = 0$, $\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sigma^{(-)}_{i}$ and~$\pi^{\scriptscriptstyle(+, i)}_{W}(x) = \sigma^{(+)}_{i}$.
-  \item else, reconsidering the expressions above recalling that \linebreak and $r(x) = \max\left(|\rho(x)|, |\rho(x + e_i)|, |\rho(x-e_1)|, |\rho(x +e_i - e_1)| \right)$ we get 
+  \item If $r(x) = 0$, then, $\pi^{\scriptscriptstyle(-, i)}_{U}(x) = \pi^{\scriptscriptstyle(+, i)}_{U}(x) = \pi^{\scriptscriptstyle(-, i)}_{V}(x) = \pi^{\scriptscriptstyle(+, i)}_{V}(x) = 0$, $\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sigma^{(-)}_{i}$ and~$\pi^{\scriptscriptstyle(+, i)}_{W}(x) = \sigma^{(+)}_{i}$ and hence, $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right) = 0$.
+  \item Else, recalling the expressions introduced in Proposition \ref{PropositionFourCell} we first get 
   \begin{align}
   \label{nine}
-   \left|\pi^{\scriptscriptstyle(\pm, i)}_{U}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}, \hspace{0.5cm} \left|\pi^{\scriptscriptstyle(-, i)}_{V}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}},
+   \left|\pi^{\scriptscriptstyle(\pm, i)}_{U}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (-)}_{1}}, \hspace{0.5cm} \left|\pi^{\scriptscriptstyle(-, i)}_{V}(x)\right| \leq \frac{4r(x)}{\sigma^{\scriptscriptstyle (+)}_{1}}.
    \end{align}
-   substracting $\sigma^{(-)}_{i}$ and applying inequality \eqref{nine} we get, 
+   Then, substracting $\sigma^{(-)}_{i}$ and applying inequality \eqref{nine} we get, 
    \begin{align}
@@
    \left|\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \sigma^{(-)}_{i}\right| & \leq \sigma^{(-)}_{i}\left| \left(1 - \frac{\pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2}}{\left(\sigma^{(-)}_{i}\right)^{2}} - \frac{\pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}}{\left(\sigma^{(-)}_{i}\right)^{2}}\right)^{\scriptscriptstyle (1/2)} - 1  \right| \nonumber \\
-   & \leq \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)
+   & \leq \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right).
    \end{align}
-   from \eqref{nine} and \eqref{ten}, we also get
+   From \eqref{nine} and \eqref{ten}, we also get
    \begin{align}
@@
   \left|\pi^{\scriptscriptstyle(+, i)}_{W}(x)\right| & = \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \nonumber \\
-  &\leq 16r(x)^{2}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\left(\sigma^{(-)}_{i} -  \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\right)^{-1}
+  &\leq 16r(x)^{2}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\left(\sigma^{(-)}_{i} -  \frac{16r^{2}(x)}{\sigma^{(-)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} \right)\right)^{-1}.
   \end{align}
- finally, from \eqref{nine} and \eqref{eleven}
+ Finally, from \eqref{nine} and \eqref{eleven}
   \begin{align}
-  \left|\pi^{\scriptscriptstyle(+, i)}_{Z}(x) - \sigma^{(+)}_{i}\right| \leq \frac{16r^{2}(x)}{\sigma^{(+)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} +  \frac{\pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}{16r^{2}(x)} \right)
+  \left|\pi^{\scriptscriptstyle(+, i)}_{Z}(x) - \sigma^{(+)}_{i}\right| \leq \frac{16r^{2}(x)}{\sigma^{(+)}_{i}}\left(\frac{1}{(\sigma^{(-)}_{i})^{2}} + \frac{1}{(\sigma^{(+)}_{i})^{2}} +  \frac{\pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}}{16r^{2}(x)} \right).
   \end{align}
@@
 & \hspace{-5cm} \left.
-+ \frac{\sigma^{(+)}_{i}\left(\left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \pi^{\scriptscriptstyle(+, i)}_{W}(x) W \right)}{\sigma^{(+)}_{i}\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\right| \\
-& \hspace{-10cm} \text{making use of the previous inequalities, there exist a constant $C_{1} \in \mathbb{R}^{+}$ depending}\\
++ \frac{\sigma^{(+)}_{i}\left(\left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V - \pi^{\scriptscriptstyle(+, i)}_{W}(x) W \right)}{\sigma^{(+)}_{i}\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\right|, \\
+& \hspace{-10cm} \text{making use of the previous inequalities, there exists a constant $C_{1} \in \mathbb{R}^{+}$ depending}\\
 & \hspace{-10cm}  \text{on $s, \sigma^{(+)}_{i}, \sigma^{(-)}_{i}$ such that,} \\
-& \hspace{-8.8cm}\leq C_{1}r(x)\left(|U| + |V| + |W|\right)
-\end{align*}}
-Also, there exist $C_2$ such that $R_{2}(x) \leq C_{2}r(x)\left(|U| + |V| + |W|\right)$. 
-Reconsidering Equation~(\ref{Thisthofour}) we get,
+  & \hspace{-9.5cm} |R_{1}(x)|  \leq C_{1}r(x)\left(|U| + |V| + |W|\right).
+\end{align*}}Also, there exists $C_2$ such that $R_{2}(x) \leq C_{2}r(x)\left(|U| + |V| + |W|\right)$. 
+Reconsidering Equation~(\ref{covconf}) we get,
 {\small
@@
  \end{align*}}
-Applying the mean value theorem, there exist a constant $C \in \mathbb{R}^{+}$ such that 
+Applying the mean value theorem, there exists a constant $C \in \mathbb{R}^{+}$ such that 
 \begin{align*}
  |\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)| & \leq C\mathbb{E}\left(|R_{1}(x)| + |R_{2}(x)|\right). \\
-& \leq Cr(x)
-\end{align*}
-We will prove the result for $i =1$, the other cases can be proven using the same arguments, let $x \in \mathbb{Z}^{2}$, considering the serie $\sum_{x \in \mathbb{Z}^{2}}\left(\mathbbm{1}_{|x_{1}| \leq m-2]}\mathbbm{1}_{|x_{2}| \leq m-1} \frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right) \right)$,
-the limit of the general term as $m$ goes to infinity is
-\begin{align*}
-\lim_{m \to \infty}\cfrac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)\mathbbm{1}_{|x_{1}| \leq m-2]}\mathbbm{1}_{|x_{2}| \leq m-1}  \\
-& \hspace{-7cm} =\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right)
-\end{align*}
-Besides, we just proved that for $m \in \mathbb{N}$, for all $x\in \mathbb{Z}^{2}$, $\left|\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x)\right)\right| \leq Cr(x)$, thus applying the dominated convergence theorem, $\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right)$ exists.
+& \leq Cr(x), 
+\end{align*}
+and the first assertion in Lemma \ref{lemmarx} is established.\\
+For the second assertion, we will only prove the result for $i =1$, the other cases can be proven using the same arguments. \\
+Considering the serie $\sum_{x \in \mathbb{Z}^{2}}\left(\mathbbm{1}_{|x_{1}| \leq m-2]}\mathbbm{1}_{|x_{2}| \leq m-1} \frac{(m-|x_2|)(m-|x_1| -1)}{m^2} \text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right) \right)$,
+the limit of the general term as $m$ goes to infinity is $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(1)}(x) \right)$.
+Besides, we just proved that for $m \in \mathbb{N}$, for all $x\in \mathbb{Z}^{2}$, $\left|\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x)\right)\right| \leq Cr(x)$, thus applying the dominated convergence theorem, if $\sum_{x \in \mathbb{Z}^{2}} r(x) < \infty$ then, $\lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t), \frac{1}{m}\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right)$ exists.
 \end{proof}
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{ThreeConfNew.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1,-1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
-}
-\label{fig2}
-\end{figure}
 
@@
 }
-
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{ThreeConfNew.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1,-1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
+}
+\label{fig2}
+\end{figure}
 Regarding the three cells configuration, one would have to reconsider the expression from the beginning and integrate the third variable $W$ that has a non vanishing variance in the independent regime \textit{i.e.} $\rho(e_1) = \rho(2e_1)=0$.

### 2023-01-17 Draft_GFC.tex
New_upload

@@
 \usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
+\usepackage{url} 
 \usepackage{tabularx}
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
+
 \newcommand{\blind}{0}
 
-% DON'T change margins - should be 1 inch all around.
 \addtolength{\oddsidemargin}{-.5in}%
@@
     \addtocounter{Ax}{1}
-    \item[A\theAx.]}
+    \item[\textbf{A}\theAx.]}
 \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
@@
 \section{Introduction}
+
+The main objective of our study is to be able to decide whether the texture of a grey-level image is isotropic or not.
+By the texture of an image, we mean the microscopic structure that is captured by the covariance function at the pixels scale.
+In order to achieve this goal, we propose a methodology built on a statistical test for which all components are rigourously validated.
+The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the pixels values.
+Let us first start with an exemple of medical images where our methodology is applied.
+
+\begin{figure}[H]
+\centering
+{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
+ \caption{Stationnarized image of a bone x-ray, with it's associted excursion sets thresholded at the first, second and third quartile.}
+\label{fig22}
+\end{figure}
+
+Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We consider the thresholded image at level $t_{\alpha}$, $\{X > t_{\alpha}\}$, and then 
+%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, 
+count the respective numbers of horizontal and vertical edges that are involved in the perimeter of the black region of the binary image.
+In case of an isotropic texture, the ratio of these two counters should be close to one.
+At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.
+
+The ratio has been computed for each image of the panel at various quantile levels. In Figure \ref{fig2}, the distribution of the obtained ratios is summerized in a boxplot for each level.
+
+\begin{figure}[H]
+  \centering  
+   {\includegraphics[scale=0.28]{BoxplotRDAu.pdf}}
+    \hspace{0.2cm}
+ \caption{For $\alpha \in [0.15, 0.9]$, we represent on the left, the confidence interval of the mean of the ratio between the two oriented perimeters computed for $t_{\alpha}, \mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$ and its corresponding boxplot for real thresholded images of bone X-rays.}
+\label{fig2}
+\end{figure}
+
+We observe that the boxplots of the ratio between the horizontal and vertical counters are not distributed around one, whatever the observed level. 
+Moreover, for almost all images the observed ratios are above one whereas for some images extreme values are observed below one.
+We checked the fact that these extreme cases below one all belong to the same small group of images.
+Apparently, these images were subject to a $\pi/2$-angle rotation.
+Nevertheless, what is relevant on this sample of X-ray images of calcaneus is that the anisotropy of the texture can be revealed at any threshold level by simply comparing two single counters.
+It is worth to note that this anisotropy, although obvious through the proposed image analysis procedure, is not perceptible to the naked eye.
+
+With a very different approach based on quadratic variations, the same sample of images has been analyzed in \cite{Richard??} and the same conclusion has been obtained: the calcaneus X-ray images are anisotropic.
+A by-product of our method is the measurement of the anisotropy through the ratio between the oriented perimeters.
+It will be used to produce a test of isotropy.
+
+\bigskip
+
+The present paper is part of the methodological literature that deals with statistical inference based on geometrical observable features.
+Although it is an old engineers question (see \cite{Longuet-Higgins} for instance), it has recently received much attention from a statistical point of view.
+To cite some of these papers, let us quote \cite{Worsley96} where the localization of peaks are infered from the observation of the Euler chracteristic in neuroimaging, \cite{Molina} where isotropy is tested through the observation of the gradient, \cite{DEL17} or \cite{bierme2019} where a test of Gaussianity is produced based on the Euler characteristic of excursion sets, \cite{Psymetrie} where a test of symmetry is produced based on the perimeter of thresholded images,  ({\sc \`a verifier et completer avec d'autres non li\'es \`a notre "famille".
+Pour chacun, what is infered?
+and what is observed?
+mettre dans ordre chronologique.})\\
+In particular, let us focus on two specific articles \cite{cabana1987affine, Berzin} with a similar objective as our, namely a test of isotropy, and based on similar observations, namely the length of level sets.
+{\sc Expliquer la methode de ces papiers et les differences avec le present papier}.
+Implementations of this type of method can be found in cosmology, neuroimaging and medical imaging in general, hydrology, etc.
+
+\bigskip
+
+%\paragraph{Outline of our method.}
+Let us now present in details what is the content of our study.
+As already said, we aim at constructing a statistical test of isotropy based on the observation at small scale of the image.
+Our observation will be very sparse since it is reduced to count the horizontal and vertical edges that are involved at the interface between the black and the white pixels of the binary image.
+This geometrical quantity is nothing but the discrete perimeter (see \cite{HermineAgnes}), considering separately the horizontal contribution and the vertical one.
+
+Assuming that the original grey-level image is a discrete Gaussian stationary field, we are able to explicitely compute the first two moments of the so-called "oriented perimeter".
+Our study of moments includes the asymptotic behavior as the number of pixels goes to infinity, as well as numerical illustrations for various Gaussian distributions.
+We then establish a Central Limit Theorem for the joint oriented perimeters at various levels.
+The perimeter being given as a sum of functionals of correlated Gaussian variables, the main argument for the CLT that we use is borrowed from Breuer-Major result as exposed in \cite{Arcones}.
+Let us note that a similar study was performed in \cite{Psymetrie} but under a very different context since the underlying Gaussian field was supposed to be a white noise.
+The totally independent structure of the pixels yield simple computations and estimations which are not allowed anymore in the correlated situation that we consider in the present paper.
+
+The next step of our method consists in building the promised statistical test.
+More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language.
+We exhibit a statistic depending on the ratio of both oriented perimeters that goes to zero under $H0$ thanks to the CLT previoulsy established.
+Moreover, we prove the consistency of the proposed test.
+Let us insist on the fact that our test is a non-parametric one so that the alternative hypothesis reduces to $H1:~\rho(e_1)\ne \rho(e_2)$.
+{\sc verifier!}
+
+The theoretical study is completed by a large amount of numerical illustrations based on simulated data.
+We sample Gaussian fields with compact support covariances and use parametric deformations to get anisotropic models.
+The performances of our test are illustrated on those models.
+The crucial question of estimating the variance of the perimeter is also explored.
+
+\bigskip
+
+{\sc The paper is organized as follows ...}
+
+\bigskip
+\bigskip
+
+\textcolor{blue}{
 \textbf{Cabana : Affine Processes: A test of isotropy based on level sets.} 
@@
 By using standard ellipse, they can compute the direction of maximum variability in a direction of angle $\theta$.
-So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability
+So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability.
+}
+
 \section{Mathematical framework}\label{section1}
@@
 Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares.
-We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and
+We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and we introduce the following notations.
 \begin{itemize}
- \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ the set of points in $S$, to ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
- \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S$, the $C_{m}(x)$ will be referred to as \textit{cells}.
-\item[$\bullet$] And finally, we denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, for each $x \in \mathbb{G}_{m}$,  $i \in \{1, 2\}$, the edge $w_{i}(x)$ is a segment of length $1$ and belongs to~$C_{m}(x) \cap C_{m}(x+e_{i})$.
-The cardinality of the sets of edges
+ \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ is the set of points in $S$ that are considered.
+We write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
+ \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2}$ will be referred to as a \textit{cell}.
+Note that $S~= \cup_{x \in \mathbb{G}_{m}} C_{m}(x)$.
+\item[$\bullet$] We denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, and for each $x \in \mathbb{G}_{m}$, we denote by $w_{i}(x)$ the intersection, $C_{m}(x) \cap C_{m}(x+e_{i})$ with $ i \in \{1, 2\}$, the edge $w_{i}(x)$  is a segment of length $1$.
+And finally,
 \begin{itemize}
 \item 
-$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{1}(x) \in C_{m}(x) \cap C_{m}(x+e_{1})\right\} $\\ 
- \hspace*{4.25cm}$ =  \left\{ 1, m - 1\right\}\times\left\{ 0, m-1 \right\},$
-\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{2}(x) \in C_{m}(x) \cap C_{m}(x+e_{2}) \right\} $\\
- \hspace*{4.25cm}$ = \left\{ 0, m-1 \right\} \times \left\{ 1, m - 1\right\},$
+$\mathbb{G}^{(1)}_{m} := \left\{ x \in \mathbb{G}_{m}; \; C_{m}(x)\cap C_{m}(x + e_{1}) \subset \mathring{S} \right\} = [\![0,m-2]\!]\times[\![0,m-1]\!], $ \\
+\item $\mathbb{G}^{(2)}_{m} := \left\{ x \in \mathbb{G}_{m}; \; C_{m}(x)\cap C_{m}(x + e_{2}) \subset \mathring{S} \right\} = [\![0,m-1]\!]\times[\![0,m-2]\!]. $ \\
 \end{itemize}
@@
   \draw[step = 1cm, black, thick](0,0) grid (4,4);
-\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
-\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
-\foreach \x in {0,1,2,3}{
-  \foreach \y in {0,1,2,3}{
-  \draw[fill = red] (\x,\y) circle (2pt);
-  } 
-}
+\draw[pattern=north west lines, pattern color=green] (0,0) rectangle (1,1);
+\draw[pattern=north west lines, pattern color=green] (3,1) rectangle (2,2);
+\draw[red] (0.8, 0.5) -- (1.2, 0.5);
+\draw[red] (0.8, 1.5) -- (1.2, 1.5);
+\draw[red] (0.8, 2.5) -- (1.2, 2.5);
+\draw[red] (0.8, 3.5) -- (1.2, 3.5);
+\draw[red] (1.8, 0.5) -- (2.2, 0.5);
+\draw[red] (1.8, 1.5) -- (2.2, 1.5);
+\draw[red] (1.8, 2.5) -- (2.2, 2.5);
+\draw[red] (1.8, 3.5) -- (2.2, 3.5);
+\draw[red] (2.8, 0.5) -- (3.2, 0.5);
+\draw[red] (2.8, 1.5) -- (3.2, 1.5);
+\draw[red] (2.8, 2.5) -- (3.2, 2.5);
+\draw[red] (2.8, 3.5) -- (3.2, 3.5);
+\draw[step = 1cm, black, thick](8,0) grid (12,4);
+\draw[pattern=north west lines, pattern color=green] (8,0) rectangle (9,1);
+\draw[pattern=north west lines, pattern color=green] (11,1) rectangle (10,2);
+\draw[blue] (8.5, 0.8) -- (8.5, 1.2);
+\draw[blue] (9.5, 0.8) -- (9.5, 1.2);
+\draw[blue] (10.5, 0.8) -- (10.5, 1.2);
+\draw[blue] (11.5, 0.8) -- (11.5, 1.2);
+\draw[blue] (8.5, 1.8) -- (8.5, 2.2);
+\draw[blue] (9.5, 1.8) -- (9.5, 2.2);
+\draw[blue] (10.5, 1.8) -- (10.5, 2.2);
+\draw[blue] (11.5, 1.8) -- (11.5, 2.2);
+\draw[blue] (8.5, 2.8) -- (8.5, 3.2);
+\draw[blue] (9.5, 2.8) -- (9.5, 3.2);
+\draw[blue] (10.5, 2.8) -- (10.5, 3.2);
+\draw[blue] (11.5, 2.8) -- (11.5, 3.2);
+% \foreach \y in {1,2,3,}{
+%   \foreach \x in {8,9,10, 11, 12}{
+%   \draw[fill = green] (\x,\y) circle (2pt);
+%   } 
+% }
 \end{tikzpicture}
@@
 \vspace{-0.25cm}
-\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
+\caption{Square tiling for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (green stripes). We represent the vertical edges $w_{1}$ in red and  the horizontal ones $w_{2}$ in blue.}
 \label{figure1}
@@
 We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
-\vspace{-1.5cm}
-\begin{figure}[H]
-    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
-    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
-    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
 \vspace{-2cm}
- \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
+\begin{figure}[H]
+% \centering
+% {\includegraphics[scale=0.4]{Gaussianfiledexample.pdf}}
+{\includegraphics[scale=0.25]{Gaussianrandom001.pdf}}
+{\includegraphics[scale=0.25]{gaussianrandom01.pdf}}
+{\includegraphics[scale=0.25]{gaussianrandom1.pdf}}
+\end{figure}
+\vspace{-5cm}
+\begin{figure}[H]
+% \centering
+{\includegraphics[scale=0.25]{EX001.pdf}}
+{\includegraphics[scale=0.25]{EX01.pdf}}
+{\includegraphics[scale=0.25]{EX1.pdf}}
+\vspace{-2cm}
+ \caption{Generations of Gaussian random fields with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with~$m = 512$, and their respective thresholded image for $t=0$ and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
 \label{fig22}
 \end{figure}
-Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} \leq t$.
+Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} < t$.
 \subsection{Perimeter of a binary image}\label{methods}
@@
 \begin{Definition}[Oriented perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
-For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$).
-Then, the oriented perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
+For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$) and we call it the oriented perimeter of the binary image~$Z^{\scriptscriptstyle (m)}$,
 \begin{equation}
@@
 This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$.
+Using the former expression, we are also able to obtain an analytic expression for the first moment.
+\begin{Proposition}(Analytic expression for the first moment of the oriented perimeter)
+\label{analytic expression}
+\begin{itemize}
+  \item if $\rho(e_{i}) \in ]-1,1]$, 
+    {\small
+  \begin{align}
+  \label{propEquationFisrtmoment}
+  \mathbb{E}\left(f^{(i)}(t) \right) = \int_{\rho(e_i)}^{1}\frac{\exp(-t^2/(1+u))}{\pi\sqrt{(1-u^2)}}du
+  \end{align}}
+  \end{itemize}
+  \end{Proposition}
+\begin{proof}
+Let $t \in \mathbb{R}$, We consider the function $h_{t}$ defined as follow \begin{align*} 
+h_{t}: (-1,1) &\longrightarrow \mathbb{R}, \\
+x & \longmapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right),
+\end{align*}
+with $N \sim \mathcal{N}\left(0,1\right)$.
+We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and
+\begin{align*}p_{t}'(x) & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right), \\
+& = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
+& \hspace{0.7cm}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right), \\
+& = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}} \\
+& \hspace{0.7cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy,\\
+& = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right) \\
+& \hspace{0.7cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy,  \\
+& = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
+\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$.
+% \begin{align*}
+% h'(x) & = \mathbb{E}\left( \left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right. \\
+% & \hspace{5cm} \left. - \left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right)\\
+% & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
+% & \hspace{6cm}  \left. - \frac{2|N| - t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
+% & = \frac{1}{2(1+x)\sqrt{1-x^2}}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
+% & \hspace{5.5cm}  \left. - \left(2|N| - t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
+% & = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
+% &\hspace{0.5cm} \mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right. \\
+% &\hspace{2cm}\left. - \left(2|N| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
+% & = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}}\\
+% &\hspace{0.5cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right. \\
+% &\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy \\ 
+% & = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
+% &\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
+% &\hspace{5cm}\left. - \left(2y - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
+% & = \frac{-\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
+% & \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
+% & = \frac{-\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
+% & = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
+% \end{align*}
+\end{proof}
 \begin{remark}(Degenerate dependence cases.)
@@
 \end{remark}
-\paragraph{Total variation.}
-\textcolor{red}{
-In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object.
+\paragraph{Total variation.}In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object.
 It is possible to link this quantity the perimeter of $u$, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.
-In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.}
+In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.
 \begin{Proposition}
@@
 \end{remark}
-\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$.
+Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$.
 This result allows us to state that the oriented perimeter is a strictly decreasing function with respect to $\rho$.
-}
-\begin{Proposition}
+\begin{remark}
 \label{powertest}
-\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure.
-For any level $t$, we  have the following result:}
+Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure.
+For any level $t$, we  have the following result:
 \begin{equation*}
@@
 \end{equation*}
-\end{Proposition}
-\begin{proof}
-Let $t \in \mathbb{R}$, We consider the function $h$ defined as follow \begin{align*} 
-h: (-1,1) &\longrightarrow \mathbb{R}, \\
-x & \longmapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right) - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right),
-\end{align*}
-with $N \sim \mathcal{N}\left(0,1\right)$. The derivative of $h$ is equal to 
-\begin{align*}
-h'(x) & = \mathbb{E}\left( \left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right. \\
-& \hspace{5cm} \left. - \left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)'\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right)\\
-& = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
-& \hspace{6cm}  \left. - \frac{2|N| - t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
-& = \frac{1}{2(1+x)\sqrt{1-x^2}}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right. \\
-& \hspace{5.5cm}  \left. - \left(2|N| - t\sqrt{2(1-x)}\right)\Phi'\left(\frac{2t - |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right) \right) \\
-& = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
-&\hspace{0.5cm} \mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right. \\
-&\hspace{2cm}\left. - \left(2|N| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
-& = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}}\\
-&\hspace{0.5cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right. \\
-&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(\frac{t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy \\ 
-& = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
-&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
-&\hspace{5cm}\left. - \left(2y - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
-& = \frac{-\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
-& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
-& = \frac{-\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
-& = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
-\end{align*}
-Since for all $|x| < 1, \; h'(x) < 0$, $h$ is a strictly decreasing function. 
-\end{proof}
-\begin{remark}
-\label{remarkesperancetest}
-\textcolor{red}{The function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ being strictly decreasing, if $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$ then~$\rho(e_1) \neq \rho(e_2) $.
+This follows directly from \ref{analytic expression}.
+The function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ being strictly decreasing, if $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$ then~$\rho(e_1) \neq \rho(e_2) $.
 Now, assume that the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$.
 Then, the ratio $\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)$ would be distributed around $1$ in the case of isotropy.
-This consideration will be crucial for the proposed local isotropy testing procedure in the next section.}
+This consideration will be crucial for the proposed local isotropy testing procedure in the next section.
 \end{remark}
@@
 \end{enumerate} 
-\textcolor{red}{TCL}
 \begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
@@
 \begin{equation*}
-\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right),
+\frac{1}{m}\left(\begin{pmatrix} \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}) \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{2}) \\  \vdots \\ \mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})  \end{pmatrix} - \begin{pmatrix} \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{1}))  \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t_{r}))\\\mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{1})) \\ \vdots \\ \mathbb{E}(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t_{r})) \end{pmatrix}\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\Sigma_{2r}^{\textcolor{white}{}^{\star}}\right),
 \end{equation*}
-where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\star}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma^\star_{2r}$ given by
+where $\xrightarrow[]{d}$ holds for the convergence in distribution and $\mathcal{N}\left(0,\,\Sigma_{2r}^{\textcolor{white}{}^{\star}}\right)$ for the $2r$-dimensional centered Gaussian distribution with covariance matrix $\Sigma_{2r}^{\textcolor{white}{}^{\star}}$ given by
 \begin{align}
 \label{CovTCL}
-\Sigma^{\star}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
+\Sigma^{\textcolor{white}{}^{\star}}_{2r}(l,i,k,j) & : = \lim_{m \to \infty}\text{Cov}\left(\frac{1}{m}\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t_{l}),  \frac{1}{m}\mathcal{P}^{\scriptscriptstyle (j)}_{m}(t_{k}) \right)
 \end{align}
@@
 \end{proof}
-\textcolor{red}{We are now in position to construct the promised isotropy test.}
+We are now in position to construct the promised isotropy test.
 \subsection{Perimeter based local isotropy test}
-As previously discussed in Remark \ref{remarkesperancetest}, we now aim to build a test using the specific structure of the mean perimeter in the case of local isotropy.
+As previously discussed in Remark \ref{powertest}, we now aim to build a test using the specific structure of the mean perimeter in the case of local isotropy.
 Following the idea  in \cite{bierme2019}  we propose a method to test the local isotropy of the field $X$.
@@
 \end{remark}
-\section{Numerical studies}
-\subsection{Numerical studies of moments of the estimated perimeter}
-Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/2C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$
-Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
-\begin{equation}
-A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
-\end{equation}
-with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{X}(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C},$, note that $a\neq b$ if and only if $Y$ is anisotropic.
-We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$.
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
-}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{Testanisotropy2.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
-    \hspace{0.2cm} 
- \caption{$p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\hline
-\diagbox{b}{t} & 0.2 &  0.3 &  0.4 &  0.5 &  0.6 &  0.7 &  0.8 &  0.9  \\ \hline
-1  & 0.9866 &   0.9638 &  0.9971 &  0.9867 &  0.9674 &  0.9951 &  0.9754 &  0.9918  \\ \hline
-1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007  \\ \hline
-1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline 
-1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline
-2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0  \\ \hline
-\end{tabular}
-\end{center}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/3, \pi/4, \pi/5, \pi/6, \pi/8 $ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.2]{TestaniRatiovsRHO.pdf}}
-    {\includegraphics[scale=0.2]{TestaniRatiovsTVA.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{imageU.pdf}}
-    \hspace{3cm}
-    {\includegraphics[scale=0.3]{levelset30000.pdf}}
-    \hspace{0.2cm}
- \caption{ Image of level $30000$}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.25]{ConfidenceIntervalRDStD.pdf}}
-    {\includegraphics[scale=0.25]{BoxplotRDStD.pdf}}
-    \hspace{0.2cm}
- \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.25]{ConfidenceIntervalRDAu.pdf}}
-    {\includegraphics[scale=0.25]{BoxplotRDAu.pdf}}
-    \hspace{0.2cm}
- \caption{We represent the mean values of the ratio between the two oriented perimeters $\mathcal{P}^{1}, \mathcal{P}^{2}$ for real life data.}
-\label{fig2}
-\end{figure}
-\subsection{Theroretical and numerical study of the covariance of the perimeter}
+\paragraph{Estimation method of the variance.} We are going to consider two approaches for estimating the variance.
+The first approach rely on having $n$ independent realization of the random field $(X_{x})_{x \in \mathbb{G}_{m}}$  (\textit{i.e} $n$images of size $m$), we start by computing the ratio $(R_{m, i}(t))_{i \leq n}$ for all $n$ images for a fixed threshold level $t$, then we consider the classical empirical estimator of the variance $\hat{\text{Var}(R_{m})}$ which we denote $\hat{\sigma}^{\scriptscriptstyle (1)}_{n, m}(t)$.
+The second method that we will consider is inspired from \cite{ElenaCeline2020} and is referred to as the ``\textit{subwindow empirical variance estimation}'', it consists of cutting the window $S$ in $n$ sub-windows and considering the classical empirical variance estimator $\hat{\sigma}^{\scriptscriptstyle (2)}_{n, m}(t)$.
+This applies in the context of covariance functions with compact support, to establish the consistency of the estimator, we compute it on domains that infinitely distant, mimicking the classical context of independent and identically distributed random variables, that is described above.
+\subsection{Theoretical and numerical study of the covariance of the perimeter}
 Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$.
@@
 & \hspace{1cm} - \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq s \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right).
-\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff}
+\end{align}}Considering the first part of the previous equation, and applying Lemma \ref{lemmasommediff},
 {\small
@@
 & \hspace{-3cm}= \mathbb{E}\left(\mathbbm{1}_{\left\{ \left|2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right| \leq \left|\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}\right|\right\}}\mathbbm{1}_{\left\{ \left|2s - S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right| \leq \left|\Delta^{\scriptscriptstyle (i)}_x\right| \right\}}\right).
-\end{align*}} We know that $|\rho(e_1)| < 1$, and that $\tilde{\Sigma}_{i}(x)$ is invertible, thus, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$.
-We get the following decomposition \\
+\end{align*}}We know that $|\rho(e_1)| < 1$, and that $\tilde{\Sigma}_{i}(x)$ is invertible, thus, applying the Cholesky decomposition to the matrix $\tilde{\Sigma}_{i}(x)$ there exist a diagonal matrix $L(x)$ such that $\tilde{\Sigma}_{i}(x) = L(x)L(x)^{\star}$ with $L(x) = \begin{pmatrix} \sigma^{\scriptscriptstyle (-)}_{1} & 0 & 0 & 0 \\
+0 & \sigma^{\scriptscriptstyle (+)}_{1} & 0 & 0 \\
+\pi^{\scriptscriptstyle(-, i)}_{U}(x) & \pi^{\scriptscriptstyle(-, i)}_{V}(x) & \pi^{\scriptscriptstyle(-, i)}_{W}(x) & 0 \\
+\pi^{\scriptscriptstyle(+, i)}_{U}(x) & \pi^{\scriptscriptstyle(+, i)}_{V}(x) & \pi^{\scriptscriptstyle(+, i)}_{W}(x) & \pi^{\scriptscriptstyle(+, i)}_{Z}(x)
+  \end{pmatrix}$, furthermore $\tilde{\Sigma}_{i}(x)$ is assumed to be invertible, thus $\text{det}\left(L(x)\right) \neq 0$, which implies that $\pi^{\scriptscriptstyle(+, -)}_{W}(x) \neq 0$ and $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) \neq 0$.
+this decomposition allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$ and we get the following decomposition \\
 $\left\{
@@
 \end{remark}
-\subsubsection{Spatial independent case} 
+\subsubsection{Spatial independence at large distance} 
 Let us start by considering the four cells configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
@@
 }Thus, $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (j)}(z)\right) = 0.$
+\section{Numerical studies}
+\subsection{Numerical studies of moments of the estimated perimeter}
+The toy model we use to illustrate the test, is a parametric model that belongs to the class of affine Gaussian processes with a covariance function of compact support, which falls within the framework of the CLT.
+The parametric nature proves to be advantageous in the examination of the behavior of the test under the alternative hypothesis ($H1$).
+Let $X$ be a stationary, isotropic centered Gaussian field with covariance function given by $\rho(x) = (1 -3||x||_{2}/2C + (||x||_{2}/2C)^{3})\mathbbm{1}_{||x||_{2} < C}, x \in \mathbb{R}^2$.
+Let ${Y(x; a, b, \theta): x \in \mathbb{R}^{2}}$ be a random field equal in distribution to  $\{X(Ax): x\in \mathbb{R}^{2}\}$, where 
+\begin{equation}
+A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
+\end{equation}
+with $a, b \in \mathbb{R}^{2}$ and $\theta \in [0, \pi)$, the field $Y$ is also Gaussian with covariance function given by  $\rho_{Y}(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C}$, note that $a\neq b$ if and only if $Y$ is anisotropic.
+We chose to illustrate the computations of the statistics of the perimeter, using this covariance structure, and the value $\theta = 0$ and $a = 1$.
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{EsperanceUnedirection.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed for different values of $b$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
+}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{Testanisotropy2.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvaluesubwindow.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+
+\end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$.}
+\label{figsubwindow}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvalue.pdf}}
+    \hspace{0.2cm} 
+ \caption{$p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\hline
+\diagbox{b}{t} & 0.2 &  0.3 &  0.4 &  0.5 &  0.6 &  0.7 &  0.8 &  0.9  \\ \hline
+1  & 0.9866 &   0.9638 &  0.9971 &  0.9867 &  0.9674 &  0.9951 &  0.9754 &  0.9918  \\ \hline
+1.1 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0.0007  \\ \hline
+1.2 & 0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline 
+1.5 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0   \\ \hline
+2 &  0 &  0 &  0 &  0 &  0 &  0 &  0 &  0  \\ \hline
+\end{tabular}
+\end{center}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/12, \pi/8, \pi/6, \pi/3$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\paragraph{Blind angle}It is important to note that we only test a form of local isotropy, with preferential axis $(e_1,e_2)$ there exist anisotropic models where $\rho(e_1) = \rho(e_2)$, like it is the case when $\theta = \pi/4$, in that case the model is clearly anisotropic as we can see Figure and the test will accept the hypothesis.
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvaluepi4.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.2]{TestaniRatiovsRHO.pdf}}
+    {\includegraphics[scale=0.2]{TestaniRatiovsTVA.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
+\label{fig2}
+\end{figure}
+
+\subsection{directional sotropy test on real world Data}
+\paragraph{Study of the anisotropic nature of bone X-rays.}
+The X-ray images are from an retrospective multi-centric study that was conducted at
+three French research hospitals (Amiens, Orleans and Cochin in Paris).
+Patients were recruited from a program originated by the hospital of Orleans between Nov.
+2004 and Feb.
+2006.
+We analyzed $245$ X-ray images of calcaneus bones.
+%to assess if the distribution of the images is isotropic or not.
+and used a geometric tool to do so, but first and for most, their is a necessary post processing step which is to  to stationarize the images, in order to be in the correct framework.
+We first applied a preprocessing step in order to get stationary images. This step is performed by sustracting the trend which is represented by a plane obtained via a mean-square linear regression.
+\begin{figure}[H]
+\centering
+{\includegraphics[scale=0.5]{UnonstationariserUstationariser.pdf}}
+ \caption{Stationnarized image of a bone x-ray, with it's associted excursion sets thresholded at the first, second and third quartile.}
+\label{fig22}
+\end{figure}
+Estimation of $\rho(e_1)\sim0.94$ and $\rho(e_2)\sim0.96$
 \subsubsection{Behavior at large distance.}
@@
     \hspace{0.2cm}
- \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40$.
+ \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40, 30, 10,1$.
+}
+\label{fig2}
+\end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{subwindowVarestimation.pdf}}
+    \hspace{0.2cm}
+ \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$, for the values $b = 1$ and $C = 40$.
 }
@@
 \Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \sigma^{\scriptscriptstyle (-)}_{1}U,  \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-S^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x} & = &  \pi^{\scriptscriptstyle(i)}_{U}(x)U +  \pi^{\scriptscriptstyle(i)}_{V}(x) V +  \pi^{\scriptscriptstyle(i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0} & = & \hspace{1.55cm} \textcolor{white}{\sigma^{\scriptscriptstyle (-)}_{1}U,} \sigma^{\scriptscriptstyle (+)}_{1}V, \textcolor{white}{+  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
+S^{\scriptscriptstyle (1)}_{\scriptscriptstyle  x} & = &  \hspace{-1cm} \pi_{U}(x)U +  \pi_{V}(x) V +  \pi_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \text{\hspace{-2cm} with,} \\
+\end{array}\right.$\\ 
+$\left\{
+\begin{array}{rlc}
+ \pi_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(1 + \rho(x-e_1) - \rho(e_1) - \rho(x)\right) \\
+\pi_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(1 + \rho(x-e_1) + \rho(e_1) + \rho(x)\right) \\
+\pi_{W}(x) & = & \left(\sigma^{\scriptscriptstyle (+)}_{1} - \pi_{U}(x)^{2} - \pi_{V}(x)^{2} \right)^{1/2} \\
 \end{array}\right.$ \\

### 2023-01-20 Draft_GFC.tex
Courage

@@
 By the texture of an image, we mean the microscopic structure that is captured by the covariance function at the pixels scale.
-In order to achieve this goal, we propose a methodology built on a statistical test for which all components are rigourously validated.
-The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the pixels values.
-Let us first start with an exemple of medical images where our methodology is applied.
-
-\begin{figure}[H]
-\centering
-{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
- \caption{Stationnarized image of a bone x-ray, with it's associted excursion sets thresholded at the first, second and third quartile.}
-\label{fig22}
-\end{figure}
-
-Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We consider the thresholded image at level $t_{\alpha}$, $\{X > t_{\alpha}\}$, and then 
-%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, 
-count the respective numbers of horizontal and vertical edges that are involved in the perimeter of the black region of the binary image.
-In case of an isotropic texture, the ratio of these two counters should be close to one.
-At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.
-
-The ratio has been computed for each image of the panel at various quantile levels. In Figure \ref{fig2}, the distribution of the obtained ratios is summerized in a boxplot for each level.
-
-\begin{figure}[H]
-  \centering  
-   {\includegraphics[scale=0.28]{BoxplotRDAu.pdf}}
-    \hspace{0.2cm}
- \caption{For $\alpha \in [0.15, 0.9]$, we represent on the left, the confidence interval of the mean of the ratio between the two oriented perimeters computed for $t_{\alpha}, \mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$ and its corresponding boxplot for real thresholded images of bone X-rays.}
-\label{fig2}
-\end{figure}
-
-We observe that the boxplots of the ratio between the horizontal and vertical counters are not distributed around one, whatever the observed level. 
-Moreover, for almost all images the observed ratios are above one whereas for some images extreme values are observed below one.
-We checked the fact that these extreme cases below one all belong to the same small group of images.
-Apparently, these images were subject to a $\pi/2$-angle rotation.
-Nevertheless, what is relevant on this sample of X-ray images of calcaneus is that the anisotropy of the texture can be revealed at any threshold level by simply comparing two single counters.
-It is worth to note that this anisotropy, although obvious through the proposed image analysis procedure, is not perceptible to the naked eye.
-
-With a very different approach based on quadratic variations, the same sample of images has been analyzed in \cite{Richard??} and the same conclusion has been obtained: the calcaneus X-ray images are anisotropic.
-A by-product of our method is the measurement of the anisotropy through the ratio between the oriented perimeters.
-It will be used to produce a test of isotropy.
-
-\bigskip
-
-The present paper is part of the methodological literature that deals with statistical inference based on geometrical observable features.
-Although it is an old engineers question (see \cite{Longuet-Higgins} for instance), it has recently received much attention from a statistical point of view.
-To cite some of these papers, let us quote \cite{Worsley96} where the localization of peaks are infered from the observation of the Euler chracteristic in neuroimaging, \cite{Molina} where isotropy is tested through the observation of the gradient, \cite{DEL17} or \cite{bierme2019} where a test of Gaussianity is produced based on the Euler characteristic of excursion sets, \cite{Psymetrie} where a test of symmetry is produced based on the perimeter of thresholded images,  ({\sc \`a verifier et completer avec d'autres non li\'es \`a notre "famille".
+In order to achieve this goal, we propose a methodology built on a statistical test for which all steps are rigorously validated.
+The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the underlying random field that is supposed to serve as a model.
+More precisely, our observable statistic will be the black domain perimeter in thresholded images.
+
+The present paper is part of the methodological literature that deals with statistical inference based on geometrical observable features given by the Lipschitz-Killing curvatures (LKC) of the excursion sets.
+In image analysis, an excursion set is a region of the image where the pixel's value is higher than a fixed level, the level set is the boundary of the excursion set and the LKC's are the three natural Minkovski functionals: Euler characteristic (number of connected components minus number of holes), perimeter (length of the boundary), area (Lebesgue measure).
+Although such type of statistical study is an old engineers task (see \cite{Longuet-Higgins} for instance), it has recently received much attention from a probability theory and mathematical statistics point of view.
+To cite some of these papers, let us quote \cite{Worsley96} where the localization of peaks is infered from the observation of the Euler characteristic of excursion sets in neuroimaging, \cite{Molina} where isotropy is tested through the observation of the gradient, \cite{DEL17} or \cite{bierme2019} where a test of Gaussianity is produced based on the Euler characteristic of excursion sets, \cite{Psymetrie} where a test of symmetry is produced based on the perimeter of thresholded images,  ({\sc \`a verifier et completer avec des papiers exterieurs \`a notre "famille".
 Pour chacun, what is infered?
@@
 In particular, let us focus on two specific articles \cite{cabana1987affine, Berzin} with a similar objective as our, namely a test of isotropy, and based on similar observations, namely the length of level sets.
-{\sc Expliquer la methode de ces papiers et les differences avec le present papier}.
-Implementations of this type of method can be found in cosmology, neuroimaging and medical imaging in general, hydrology, etc.
+Both papers are concerned with affine two-dimensional random fields, \emph{i.e.} stationary random fields $X$ defined on $\mathbb{R}^2$ and given as $X(\cdot)=Z(A\cdot)$, where $Z$ is centered, stationary and isotropic defined on $\mathbb{R}^2$ and $A$ is a matrix that can be reduced to $\begin{pmatrix} a&0\\0&b\end{pmatrix} \,\begin{pmatrix} \cos \theta & \sin \theta \\ -\sin \theta & \cos \theta\end{pmatrix}$.
+Within this continuous parametric frame, $X$ is isotropic in distribution if and only if $a=b$.
+In both articles, a test of isotropy is constructed, based on the measurement of the respective horizontal and vertical components of the length of the level sets.
+In the former article, some mixing condition yields a Gaussian asymptotics of the normalized level set length, while in the later article, a Gaussian condition  yields a similar result.
+This central limit theorem is the crux for establishing a fair statistical test.
+
+Implementations of this type of method can be found in medical imaging and image analysis in general, cosmology, hydrology, sea waves modeling, etc.
+As an example, let us exhibit some medical images that can be handled with our methodology.
+In this introductory part, we just show the images and a first tentative of descriptive statistics.
+The statistical results that we are able to infer from our methodology is detailed at the end of the present paper (see Section 4.3).
+%\paragraph{Study of the anisotropic nature of bone X-rays.}
+%\textcolor{blue}{\textbf{Dans le papier, ils disent qu'ils ont 174 images, j'en ai 245 dans le dossier.}}
+%The X-ray images are from an retrospective multi-centric study that was conducted at
+%three French research hospitals (Amiens, Orleans and Cochin in Paris). ({\sc details necessaires?})
+%Patients were recruited from a program originated by the hospital of
+%Orleans between Nov. 2004 and Feb. 2006. 
+We analyzed $245$ X-ray images of calcaneus bones in order to detect the eventual anisotropic nature of the microarchitecture.
+%to assess if the distribution of the images is isotropic or not.
+and used a geometric tool to do so, but first and for most, their is a necessary post processing step which is to  to stationarize the images, in order to be in the correct framework.
+We first applied a preprocessing step in order to get stationary images 
+%This step is performed by sustracting the trend which is represented by a plane obtained via a mean-square linear regression.
+and then 
+%Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We 
+consider the thresholded images at various quantile levels $t_{\alpha}$, \emph{i.e.} the binary images $\{X > t_{\alpha}\}$.
+\begin{figure}[H]
+\centering
+{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
+ \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}
+\label{fig22}
+\end{figure}
+As observable statitics, we use 
+%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, count
+the respective numbers of horizontal and vertical edges that separate a black pixel from a white pixel of the binary image.
+We name these counters as oriented perimeters, horizontal and vertical respectively.
+In case of an isotropic texture, the ratio of the two oriented perimeters should be close to one.
+At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.
+
+The ratio has been computed for each image of the panel at various quantile levels $t_{\alpha}$.
+In Figure \ref{figBoxplot}, the distribution of the obtained ratios is summerized in a boxplot for each level.
+
+\begin{figure}[H]
+  \centering
+    %{\includegraphics[scale=0.25]{ConfidenceIntervalRDAu.pdf}}
+    {\includegraphics[scale=0.28]{BoxplotRDAu.pdf}}
+    \hspace{0.2cm}
+ \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratio between the two oriented perimeters computed at $t_{\alpha}$ level, $\mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$, for real thresholded images of bone X-rays.}
+\label{figBoxplot}
+\end{figure}
+
+We observe that the boxplots of the ratio between the horizontal and vertical perimeters are not distributed around one, whatever the considered level. 
+%Which occurs when the distribution of the oriented perimeter is not the same, which appears to be the case in an anisotropic framework.
+Moreover, for almost all images the observed ratios are above one whereas for some images extreme values are observed below one.
+We checked the fact that these extreme cases below one all belong to the same small group of images.
+%Apparently, these images were subject to a $\pi/2$-angle rotation. 
+Nevertheless, what is relevant on this sample of X-ray images of calcaneus is that the anisotropy of the texture can be revealed at any threshold level by simply comparing two single counters.
+It is worth to note that this anisotropy, although obvious through the proposed image analysis procedure, is not perceptible to the naked eye.
+\\
+With a very different approach based on quadratic variations, the same sample of images has been analyzed in \cite{Richard-Birme} and the same conclusion has been obtained: the calcaneus X-ray images are anisotropic.
+In the present paper, our work consists in a theoretical study of the oriented perimeters seen as random objects: proper definition, first moments, asymptotic behaviour as the size of image goes to infinity.
+A by-product of our method is the measurement of the anisotropy through the ratio between the oriented perimeters.
+It is used to produce a test of isotropy.
 
@@
 Let us note that a similar study was performed in \cite{Psymetrie} but under a very different context since the underlying Gaussian field was supposed to be a white noise.
-The totally independent structure of the pixels yield simple computations and estimations which are not allowed anymore in the correlated situation that we consider in the present paper.
+The induced totally independent structure of the pixels led to simple computations and estimations which are not allowed anymore in the correlated situation that we consider in the present paper.
 
@@
 More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language.
-We exhibit a statistic depending on the ratio of both oriented perimeters that goes to zero under $H0$ thanks to the CLT previoulsy established.
+We exhibit a statistic depending on the ratio of the oriented perimeters that goes to one under $H0$ thanks to the CLT previoulsy established.
 Moreover, we prove the consistency of the proposed test.
 Let us insist on the fact that our test is a non-parametric one so that the alternative hypothesis reduces to $H1:~\rho(e_1)\ne \rho(e_2)$.
-{\sc verifier!}
-
-The theoretical study is completed by a large amount of numerical illustrations based on simulated data.
+
+The theoretical study is completed by extensive numerical illustrations based on simulated data.
 We sample Gaussian fields with compact support covariances and use parametric deformations to get anisotropic models.
@@
 The crucial question of estimating the variance of the perimeter is also explored.
+Finally, we apply our method to the calcaneus X-ray images that we have already presented.
+It allows us to infer properties and to estimate quantities that could be of interest from a medical point of view.
 
@@
 
-{\sc The paper is organized as follows ...}
+The paper is organized as follows.
+Section 2 is devoted to the presentation of the mathematical framework, namely the grid  that defines the pixels and implies the discrete nature of the Gaussian random field that we use as a model for the grey-level image.
+We also precisely define the notion of discrete oriented perimeters that we consider all over the article.
+In Section 3, we proceed to the statistical study of the oriented perimeters by computing their first two moments and establishing a joint central limit theorem for both directions and various levels.
+Section 4 contains the numerical studies.
+Section 4.1 is dedicated to Monte-Carlo estimations of the variance of the oriented perimeter for a Gaussian toy model and to numerical illustrations of the local isotropy test for the same toy model.
+Section 4.2 is dedicated to the numerical analysis of the variance given as a convergent series and Section 4.3 to the statistical analysis of real data, the bones X-ray images that we already mentioned.
 
@@
 
-\textcolor{blue}{
+\begin{comment}
 \textbf{Cabana : Affine Processes: A test of isotropy based on level sets.} 
@@
 So, they are able to describe the spatial behavior of the mean vectors, quantifying by the calculation of $\theta$ the direction of maximum variability.
-}
+\end{comment}
 
@@
 \label{analytic expression}
-\begin{itemize}
-  \item if $\rho(e_{i}) \in ]-1,1]$, 
-    {\small
   \begin{align}
@@
   \mathbb{E}\left(f^{(i)}(t) \right) = \int_{\rho(e_i)}^{1}\frac{\exp(-t^2/(1+u))}{\pi\sqrt{(1-u^2)}}du
-  \end{align}}
-  \end{itemize}
+  \end{align}
   \end{Proposition}
@@
 We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and
-\begin{align*}p_{t}'(x) & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right), \\
+\begin{align*}p_{t}'(x) & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right)\\
 & = \frac{\exp(-t^2/(1+x))}{2\sqrt{2\pi}(1+x)\sqrt{1-x^2}}\\
-& \hspace{0.7cm}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right), \\
+& \hspace{0.7cm}\mathbb{E}\left(\left(-2|N| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|N|\sqrt{2(1-x)}}{1+x}\right)\exp\left(\frac{-N^{2}(1-x)}{2(1+x)}\right)\right) \\
 & = \frac{\exp(-t^2/(1+x))}{4\pi(1+x)\sqrt{1-x^2}} \\
-& \hspace{0.7cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy,\\
+& \hspace{0.7cm} \int_{-\infty}^{\infty}\exp\left(-\frac{y^2}{1+x}\right)\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(\frac{-t|y|\sqrt{2(1-x)}}{1+x}\right)\right)dy\\
 & = \frac{\exp(-t^2/(1+x))}{2\pi(1+x)\sqrt{1-x^2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right) \\
-& \hspace{0.7cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy,  \\
+& \hspace{0.7cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
 & = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
@@
 \begin{remark}(Degenerate dependence cases.)
+\label{casdegenerer}
 \begin{itemize}
 \item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, note that $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
+\item In the case where $\rho(e_i) \sim 1$, then $\mathbb{E}\left(f^{(i)}(t) \right) \sim \frac{\sqrt{1-\rho(e_i)}}{\pi\sqrt{2}} \exp(-t^2/2)$, as in \cite{HermineAgnes}, in that case the ratio $\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)$ is invariant in regard to $t$
 \item In the independent case, \textit{i.e.} $\rho(e_{i}) = \text{Cov}\left(X_{0}, X_{e_i}\right) = 0$, we can write
@@
 \label{isotest}
-In order to construct a local isotropy test using the oriented perimeter of the field $X$, we first  establish a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$.
-To do that, we have to add some assumptions on $\rho$ the covariance structure of the field $X$.
+In order to construct a local isotropy test using the oriented perimeter of the binary image, we first  establish a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$.
+To do that, we add some assumptions on $\rho$, the covariance structure of the field $X$.
 \begin{enumerate}
@@
 \begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold).
-We consider that $(X_{x})_{x\in \mathbb{G}_{m}}$ is a centered stationary standard Gaussian field.
+We consider that $(X_{x})_{x\in \mathbb{G}_{m}}$ is a centered stationary standard Gaussian field with a covariance function what satisfies (\textbf{A}1) and (\textbf{A}2).
 Let $r$ be a positive integer and $t_{1}, \cdots,t_{r} \in \mathbb{R}$.
-Then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},
 \begin{equation*}
@@
 \begin{proof} For the sake of simplicity, we will prove the theorem for $r=1$, the generalized case can be established by following the same procedure.
-Using the Cramèr-Wold method, we will prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have
+Let~$ t \in \mathbb{R}$, using the Cramèr-Wold method, we will prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have
 \begin{align*}
@@
 \end{align*}
-with $\sigma^{2}(t) < \infty$. Let~$ t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$, we recall the notation introduced in \eqref{fi}
+with $\sigma^{2}(t) < \infty$. For $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$, we recall the notation introduced in \eqref{fi}
 \begin{align*}
@@
 \end{align*}
-Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 
+Let us introduce the 4-dimensional Gaussian vector $\mathbb{X}_{x} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and the function $g_{t}$ defined on  $\mathbb{R}^{4}$, 
 \begin{align*}
@@
 As previously discussed in Remark \ref{powertest}, we now aim to build a test using the specific structure of the mean perimeter in the case of local isotropy.
-Following the idea  in \cite{bierme2019}  we propose a method to test the local isotropy of the field $X$.
+We propose a method to test the local isotropy of the field $X$.
 Let us consider the null hypothesis
@@
   $H_{0}$ \, :\; $\rho(e_1) = \rho(e_2)$.
-\end{center}
+\end{center}ttt
 Under $H_{0}$, let us remark that $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t) \right)= \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)\right)$ and $\mathbb{V}\left(\mathcal{P}^{\scriptscriptstyle  (1) }_{m}(t) \right)= \mathbb{V}\left(\mathcal{P}^{\scriptscriptstyle  (2) }_{m}(t)\right)$ for all~$t$.
@@
 \begin{Proposition}[Ratio of oriented perimeters]\label{deltamethodgeneralprop} 
-Let  $t \in \mathbb{R}$, and $\mathcal{P}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre}. Then, it holds that,
+Let  $t \in \mathbb{R}$, and $\mathcal{P}_{m}^{\scriptscriptstyle  (i) }(t)$ be the oriented perimeter over direction $i$, introduced in Definition \ref{defPerimetre}, under the same assumptions as in Theorem \ref{TCL}, it holds that,
 \begin{equation*}
@@
 \end{Lemma}
-Let $x \in \mathbb{Z}^{2}$ such that the covariance matrix $\Sigma_{i}(x)$ of the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ is invertible, 
+Let us now proceed and compute the contribution of the 4-cells configuration to the covariance.
+Let $x \in~\mathbb{Z}^{2}$ such that the covariance matrix $\Sigma_{i}(x)$ of the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ is invertible, 
 $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
@@
 \rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$
-Let us define the following quantities   \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
+Let us define the following quantities   
 \begin{center}
@@
  \begin{array}{rlc}
- \sigma^{\scriptscriptstyle (-)}_{1} & = &  \sqrt{2(1-\rho(e_1))} \\
- \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
- \end{array}\right.$ \\
+ \sigma^{\scriptscriptstyle (-)}_{1} & = &  \hspace{-6.9cm} \sqrt{2(1-\rho(e_1))} \\
+ \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \hspace{2cm} \text{with $\sigma^{\scriptscriptstyle (-)}_{1} > 0,  \; \sigma^{\scriptscriptstyle (+)}_{1} > 0 $, and} \\
+ \end{array}\right.$\\
  $\left\{
  \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \hspace{-3cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right)  \\
-   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = & \hspace{-3cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
-   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)}, \end{array}\right.$ \\
-    $\left\{
+   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \hspace{-8cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = & \hspace{-8cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
+   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \text{with also $\pi^{\scriptscriptstyle(-, i)}_{W}(x) > 0$, and}, \end{array}\right.$   \\ $\left\{
  \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = & \hspace{-5cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
-    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \hspace{-5cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
-     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \hspace{-1.5cm} \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
-   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}.
+   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = & \hspace{-9.5cm} \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
+    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \hspace{-9.5cm} \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
+     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \hspace{-6cm} \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
+   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \text{and finally, $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) > 0$}.
 \end{array}\right.$  \\
@@
 \begin{proof}(Proof of Proposition \ref{PropositionFourCell})
-Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $$\Sigma_{i}(x) = \begin{pmatrix} 1 & \rho(e_1) & \rho(x) & \rho(x+e_i)\\
-\rho(e_1) & 1 & \rho(x-e_1) &  \rho(x+e_i- e_1) \\ 
-\rho(x) & \rho(x-e_1) & 1 & \rho(e_i) \\
-\rho(x+e_i) & \rho(x+e_i-e_1) & \rho(e_i) & 1 \end{pmatrix}.$$ 
+Let us consider the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_1}, X_{\scriptscriptstyle x}, X_{x+e_i}\right)$ of covariance matrix given by $\Sigma_{i}(x)$ 
 Let us define the following quantities   \begin{equation} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} - X_{\scriptscriptstyle x}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} := X_{x+e_i} + X_{\scriptscriptstyle x},\end{equation}
-\begin{center}
-$\Delta \rho(x) = \rho(x-e_1)-\rho(x)$ and $S\rho(x)  =  \rho(x-e_1)+\rho(x)$.
-\end{center}
 The covariance matrix of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}, \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x}\right)$ is equal to ${\tilde{\Sigma}_{i}(x)~= M\Sigma_{i}(x) M^{\star}}$ with {\small $M = \begin{pmatrix}
@@
   \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle  x}& = &  \pi^{\scriptscriptstyle(-, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(-, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) W, \textcolor{white}{ + \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, } \\
-  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z, \text{with}
-\end{array}\right.$ \\
-$\left\{
- \begin{array}{rlc}
- \sigma^{\scriptscriptstyle (-)}_{1} & = &  \sqrt{2(1-\rho(e_1))} \\
- \sigma^{\scriptscriptstyle (+)}_{1} & = & \sqrt{2(1+\rho(e_1))} \\
- \end{array}\right.$ \\
- $\left\{
- \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(-, i)}_{U}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x+e_i) -\Delta \rho(x)\right) \\
-   \pi^{\scriptscriptstyle(-, i)}_{V}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S\rho(x+e_i)-S\rho(x)\right)  \\
-   \pi^{\scriptscriptstyle(-, i)}_{W}(x)& = & \left(2(1 - \rho(e_{i})) - \pi^{\scriptscriptstyle(-, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(-, i)}_{V}(x)^{2}\right)^{\scriptscriptstyle (1/2)} \end{array}\right.$ \\
-    $\left\{
- \begin{array}{rlc}
-   \pi^{\scriptscriptstyle(+, i)}_{U}(x) & = &  \frac{1}{\sigma^{\scriptscriptstyle (-)}_{1}}\left(\Delta \rho(x) + \Delta \rho(x+e_i)\right) \\
-    \pi^{\scriptscriptstyle(+, i)}_{V}(x) & = & \frac{1}{\sigma^{\scriptscriptstyle (+)}_{1}}\left(S \rho(x) + S\rho(x+e_i)\right) \\
-     \pi^{\scriptscriptstyle(+, i)}_{W}(x) & = & \frac{-1}{\pi^{\scriptscriptstyle(-, i)}_{W}(x)}\left(\pi^{\scriptscriptstyle(-, i)}_{U}(x)\pi^{\scriptscriptstyle(+, i)}_{U}(x) + \pi^{\scriptscriptstyle(-, i)}_{V}(x)\pi^{\scriptscriptstyle(+, i)}_{V}(x)\right) \\
-   \pi^{\scriptscriptstyle(+, i)}_{Z}(x)& = & \left(2(1 + \rho(e_i)) - \pi^{\scriptscriptstyle(+, i)}_{U}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{V}(x)^{2} - \pi^{\scriptscriptstyle(+, i)}_{W}(x)^{2}\right)^{\scriptscriptstyle (1/2)}.
+  S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} & = &    \pi^{\scriptscriptstyle(+, i)}_{U}(x)U +  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V +  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W +  \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z.
+
 \end{array}\right.$ \\
@@
 & = \mathbbm{1}_{\big\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z} \\
-& \hspace{3cm} _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}
-\end{align*}}Thus, 
+& \hspace{3cm} _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}},
+\end{align*}}thus, 
 \begin{align*}
@@
 \end{remark}
-\subsubsection{Spatial independence at large distance} 
-Let us start by considering the four cells configuration and let us see what happens when ${\rho(x) = \rho(x+e_i) = \rho(x-e_i) = \rho(x + e_i - e_1) = 0}$, supposedly when $x > > 0$. Then
-$\pi^{\scriptscriptstyle(-, i)}_{W}(x) = \sqrt{2(1-\rho(e_i))}$, $\pi^{\scriptscriptstyle(+, i)}_{W}(x) = 0$ and $\pi^{\scriptscriptstyle(+, i)}_{Z}(x) = \sqrt{2(1+\rho(e_i))}.$ Thus, Equation \eqref{Thisthofour} becomes
-{\small
-\begin{align*}
-\mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_1}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_1})\right\}}\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle x}, X_{x+e_i}) \leq s \leq \max(X_{\scriptscriptstyle x}, X_{x+e_i}) \right\}}\right) \nonumber \\
-& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}} \right.  \\
-& \left.
-\hspace{-10cm} \left(\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_i))}W \geq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \sqrt{2(1-\rho(e_1))} W\right) - \Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left(2s - \sqrt{2(1-\rho(e_1))} W\right)\right) \right.
-\right.
-\\
-&  \hspace{-10cm} \left.
-\left.
-\mathbbm{1}_{\left\{\sqrt{2(1-\rho(e_1))} W  \leq 0\right\}} \left(\Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \sqrt{2(1-\rho(e_1))}W \right) - \Phi_{\pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left(2s + \sqrt{2(1-\rho(e_1))} W\right)\right)\right)\right)\\
-& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}}\mathbbm{1}_{\left\{ |s - \frac{\sqrt{2(1+\rho(e_i))}Z}{2}| \leq |\frac{\sqrt{2(1-\rho(e_i))}W}{2}|\right\}}\right) \\
-& \hspace{-10cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |t - \frac{\sqrt{2(1+\rho(e_1))}V}{2}| \leq |\frac{\sqrt{2(1-\rho(e_1))}U}{2}|\right\}}\right)\mathbb{E}\left(\mathbbm{1}_{\left\{ |s - \frac{\sqrt{2(1+\rho(e_i))}Z}{2}| \leq |\frac{\sqrt{2(1-\rho(e_i))}W}{2}|\right\}}\right).
-\end{align*}
-}Thus, $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (j)}(z)\right) = 0.$
 \section{Numerical studies}
 \subsection{Numerical studies of moments of the estimated perimeter}
-The toy model we use to illustrate the test, is a parametric model that belongs to the class of affine Gaussian processes with a covariance function of compact support, which falls within the framework of the CLT.
+The toy model we use to illustrate the test, is a parametric model that belongs to the class of affine Gaussian processes with a covariance function of compact support, commonly known as `$m$-dependent field', the parameter $m$ designates the range of dependence meaning that for $||x||_{2} > C$, $\text{Cov}\left(X_{0}, X_{x}\right) = 0$ and in particular $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (i)}(x)\right) = 0$.
+This model falls within the framework of the CLT.
 The parametric nature proves to be advantageous in the examination of the behavior of the test under the alternative hypothesis ($H1$).
@@
 }
-\label{fig2}
+% \label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange.}
+\label{figsubwindow}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{fourConfNew.pdf}}
+    \hspace{0.2cm}
+ \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1, 1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
+}
+\label{figfourConNew}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
+    \hspace{0.2cm}
+ \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40, 30, 10,1$.
+}
+\label{figVariance}
+\end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.3]{subwindowVarestimation.pdf}}
+    \hspace{0.2cm}
+ \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$, for the values $b = 1$ and $C = 40$.
+}
+\label{figSubwindowVariance}
 \end{figure}
@@
  \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.4]{TestaniRatiopvaluesubwindow.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent the values of $\hat{\Phi}_{m}(b)$ see Equation \eqref{phihat} in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
-
-\end{figure}
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{EsperanceUnedirectionfonctionB.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent the values of first moment of the oriented perimeter in direction $2$ computed as a fonction of $b$ for a fixed level $t = 0$, the theoretical curve Equation \eqref{propFisrtmoment} is depicted using a blue color (blue) and the empirical values are in orange, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$.}
-\label{figsubwindow}
+% \label{fig2}
 \end{figure}
@@
  \caption{$p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1, 1.1, 1.2, 1.5, 2$ and $C = 40$.}
-\label{fig2}
+% \label{fig2}
 \end{figure}
@@
   \centering
+    {\includegraphics[scale=0.4]{TestaniRatiopvaluesubwindow.pdf}}
+    \hspace{0.2cm} 
+ \caption{We represent the $p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ the computations for the variance were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$  for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
+% \label{fig2}
+
+\end{figure}
+\begin{figure}[H]
+  \centering
     {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
@@
  \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/12, \pi/8, \pi/6, \pi/3$ and $C = 40$.}
-\label{fig2}
+% \label{fig2}
 \end{figure}
@@
 \paragraph{Blind angle}It is important to note that we only test a form of local isotropy, with preferential axis $(e_1,e_2)$ there exist anisotropic models where $\rho(e_1) = \rho(e_2)$, like it is the case when $\theta = \pi/4$, in that case the model is clearly anisotropic as we can see Figure and the test will accept the hypothesis.
+\textcolor{red}{Add discussion about this, l'erreur de type 1 et 2.}
 \begin{figure}[H]
@@
  \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$.}
-\label{fig2}
+% \label{fig2}
 \end{figure}
@@
  \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
-\label{fig2}
+% \label{fig2}
 \end{figure}
@@
  \caption{We represent the values of the mean of the ratio between the oriented perimeter $\mathbb{E}\left(\frac{\mathcal{P}^{(1)}(0)}{\mathcal{P}^{(2)}(0)}\right)$ in blue and the ratio between of the empirical value for $\hat{\rho(e_i)}$ computed using the first moment of the total variation (\ref{totalvariation}) for different values of $b$, Montecarlo $= 500$, $t = 0$ and $C = 40$.}
-\label{fig2}
-\end{figure}
-
-\subsection{directional sotropy test on real world Data}
+% \label{fig2}
+\end{figure}
+\subsection{Application of the local isotropy test to real world Data}
 \paragraph{Study of the anisotropic nature of bone X-rays.}
@@
 We analyzed $245$ X-ray images of calcaneus bones.
-%to assess if the distribution of the images is isotropic or not.
-and used a geometric tool to do so, but first and for most, their is a necessary post processing step which is to  to stationarize the images, in order to be in the correct framework.
-We first applied a preprocessing step in order to get stationary images. This step is performed by sustracting the trend which is represented by a plane obtained via a mean-square linear regression.
+We first applied a preprocessing step in order to get stationary images.
+This step is performed by substracting the trend which is represented by a plane obtained via a mean-square linear regression, to avoid boundarie issues, we decided to crop from a $400\times400$  image to a $300\times300$ image.
 \begin{figure}[H]
@@
 {\includegraphics[scale=0.5]{UnonstationariserUstationariser.pdf}}
- \caption{Stationnarized image of a bone x-ray, with it's associted excursion sets thresholded at the first, second and third quartile.}
+ \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}
 \label{fig22}
 \end{figure}
-Estimation of $\rho(e_1)\sim0.94$ and $\rho(e_2)\sim0.96$
-\subsubsection{Behavior at large distance.}
+\paragraph{Applying the local isotropy test.}The first analysis of Figure \ref{figBoxplot} suggests that an additional pre-processing step is required.
+We observe a cluster of points for which the ratio $\mathcal{P}_{1}(q_{\alpha})/\mathcal{P}_{2}(q_{\alpha}) < 1$, which means that the corresponding images are misoriented.
+Thus, before proceeding with the analysis, it is necessary to apply a $\pi/2$-rotation to these images, which amounts to interchanging the values of $\mathcal{P}_{1}(q_{\alpha})$ and $ \mathcal{P}_{2}(q_{\alpha})$, here is the new boxplot that,
+\vspace{-0.5cm}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{Boxplotimageretourne.pdf}}
+    \hspace{0.2cm}
+ \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratio between the two oriented perimeters computed at $t_{\alpha}$ level, $\mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$, for real thresholded images of bone X-rays.}
+\label{Boxplotretournee}
+\end{figure}
+\vspace{-0.5cm}
+We can now proceed to apply the local isotropy test, we start by computing the ratio $R_{i}(q_{\alpha})$ for each level set of the image $U_{i}$ at quantile level $\alpha$, with then compute the $p_{value}(q_{\alpha}) = 2(1-\mathbb{P}\left(\mathcal{N} \leq \left|\overline{R}_{n}(q_{\alpha}) - 1)\right|/\overline{\sigma}_{n}(q_{\alpha})\right))$.
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.38]{Testalphadonnereel.pdf}}
+    \hspace{0.2cm}
+ \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{alpha}$ for real thresholded images of bone X-rays.}
+% \label{fig}
+\end{figure}
+The $p_{value}$ is lower than $0.001$, except for extreme values of $q_{\alpha}$ (\textit{i.e} $\alpha = 0.99$), this leads us to reject $H_{0}$ of having local isotropy, furthermore, when analyzing Figure \ref{Boxplotretournee} the distribution of the ratio $\left(R_{i}(t)\right)_{i\leq n}$ seems to be invariant in regards to the threshold level as cited in \ref{casdegenerer}, this suggests that the field is highly dependent, the next step would be to estimate $\rho(e_i)$ by using the total variation of the image by applying Proposition \ref{Variationtotal}.
+% \begin{figure}[H]
+%   \centering
+%     {\includegraphics[scale=0.4]{rho.pdf}}
+%     \hspace{0.2cm}
+%  \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{alpha}$ for real thresholded images of bone X-rays.}
+% % \label{fig}
+% \end{figure}
+% \begin{figure}[H]
+%   \centering
+%     {\includegraphics[scale=0.4]{boxplotrho.pdf}}
+%     \hspace{0.2cm}
+%  \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{alpha}$ for real thresholded images of bone X-rays.}
+% % \label{fig}
+% \end{figure}
+\begin{figure}[H]
+  \centering
+    {\includegraphics[scale=0.4]{rhoss.pdf}}
+    \hspace{0.2cm}
+ \caption{On the left side of the image, we represent the couple $\left(\hat{\rho}_{i}(e_1), \hat{\rho}_{i}(e_2)\right)$ for each image $U_{i}$ and on the right side, we represent the boxplot of $(\hat{\rho}_{i}(e_1))_{i \leq n}$ (blue) and $(\hat{\rho}_{i}(e_2))_{i \leq n}$ (orange).}
+\label{boxplotrho}
+\end{figure}
+Looking at Figure \ref{boxplotrho}, it confirms the highly dependence behavior of the field.
+\appendix 
+\section{Behavior at large distance.}
 Considering the case where the size of the window $S$ goes to infinity, and assuming that $\rho(x) \to 0$ when $||x||_{2} \to \infty$, we would like to study the decay of $\text{Cov}\left(f_{t}^{\scriptscriptstyle(1)}(0), f_{s}^{\scriptscriptstyle(i)}(x) \right)$ for~$||x||_{2} >> 1$,
@@
 
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{fourConfNew.pdf}}
-    \hspace{0.2cm}
- \caption{In each panel, we represent of the values of $\mathbb{E}\left(f^{1}(0,1)f^{2}(x)\right)$ for $x = (1, 1)$ computed for different values of $b$, the value of the theoretical curve Equation \eqref{thisthothree} in (blue)and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$, for different values of $b = 1, 2.5, 5, 10$ and $C = 40$.
-}
-\label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
-    \hspace{0.2cm}
- \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40, 30, 10,1$.
-}
-\label{fig2}
-\end{figure}
-\begin{figure}[H]
-  \centering
-    {\includegraphics[scale=0.3]{subwindowVarestimation.pdf}}
-    \hspace{0.2cm}
- \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$, for the values $b = 1$ and $C = 40$.
-}
-\label{fig2}
-\end{figure}
-\appendix 
 \section{Computation of the covariance for the three cells configuration}
@@
 }
-\label{fig2}
+\label{figThreeconfnew}
 \end{figure}

### 2023-01-25 Draft_GFC.tex
backup

@@
 \section{Introduction}
-
 The main objective of our study is to be able to decide whether the texture of a grey-level image is isotropic or not.
@@
 {\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
- \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}
+ \caption{Stationnarized bone X-ray image, with its associated excursion sets thresholded at the first, second and third quartile.}
 \label{fig22}
@@
 More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language.
-We exhibit a statistic depending on the ratio of the oriented perimeters that goes to one under $H0$ thanks to the CLT previoulsy established.
+We exhibit a statistic depending on the ratio of the oriented perimeters that goes to one under $H0$ thanks to the CLT previously established.
 Moreover, we prove the consistency of the proposed test.
@@
 \end{proof}
-This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$.
+This result extends the one given in \cite{HermineAgnes} (Proposition 3) where the expected perimeter is computed in the case $\rho(e_i) > 0$.
 Using the former expression, we are also able to obtain an analytic expression for the first moment.
 \begin{Proposition}(Analytic expression for the first moment of the oriented perimeter)
+Considering again the former expression, we get that 
 \label{analytic expression}
   \begin{align}
-  \label{propEquationFisrtmoment}
+  \label{propEquationFisrtmoment2}
   \mathbb{E}\left(f^{(i)}(t) \right) = \int_{\rho(e_i)}^{1}\frac{\exp(-t^2/(1+u))}{\pi\sqrt{(1-u^2)}}du
@@
 \end{align*}
-with $N \sim \mathcal{N}\left(0,1\right)$.
-We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and
+with $N \sim \mathcal{N}\left(0,1\right)$, one should note that $\mathbb{E}\left(f^{(i)}(t)\right) = h_{t}\left(\rho(e_i)\right)$.
+We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$.
+Making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and
 \begin{align*}p_{t}'(x) & = \mathbb{E}\left(\frac{-2|N| -t\sqrt{2(1-x)}}{2(1+x)\sqrt{1-x^2}}\Phi'\left(\frac{2t + |N|\sqrt{2(1-x)}}{\sqrt{2(1+x)}}\right)\right)\\
@@
 & = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.
-\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$.
+\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$ and besides $h(1) = 0$, which gives us the results.
 % \begin{align*}
@@
 \begin{itemize}
-\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, note that $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
-\item In the case where $\rho(e_i) \sim 1$, then $\mathbb{E}\left(f^{(i)}(t) \right) \sim \frac{\sqrt{1-\rho(e_i)}}{\pi\sqrt{2}} \exp(-t^2/2)$, as in \cite{HermineAgnes}, in that case the ratio $\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)$ is invariant in regard to $t$
+\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
+\item In the case of a highly dependent field, \textit{i.e} $\rho(e_i) \sim 1$ ,  from Equation \eqref{propEquationFisrtmoment2} note that we would be integrating over a small interval, therefore $\mathbb{E}\left(f^{(i)}(t) \right) \sim \frac{\sqrt{1-\rho(e_i)}}{\pi\sqrt{2}} \exp(-t^2/2)$, as it has been shown in \cite{HermineAgnes}.
+In that case, the ratio $\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)$ is invariant in regard to $t$.
+\textcolor{blue}{Demander a Hermine, comment on relie ce resultat a son papier}
 \item In the independent case, \textit{i.e.} $\rho(e_{i}) = \text{Cov}\left(X_{0}, X_{e_i}\right) = 0$, we can write
@@
 \subsection{Theoretical and numerical study of the covariance of the perimeter}
-Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$.
+Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$ and that $\rho$ corresponds to a spectral measure that has a density.
 \begin{Lemma} 
@@
 \end{figure}
-Let us first start with the two cells case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$.
+\textcolor{red}{mettre une remarque qui dit que l'existence de la densite spectral nous dit que si les les points sont distincts la covariance est inversible .
+Donc la somme se decompose en : j'ai 2 points, 3 ou 4 points, toruver une ref pour justifier tout ca} \\
+
+Let us first start with the 2-cells case (\textit{see} Lemma \ref{2cells} below), which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, the 4-cells case, will be computed in the Proposition \ref{PropositionFourCell} and finally, the 3-cells case will be studied in the Appendix.
 Applying the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}, we get the next result.
@@
 \begin{Lemma}(Computation of the two cells contribution)
+\label{2cells}
 \begin{align*}
@@
 \begin{equation}
+\label{CovarianceAffine}
 A:= \begin{pmatrix} a & 0 \\ 0 & b\end{pmatrix} \begin{pmatrix} \cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta)\end{pmatrix} 
@@
     \hspace{0.2cm}
- \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$, for the values $b = 1$ and $C = 40$.
+ \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $ m = 4800$, $C = 40$ and the size of $T_{i}$ equal $240\times240$, for the values $b = 1$ and $C = 40$.
 }
@@
     \hspace{0.2cm} 
- \caption{We represent the $p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ the computations for the variance were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$  for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
+ \caption{We represent the $p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ the estimation of the variance was done using an image of size $m = 4800$ and the size of $T_{i}$ being equal to $240\times240$  for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
 % \label{fig2}
-
 \end{figure}
@@
   \centering
-    {\includegraphics[scale=0.4]{TestaniRatiopvaluepi4.pdf}}
-    \hspace{0.2cm} 
- \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$.}
+    {\includegraphics[scale=0.28]{Figurepi411.pdf}} \hspace{-1cm}
+      {\includegraphics[scale=0.28]{Figurepi410.pdf}}
+      \end{figure}
+      \vspace{-3cm}
+      \begin{figure}[H]
+      \hspace{-0.5cm}
+        \centering
+    {\includegraphics[scale=0.28 ]{TestaniRatiopvaluepi4}}
+    % {\includegraphics[scale=0.25]{TestaniRatiopvaluepi410.pdf}}
+    % \vspace{-3cm}
+ \caption{On the first row we represent two generations of an affine Gaussian random fields with covariance of a compact support $\rho(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C}$, as in \eqref{CovarianceAffine} with~$m = 512$, and $\theta = \pi/4$ and $C = 40$ respectively on the left $b = 1.1$ and $b = 10$, on the second row, we represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$..}
 % \label{fig2}
@@
 \end{figure}
-
 \begin{figure}[H]
@@
 \end{figure}
-\subsection{Application of the local isotropy test to real world Data}
+\subsection{Application of the local isotropy test to real world data}
 \paragraph{Study of the anisotropic nature of bone X-rays.}
 The X-ray images are from an retrospective multi-centric study that was conducted at
-three French research hospitals (Amiens, Orleans and Cochin in Paris).
+three French research hospitals (Amiens, Orleans and Cochin in Paris) \textcolor{red}{bien citer les refs des images}.
 Patients were recruited from a program originated by the hospital of Orleans between Nov.
@@
 2006.
-We analyzed $245$ X-ray images of calcaneus bones.
-We first applied a preprocessing step in order to get stationary images.
-This step is performed by substracting the trend which is represented by a plane obtained via a mean-square linear regression, to avoid boundarie issues, we decided to crop from a $400\times400$  image to a $300\times300$ image.
+We analyzed $n=245$ X-ray images of calcaneus bones.
+We first applied a pre-processing step in order to get stationary images.
+This step is performed by substracting the trend which is represented by a plane obtained via a mean-square linear regression.
+Furthermore, to avoid boundaries issues, we decided to crop from a $400\times400$  image to a $300\times300$ image, it is also necessary to standardize the images to be in the correct framework.
 \begin{figure}[H]
@@
 {\includegraphics[scale=0.5]{UnonstationariserUstationariser.pdf}}
- \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}
+ \caption{Example of images before (first row) and after (second row) the stationarization procedure and their respective excursion sets at quantile level $0.5$.}
 \label{fig22}
 \end{figure}
-\paragraph{Applying the local isotropy test.}The first analysis of Figure \ref{figBoxplot} suggests that an additional pre-processing step is required.
-We observe a cluster of points for which the ratio $\mathcal{P}_{1}(q_{\alpha})/\mathcal{P}_{2}(q_{\alpha}) < 1$, which means that the corresponding images are misoriented.
-Thus, before proceeding with the analysis, it is necessary to apply a $\pi/2$-rotation to these images, which amounts to interchanging the values of $\mathcal{P}_{1}(q_{\alpha})$ and $ \mathcal{P}_{2}(q_{\alpha})$, here is the new boxplot that,
+\paragraph{Applying the local isotropy test.}The first analysis of Figure \ref{figBoxplot} suggests the existence of two clusters in regard to the ratio of the two perimeters.
+Indeed, we observe a cluster of points for which the ratio $\mathcal{P}_{1}(q_{\alpha})/\mathcal{P}_{2}(q_{\alpha}) < 1$, which means that the corresponding images are mis-oriented.
+Thus, before proceeding further with the analysis, we apply a $\pi/2$-rotation to these images, which amounts to interchanging the values of $\mathcal{P}_{1}(q_{\alpha})$ and $ \mathcal{P}_{2}(q_{\alpha})$, here is the new boxplot that is obtained,
 \vspace{-0.5cm}
@@
     \hspace{0.2cm}
- \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratio between the two oriented perimeters computed at $t_{\alpha}$ level, $\mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$, for real thresholded images of bone X-rays.}
+ \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratios $(R_{i}(q_{\alpha}))_{i \leq 245}$ between the two oriented perimeters computed at $t_{\alpha}$ level, for real thresholded images of bone X-rays and flipped images.}
 \label{Boxplotretournee}
@@
 \vspace{-0.5cm}
-We can now proceed to apply the local isotropy test, we start by computing the ratio $R_{i}(q_{\alpha})$ for each level set of the image $U_{i}$ at quantile level $\alpha$, with then compute the $p_{value}(q_{\alpha}) = 2(1-\mathbb{P}\left(\mathcal{N} \leq \left|\overline{R}_{n}(q_{\alpha}) - 1)\right|/\overline{\sigma}_{n}(q_{\alpha})\right))$.
+We can now proceed to the local isotropy test and comput the ratio $R_{i}(q_{\alpha}) = \mathcal{P}^{1,i}(t_{\alpha})/\mathcal{P}^{2,i}(t_{\alpha})$ for each image $i$ at quantile level $\alpha$, and then compute  \linebreak the $p_{value}(q_{\alpha}) = 2(1-\mathbb{P}\left(\mathcal{N} \leq \left|\overline{R}_{n}(q_{\alpha}) - 1)\right|/\overline{\sigma}_{n}(q_{\alpha})\right))$, $\overline{\sigma}_{n}(q_{\alpha})$ is estimated using the Montecarlo technique (\textcolor{red}{renvoyer a la partie sur l estimation et dire qui est Rm aussi, qu'on a fait une moyenne sur les Ri et mettre Ri en ordonnee}) .
 \begin{figure}[H]
@@
     \hspace{0.2cm}
- \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{alpha}$ for real thresholded images of bone X-rays.}
+ \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{\alpha}$ for real thresholded images of bone X-rays.}
 % \label{fig}
 \end{figure}
-The $p_{value}$ is lower than $0.001$, except for extreme values of $q_{\alpha}$ (\textit{i.e} $\alpha = 0.99$), this leads us to reject $H_{0}$ of having local isotropy, furthermore, when analyzing Figure \ref{Boxplotretournee} the distribution of the ratio $\left(R_{i}(t)\right)_{i\leq n}$ seems to be invariant in regards to the threshold level as cited in \ref{casdegenerer}, this suggests that the field is highly dependent, the next step would be to estimate $\rho(e_i)$ by using the total variation of the image by applying Proposition \ref{Variationtotal}.
+The values of $p_{value}$ are lower than $0.001$, except for extreme values of $q_{\alpha}$ (\textit{i.e} $\alpha = 0.99$), this leads us to reject $H_{0}$ which is the hypothesis of having local isotropy.
+Furthermore, when analyzing Figure \ref{Boxplotretournee}, the distribution of the ratio $\left(R_{i}(t)\right)_{i\leq n}$ seems to be invariant in regards to the threshold level as cited in Remark \ref{casdegenerer}, which suggests that the field is highly dependent.
+The next step consists in estimating $\rho(e_i)$ by using the total variation of the image and applying Proposition \ref{Variationtotal}.
 % \begin{figure}[H]
@@
 \end{figure}
-Looking at Figure \ref{boxplotrho}, it confirms the highly dependence behavior of the field.
+Looking at Figure \ref{boxplotrho}, it confirms the highly dependence behavior of the field \textit{i.e} $\rho(e_1) \sim 1$ and $\rho(e_2) \sim 1$.
 \appendix 
